### 2013-02-20 phys715/report/report.tex
Added all of the classwork stuff that was on fox2

\documentclass[12pt]{article}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{gensymb}
%\usepackage{epsfig}
\linespread{1.9}

\geometry{
  body={5in, 8.5in},
left=1.25in,
right=1.25in,
  top=1.5in
}

\begin{document}

\title{Physics 715 Term Project:  Numerical Tools \& Aerodynamic Engineering}
\author{Ben Keller}
\maketitle
\newpage

\section{Introduction}
A most remarkable application of the principles of fluid mechanics is that of
heavier than air flight.  Through the application of theory developed by 
Prandtl, Bernoulli, and others, humankind has been constructing aircraft for 
over a century.  Aerospace engineering has become a major part of Western 
industry, accounting for 1.6\% of Canada's GDP in 2008, with a total industry
revenue of over \$20 billion in that same year[1].  The innovation that fuels
this engine of wealth creation is driven by the use of fluid mechanics in 
designing better airfoils and aerodynamic structures.  This process is now 
almost exclusively done using numerical simulations of the Navier-Stokes
Equations with the boundary conditions for the designs being tested.  These 
tools allow rapid turnaround between computer-aided design (CAD) of products
to numerical simulations of their performance, and further revision of the
designs.\par

In this project, I hope to show an outline of the work that goes into designing
a typical component in which hydrodynamic simulations are an important part of
the design process.  These tools are used beyond the aerospace field, and are 
important in the design of products ranging from sports cars to ship propellers
and plumbing.  I will begin by posing a simple design problem: Can a 
cylindrically-symmetrical airfoil be designed and used to focus the airflow
from a fan and improve its performance?  I will design 3 test cases, and simulate
them using a hydrodynamic code with 3D CAD models I will build for each case. 
From this simulation, I will compare the quantitative performance of each case,
and determine the best design.

\section{A Simple Design Problem}
One of the most elementary cases examined in fluid mechanics is that of flow 
over an airfoil.  As the airfoil produces vorticity from the formation of a
viscous boundary layer on along it's surface (a result of the Kutta condition),
it experiences a lifting force proportional to the circulation $\Gamma$ about
its surface, and the flow velocity $u$ relative to the airfoil:
$$F_L = \rho u \Gamma$$
Besides the obvious application of lifting wings on aircraft, airfoils are 
frequently used to duct fans and wind turbines to increase the performance
therein by utilizing the same vorticity effect to push more air across the fan
or wind turbine blades.  I would like to examine this by designing an airfoil
for use around a simple computer cooling fan.  I will examine the flow 
properties of this airfoil in a $10\times10\times10cm$ square duct, similar in
size to a typical ATX computer power supply.

\section{Three Airfoil Designs}
The airfoils I tested were 3 simple designs: a simple hollow cylinder, a $4cm$ long airfoil, and a $2cm$ long airfoil.  The shapes of the
airfoils are discussed in section below.
The fan I will design the airfoil for is a $7cm^2$ square 12V DC fan, rated to 
pump air at a rate of 70 cfm (cubic feet per minute).  This results in a fluid
velocity of roughly $6.7m/s$.  As the airfoil will have a diameter of $7cm$, 
this results in a Reynolds number (in air, at 25\degree C, the kinematic viscosity is 
$\approx1.56*10^{-5} m^2/s$) of:
$$R_e = \frac{UL}{\nu} = \frac{6.7*0.07}{1.56*10^{-5}} = 3.0*10^4$$
This large Reynolds number implies that turbulence may become an important for
accurately modelling this situation.

I chose two NACA airfoils for my experiment, NACA5440 with a length of $2cm$
and NACA5420 with a length of $4cm$ .  This pair was chosen so that the airfoil
with twice the length (NACA5420) would have the same aperture diameter (since it has half the thickness of NACA5440).  The rectangular airfoil was simply a $4
\times 0.5cm$ box.

\begin{figure}[H]
\centering
\includegraphics[width=6in]{../images/airfoils.png}
\caption{Cross-sections of my 3 airfoils}
\end{figure}

\subsection{NACA Parametric Airfoils}
The two lifting airfoils I will test are based on the National Advisory
Committee for Aeronautics (NACA)'s four digit series of parametric airfoils.
Ironically, these airfoils were designed and tested in 1933, long before 
digital computers became widely available.  The NACA airfoils are described
by a series of parametric equations of three variables.  The three variables,
$m$, $p$, and $t$ describe the fractional camber, the location of the
maximum camber in the x-axis, and and the fractional maximum thickness.  The
camber of the airfoil is a measure of the asymmetry between the upper and lower
surfaces, and is measured as the fraction of the distance of the maximum on the
curve of mean thickness from the x-axis over total length of the airfoil.  The
fractional maximum thickness is simply a ratio of the maximum thickness in the
y-axis over the length $l$ of the airfoil.  Expressed as percentages, the first
digit of $m$ and $p$, and the first two digits of $t$ define the airfoil 
NACA MPTT (ie, NACA 1234 has a maximum camber of 10\%, located at 20\% of its
total length, and has a thickness 34\% of its length).  The equations that
define the upper $(x_U, y_U)$  and lower $(x_L, y_L)$ surfaces of these 
airfoils are as follows:
$$x_U = x - y_t\sin\theta, \quad y_U = y_c+y_t\cos\theta$$
$$x_L = x + y_t\sin\theta, \quad y_L = y_c-y_t\cos\theta$$
$$\theta = \tan^{-1}(\frac{dy_c}{dx})$$
$$y_t = \frac{t}{0.2}l[0.2969\sqrt{\frac{x}{l}}-0.1260(\frac{x}{l})-
0.3516(\frac{x}{l})^2+0.2843(\frac{x}{l})^3-0.1015(\frac{x}{l})^4]$$
\[y_c = \left\{\begin{array}{l l}
    m\frac{x}{p^2}(2p-\frac{x}{l}) & \quad 0 \le x \le pl \\
    m\frac{l-x}{(1-p)^2}(1+\frac{x}{l}-2p) & \quad pl \le x \le l\\
  \end{array} \right.
\]

\section{Numerical Methods}
As the reader may be aware, the Navier-Stokes Equations are a system of 
nonlinear partial differential equations that describe the flow of viscous
fluid.  The equations determine the evolution of the velocity field in the
fluid $\mathbf{v}$ in relation to the body forces $\mathbf{F}$, the stress 
on the fluid $\mathbb{T}$, the density $\rho$, and the pressure $P$.  The
equations are defined as follows:
$$\rho\frac{D\mathbf{v}}{Dt} = -\nabla P +\nabla\cdot\mathbb{T}+\mathbf{F}$$
Finding solutions to these equations beyond simple cases,
as with finding solutions for any system of nonlinear PDEs, usually comes to
finding numerical solutions.

\subsection{Domain Decomposition \& Meshing}
The first step in testing my airfoils was to model them in a Computer Aided
Design program.  I used OpenSCAD to generate the 2D slices of the airfoils
using the parametric equations, and then ``extruded'' them in a $3.5cm$ radius
circle about the z-axis.  This extrusion process is equivalent to defining
the $x$ and $y$ coordinates of the NACA equations to be the $z$ and $r$ 
coordinates of a cylindrical coordinate frame, and integrating the equations 
about the $\theta$ axis.  An example of the resulting 3D surface is shown in
figure NUM.

\begin{figure}[H]
\centering
\includegraphics[width=6in]{../images/NACA5420.png}
\caption{NACA5420 airfoil extruded in 3D}
\end{figure}

Once the airfoil has been designed using OpenSCAD, it can be exported as a 
Standard Tessellation Language (STL) file.  This file contains a series of
vertices and unit normals describing a triangular tessellation of the airfoil
surface.  I then wrote a script for the finite element mesh generator gmsh that
defined the volume of the simulation, with the airfoil STL centred in a 
$10\times 10\times 10 cm$ box.  Gmsh then automatically decomposed the volume
of the box into a tetrahedral mesh.  This meshing is essential for the Finite
Volume method, which will be discussed in the next section.
An example of the resulting mesh is shown in figure NUM.

\begin{figure}[H]
\centering
\includegraphics[width=6in]{../images/mesh.png}
\caption{Domain decomposition mesh generated by gmsh}
\end{figure}

\subsection{Code\_Saturne}
The tool I used for solving the Navier-Stokes equations in the case
of flow around my airfoils was a 
suite of software tools written by the French utility corporation 
\'{E}lectricit\'{e} de France (EDF), Code\_Saturne.  
\subsubsection{Discretization \& Numerical Solver}
Naturally, the first step one would expect in trying to solve a system of
equations such as the Navier-Stokes would be to discretize the problem: to split
the time and space components into finite elements.  The splitting of the fluid
volume into cells makes this solution one of a class of solutions known as 
Finite Volume Models.  The general transport equation that Code\_Saturne solves
is for the transport of quantity $f$, with sources $S$, density $\rho$, 
kinetic energy $K$, and fluid velocity $\mathbf{u}$, is:
$$\rho\frac{\partial f}{\partial t} + \nabla\cdot((\rho\mathbf{u})f) - 
\nabla\cdot (K\nabla f) = Sf+\nabla\cdot(\rho\mathbf{u})f$$
By solving this equation, the transport of any quantity can be determined.

Code\_Saturne offers a number of time discretization methods, all from the 
family of linear multistep methods.  I used the simplest, 1st order method, 
where a quantity $\Phi$ is calculated at timestep $n+1$ using the value at 
timestep $n$ and $n-1$:
$$\Phi^{n+1} = 2\Phi^n-\Phi^{n-1}$$
The discrete form of the general transport equation, for timesteps of 
$\Delta t$:, is:
$$\frac{\rho}{\Delta t}(f^{n+1}-f^n)+\nabla\cdot((\rho\mathbf{u})(f^{n+1})
-\nabla\cdot(K\nabla f^{n+1})=[Sf]^{n+1} + \nabla\cdot(\rho\mathbf{u})f^{n+1}$$
This allows the incremental calculation of quantities at timestep $n+1$ using
the properties of the flow and the quantity at timestep $n$.

The volume discretization simply uses the non-spatially varying elements to be
averaged over the volume of the cell.  Divergences are simple to calculate in
this discrete form using Green's Theorem:
$$\nabla\cdot \Phi = \displaystyle\sum\limits_{i,j \in Neighbour(i)}\Phi_{ij}
S_{ij}$$
In other words, the divergence of quantity $\Phi$ is simply the sum over all
cells $i$ with faces intersecting cells $j$, with surface area $S_{ij}$ and
$\Phi_{ij}$ on the interface between them.  By iterating the general transport
equation over every cell face, and matching the boundary conditions on the 
edges of every intersecting cell, a continuous volume evolving over a continuous
period of time can be broken down into a discretized volume of finite cells
evolving over a finite number of timesteps in an iterative process.  A more 
thorough examination of the numerical methods used in Code\_Saturne and other
Navier-Stokes solvers is beyond the scope of this paper.  For a full treatment
of Code\_Saturne's architecture, see [3] and [5].
\subsection{Usage}
Code\_Saturne read the mesh I generated earlier, using the mesh elements as the
3D domains in the finite element method.  I gave the tool fluid properties
(density, temperature, viscosity) of air at 25\degree C, and defined the 
boundary conditions such that the cube faces around the airfoil were solid 
walls, but the face in front of the airfoil was an inlet, pumping air in at
$6.7m/s$, and the face behind the airfoil was an outlet, allowing air to escape
without piling up.  I gave the air in the box an initial velocity of $6.7m/s$
in the $-z$ direction, so that there wasn't a discontinuity in flow velocity
at the inlet.  I used Code\_Saturne's steady, single phase flow solver, along
with the $k-\epsilon$ turbulence model.  While by definition turbulent flow 
is unsteady, the bulk flow in this case is steady, and so this solver can be
used.  I ran the simulation for a total of 1 second, with timesteps calculated
automatically.
I ran 4 cases with Code\_Saturne: an empty box, and 1 for each of my 3 airfoils.
Code\_Saturne produced a file that could be read using ParaView to examine
various physical properties in 3D.

\subsubsection{Turbulence Modelling}
The turbulence model I used for this project was the $k-\epsilon$ model.  This
technique works by solving for the transport of two scalar values: the 
turbulent kinetic energy $k$ and the turbulent dissipation (in other words,
the turbulence scale) $\epsilon$.  This model depends only on the Reynolds 
stress tensor $\mathbb{R}$, fluid density $\rho$, and dynamic viscosity $\mu$.
The equations describing this model are shown below, for the case of an
incompressible flow without sources or sinks:
$$k = \frac{1}{2}R_{ij}$$
$$\mathcal{P} = -\rho R_{ij}\frac{\partial u_i}{\partial x_j}$$
$$\rho\frac{Dk}{Dt} = (\mu+0.009\frac{k^2}{\epsilon}\nabla k)+\mathcal{P} -
\rho\epsilon$$
$$\rho\frac{D\epsilon}{Dt} = (\mu+0.007\frac{k^2}{\epsilon}\nabla\epsilon) +
1.44\frac{\epsilon}{k}\mathcal{P} - 1.92\rho\frac{\epsilon^2}{k}$$
As the reader may deduce, the first term of the two transport equations act
as a turbulent viscosity term that feeds back to the full Navier-Stokes 
Equations:
$$\mu_t = 0.009\rho\frac{k^2}{\epsilon}$$
The derivation of this model is beyond the scope of this project, and can be 
found in [5].

\section{Results \& Analysis}
I compared the resulting simulation using data generated using the ParaView 
utility.  I used this tool to obtain a 2 dimensional slice of the simulated
volume, normal to the z-axis, and $1cm$ from the exit of the airfoil.  This 
slice contained measurements at points on the surface (based on the number of 
intersecting mesh cells) for pressure, velocity, and energy stored in 
turbulence. Figure NUM shows streamlines plotted around the NACA5420 airfoil
using ParaView.  Figure NUM shows one of the slices I used to get data points.

\begin{figure}[H]
\centering
\includegraphics[width=6in]{../images/NACA5420_streamlines.png}
\caption{Streamlines flowing across NACA5420 airfoil, colored by turbulent
kinetic energy}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=6in]{../images/slice_generation.png}
\caption{Slice through flow $1cm$ behind NACA5440 airfoil, colored by velocity}
\end{figure}

I used python, along with the Numpy numerical module and matplotlib plotting
utility to produce plots of the velocity through the slice, the turbulent energy, and an approximation of vorticity magnitude $\bar\omega$
calculated using the velocity component parallel to the plane $v_{||}$:
$$\bar\omega = rv_{||}$$

As figure NUM shows, NACA5440 had the highest total airflow, with a mean flow
velocity of $6.87m/s$.  However, the high spread suggests this is due to 
turbulence, and not a bulk flow.  The low spread on the NACA5440 airfoil 
is a desirable trait for a cooling fan, as you won't find pockets of hot
and cool forming because of inconsistent flow rate.  Figure NUM confirms my
suspicion about turbulence in NACA5440, with a much higher turbulent energy loss
than even the empty box.  NACA5420 also has the nice property of very laminar
flow, with vorticity close to zero across the entire flow surface, as shown in
figure NUM.  A table of average and RMS velocities through the surface is shown
in the table below.\\

\begin{figure}[H]
\centering
\includegraphics[width=5in, clip=true, trim=0in 0in 0.5in 0.5in]{../images/velocity_profile.png}
\caption{Z component velocity profile}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=5in, clip=true, trim=0in 0in 0.5in 0.5in]{../images/turb_profile.png}
\caption{Turbulent energy profile}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=5in, clip=true, trim=0in 0in 0.5in 0.5in]{../images/vorticity_profile.png}
\caption{Z normal vorticity profile}
\end{figure}

\begin{tabular}{| l | l | l |}
\hline
Case & Mean Velocity (m/s) & RMS Velocity (m/s) \\
\hline
Empty Box & 6.36 & 1.3 \\
NACA5440 & 6.87 & 3.2 \\
NACA5420 & 6.43 & 0.66 \\
\hline
\end{tabular}

\subsection{Pitfalls}
The biggest issue I came across during this project was the clearly incorrect 
turbulent velocities generated in the simple cylinder case.  As figure NUM 
shows, the velocity at a number of points on the test surface were actually
greater than $c$!  This I believe is a result of numerical divergence in the
turbulence $k-\epsilon$ model, and the sharp edges of the cylinder. Figure NUM
shows that the turbulent energy within the flow is absurdly high, peaking at
$10^{18}J$.

\begin{figure}[H]
\centering
\includegraphics[width=5in, clip=true, trim=0in 0in 0.5in 0.5in]{../images/cylinder_velocity_profile.png}
\caption{Turbulent velocity in cylinder test case}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=5in, clip=true, trim=0in 0in 0.5in 0.5in]{../images/cylinder_turb_profile.png}
\caption{Turbulent energy in cylinder test case}
\end{figure}

The leading edge of the cylinder was normal to the fluid velocity, and this 
was likely the source of this problem.  The $k-\epsilon$ model fails in
cases with large pressure gradients, and the flow colliding with this
surface may have caused the turbulence model to produce unphysical turbulent
kinetic energies.

This problem could likely be corrected by replacing the flat surfaces with 
rounded ones, or using a more robust turbulence model.

\section{Conclusion}
The data I obtained in this project is not as conclusive as I would have hoped.
While it appears that the NACA5420 is actually excellent for laminarizing the
airflow in my duct, a certainly useful property, none of my airfoils produced
a statistically significant increase in mean velocity through the duct.  This
isn't very surprising, since I didn't actually simulate an airfoil 
around a fan, but an airfoil placed in front of a fan, and ducts placed around
fans are usually there to improve fan performance.

I really only was able
to scratch the surface of the many problems involved in simulating fluid flow, 
and a larger, future project could go in many directions.  I would have liked to
examine in more depth the turbulence modelling, perhaps by looking at other
models than $k-\epsilon$, as well as actually iterating through designs to
improve the performance, rather than just comparing a random selection of 
airfoils.  With numerical tools for analyzing flow, design work such as this
has become extremely efficient, and the entire parameter space of the NACA
airfoils could easily be probed with only a few months of CPU time.  Along with
tools like CNC machining, entire designs can move from idea to physical 
product using nothing more than a computer.

\section*{References}
\begin{enumerate}
\item \textit{Aerospace Globalization 2.0: Implications for Canada's Aerospace
Industry} AeroStrategy Management Consulting, November 2009

\item \textit{Code\_Saturne User Manual} EDF R\&D, December 2011 
(retrieved from\\ 
\verb!http://research.edf.com/fichiers/fckeditor/Commun/Innovation/!\\
\verb!logiciels/code_saturne/Documents/2.1/user.pdf!)

\item \textit{Code\_Saturne Theory Manual} EDF R\&D, December 2011
(retrieved from\\
\verb!http://research.edf.com/fichiers/fckeditor/Commun/Innovation/!\\
\verb!logiciels/code_saturne/Documents/2.1/theory.pdf!)
\item \textit{Aerodynamics of Wind Turbines} Martin O. L. Hansen, Routledge
December 2007

\item \textit{Code\_Saturne: a Finite Volume Code for the Computation of
Turbulent Incompressible Flows - Industrial Applications} Fr\'{e}d\'{e}ric
Archambeau, Namane M\'{e}chitoua, \& Marc Sakiz, International Journal on Finite
Volumes, Vol 1, 2004

\item \textit{The Characteristics of 78 Related Airfoil Sections From Tests In
The Variable Density Wind Tunnel} E. N. Jacobs, K. E. Ward, \& R. M. Pinkerton,
NACA Report No. 460, 1933
\end{enumerate}

\section*{Software Used}
\begin{itemize}
\item OpenSCAD  \textit{www.openscad.org}
\item Fully parametric NACA 4 digit Airfoil/Wing profile 
\textit{http://www.thingiverse.com/thing:10513}
\item gmsh \textit{geuz.org/gmsh/}
\item Code\_Saturne \textit{www.code-saturne.org}
\item paraView \textit{www.paraview.org}
\item Python \textit{www.python.org}
\item Numpy \textit{www.numpy.scipy.org}
\item Matplotlib \textit{matplotlib.sourceforge.net}
\end{itemize}
\end{document}

### 2013-02-20 phys761/phys761assign3.tex
Added all of the classwork stuff that was on fox2

\documentclass{article}
\author{Ben Keller}
\title{Physics 761 Presentation: "Population III stars: hidden or disappeared?"}
\begin{document}
\maketitle
\section{Background: Metallicity \& Stellar Populations}
\section{The Paper's Methodology}
This paper tried to answer the question of how late could Population III stars
could still form using a series of numerical simulations.  The authors used 
smoothed particle hydrodynamics (SPH) to simulate a comoving volume of VOLUME 
Mpc$^3$.  This volume was filled with $2*256^3$ dark matter and baryonic 
particles ($256^3$ of each).  These particles had a mass 
\section{The Paper's Results}
\section{Conclusions}
\end{document}

### 2013-02-20 phys781/report.tex
Added all of the classwork stuff that was on fox2

\documentclass[12pt]{article}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{gensymb}
%\usepackage{epsfig}
\linespread{1.9}

\geometry{
  body={5in, 8.5in},
left=1.25in,
right=1.25in,
  top=1.5in
}

\begin{document}

\title{Physics 781 Term Report:\\  Bulges, Black Holes, and Cores:\\ A Review of
the $M_{BH}-\sigma$ and  $M_{BH}-M_{bulge}$ Relation in Theory \& Observation}
\author{Ben Keller}
\maketitle
\newpage

\section{Introduction}
when one examines the structure and evolution of a galaxy, at first glance it 
would seem that the central supermassive black hole (SMBH) would play a 
minimal role in the larger observable properties of the galaxy.  On both mass 
and length scales, the SMBH is small compared to the galaxy as a whole.  For
a typical Milky-Way type galaxy, the SMBH mass is 4 orders of magnitude less 
than the total baryonic mass of the galaxy 
($4*10^6M_\odot$ vs $6*10^{10}M\odot$).  The Schwartzchild radius of this black
hole is even further from the scale of the galaxy, falling 11 orders of 
magnitude smaller than the disk radius ($4*10^{-7}$pc vs. $25$kpc).  Recent 
developments have shown, however, for the spheroidal bulge component of disk 
galaxies, the mass of this SMBH has a tight correllation with the large scale
properties of the bulge, most notably the total bulge mass and the velocity 
dispersion of stars within the disk.  Upon a more thorough examination of the
physical processes governing this system, and the history of its evolution, it
should become clear to the reader that this is neither particularly mysterious
nor is it truly something that should be unexpected.  Despite this, there still
remains some uncertainty regarding the precise nature of these (hence
refered to as the $M_{BH}-M_{bulge}$ and $M_{BH}-\sigma$) relations.  In this
paper, I hope to guide the reader to an understanding of the theory behind these
observations, as well as the current state of knowledge on the topic.
\section{Background \& Observations}
Simply by looking at night sky from a southern location, one can deduce that
the Milky Way galaxy is densest in a region lying in the constellation 
Saggitarius.  Kapteyn was able to determine, roughly a century ago, that the
shape of our galaxy was that of a disk, and that our sun roughly halway along
the radius of this disk.  Close examination of the core region, Sgr A, has 
until relatively recently, been difficult due optically thick obscuring dust.
With the advent of long wavelength astronomy, it has become possible to directly
image stars and gas within the galactic core.  It has been known from infrared
observations since Genzel \& Townes 1987 that the core radius of the galaxy is
extremely compact, with current estimates placing it at $\approx 0.5$pc in
radius (Merrit 2010).  Warm gas and dust have also been observed in infrared and
radio wavelengths at higher densities in this core region.
\subsection{A Central, Supermassive Black Hole}
Within the core region of Sgr A exists a bright radio and hard X-ray emitter, 
Sgr A*.  X-ray observations of this source have constrained it to being highly
compact, and extremely hot ($10^8-10^{10}$K).  This observation points towards
a highly energetic source within the core.  This source explained originally by
two competing models: a driving SMBH, heating gas through accretion, or a 
particularly violent and compact region of starburst activity.  The X-ray 
emission observed within this core region constrained the mass of the black hole
only very loosely ($M_{BH} > 100 M_\odot$) if starburst activity and UV heating
of the gas was the source of the gas heating.  The starburst model truly fails
in the face of one important datum:  the enclosed mass of the core.  By 
examining the rotation curve of stars and gas very close to the core, the 
mass enclosed by that core was able to be determined, as is shown in figure NUM.
As is clear from the figure, the SMBH model is a perfect fit for the observed 
rotation curve.  In addition to this, the densities for the core are so large
that there is no configuration of stars that could be long lived at that 
density.

\subsection{Extragalactic SMBHs}
\subsection{The $M_{BH}-\sigma$ Relation}
We are used to seeing relations between masses and velocity distributions before
in the form of the Tully-Fisher and Faber-Jackson relations for galaxies (though
in these cases, it is an indirect measure of stellar mass through their 
luminosity).  This should not come as much of a suprise to us, since the 
Virial Theorem tells us there must be a relation between the kinetic energy and
the enclosed mass.
\section{Theory}
While observations have done an excellent job of showing the \textit{existence}
of the $M_{BH}-\sigma$ relation, they leave open the obvious question as to the
nature of this relation, namely how and why it arises.  The first major attempt
to answer this question was presented in Silk \& Rees 1998, with a coevolution 
model.
\section{Recent Developments}
\section{Conclusion}
\section*{References}
\begin{enumerate}
\item \textit{Exploring the unusually high black hole-to-bulge mass ratios in 
NGC4342 and NGC4291: the asynchronous growth of bulges and black holes} Bogdan 
et al.,  submitted to ApJ, retrieved via arXiv 2012
\item \textit{The Distribution of Stars and Stellar Remnants at the Galactic 
Center} Merritt, ApJ 718, 2010
\item \textit{The Supermassive Black Hole at the Galactic Center} Melia \& 
Falcke, ARAA 39, 2001
\item \textit{Quasars and Galaxy Formation} Silk \& Rees, A\&A 331, 1998.
\item \textit{Inward Bound -- The Search for Supermassive Black Holes in 
Galaxtic Nuclei} Kormendy \& Richstone, ARAA 33, 1995
\item \textit{Physical Conditions, Dynamics, and Mass Distribution in the Center
of the Galaxy} Genzel \& Townes, ARAA 25, 1987
\end{enumerate}
\end{document}

### 2013-02-20 phys785/assign1/assign1.tex
Added all of the classwork stuff that was on fox2

\documentclass{article}
\author{Ben Keller}
\title{Physics 785 Assignment 1}
\begin{document}
\maketitle
\centering
\section*{A Virialized Filamentary Infrared Dark Cloud}
\subsection*{Abstract}
Infrared Dark Clouds (IRDC) match the initial conditions of massive 
and clustered star formation, and are thus an excellent tool
to probe the earliest stages of these modes of star formation.
Using IRAM molecular line observations of $C^{18}O$ along
with MIREX extinction maps, we measure the kinematics of a
filament containing a few $10^3 M_\odot$, with a length of
$\approx4pc$.  We use this data to obtain the total velocity
dispersion $\sigma$ along the line of sight to approximately
$10\%$ accuracy. This allows us to use a simple theoretical
model of the filament geometry to perform a virial analysis
on the filament probing smaller scales (and produce better
mass estimates) than done in 
previous studies, such as Hernandez and Tan 2011. Our results
show that, contrary to previous studies, IRDC filaments are
in (or near) virial equilibrium.  If IRDC filaments are the
initial locations of star formation, this result implies that
stars form from gas that is in rough pressure equilibrium, 
validating one of the main assumptions of McKee and Tan's
core accretion model of massive star formation.
\end{document}

### 2013-02-20 phys785/assign1/assign2.tex
Added all of the classwork stuff that was on fox2

\documentclass{article}
\usepackage[hmargin=3cm, vmargin=3cm]{geometry}
\usepackage{graphicx}
\author{Ben Keller}
\title{Physics 785 Problem Set 1}
\begin{document}
\maketitle
\section{CGPS Spin Temperatures}
For this problem, the spin temperature $T_s$ was calculated using the same
equation as Strasser \& Taylor 2004:
$$ T_s = \frac{T_{boff}}{1-e^{-\tau}}$$
The error was in this was calculated using the partial derivatives:
$$ \delta T_s = \delta T_{boff} \frac{\partial T_s}{\partial T_{boff}} + \delta
	e^{-\tau} \frac{\partial T_s}{\partial e^{-\tau}}$$
$$ \delta T_s = \frac{\delta T_{boff}}{1-e^{-\tau}} + \frac{\delta
e^{-\tau}}{(e^{-\tau}-1)^2}$$

I also calculated a signal-to-noise value comparable to that used in Simon
Strasser's MSc thesis, and selected only spin temperatures where this value
was greater than 3 (ie, a $>3\sigma$ detection):
$$ SN = \frac{|T_{on}-T_{off}|}{\sqrt{\delta T_{on}^2 + \delta T_{off}^2}} $$
I also calculated the average spin temperature $\bar T_s$ of these three lines 
of sight for all channels that passed the previous criteria in all three lines 
of sight.  I also calculate an error for this average,
$$\delta \bar T_s = \sqrt{\delta T_{s1}^2+\delta T_{s2}^2+\delta
T_{s3}^2}/\sqrt{N}$$
This is shown in Figure 2, and
provides a similar picture as Figure 4.7 in the Strasser thesis:  since the 
LSR velocity is primarily a determined by projection of the galactic rotation
curve, this figure provides a view of the spin temperature at different depths 
in the galactic plane.
\begin{figure}
	\includegraphics[scale=0.65]{110.600_4.6946.eps}
\end{figure}
\begin{figure}
	\includegraphics[scale=0.65]{111.612_0.3739.eps}
\end{figure}
\begin{figure}
	\includegraphics[scale=0.65]{111.649_2.4038.eps}
\caption{Off-source brightness temperature, exponential optical depth, and 
spin temperature for three lines of sight}
\end{figure}
\begin{figure}
	\includegraphics[scale=0.6]{meanTs.eps}
\caption{Mean spin temperature as a function of LSR velocity from 3 lines of
sight.}
\end{figure}
\pagebreak
\section{Cooling Function}
For the construction of a simple 3-component (Hydrogen, Carbon II, and Sulfur
II) cooling curve, used the following equations, derived from Dalgarno \& McCray
1972 for CII and from Penston 1970 for Hydrogen and SII.  The cooling component
I included for the two metals was \textit{Electron Impact Excitation} collisions
with HI.  The mechanism that HI cools in this function is through Lyman-$\alpha$
emission.  Each of these functions have had the density normalized out (but for
the diffuse ISM, the density can be expected to be $\approx 0.1 cm^{-3}$.  Also
omitted is the fractional ionization, which can become important in regions with
large cosmic ray or FUV flux.  In Figure 3, note the negative slope in
$\Lambda_{total}$ between  $\approx 200 - 4000 $K, indicative of a thermal
instability.  The abundances for CII and SII were obtained from Table 1 of 
Dalgarno \& McCray 1972.  The per-species cooling functions as a function of
temperatrue are shown below ($f_{CII}$ and $f_{SII}$ are the fractional
abundances of Carbon and Sulfur, and were set to $3.75*10^{-4}$ and
$1.4*10^{-5}$ respectively).
$$ \Lambda_{H} (T) = 10.2eV*3.23*10^{-10}T^{1/2}(1+17500/T)e^{-118000/T}$$
$$ \Lambda_{CII} (T) = f_{CII}*7.9*10^{-20}T^{-1/2}e^{-92/T}$$
$$ \Lambda_{SII} (T) = f_{SII}*8.44*10^{-18}T^{-1/2}e^{-21400/T}$$
\\
\\
\textit{Note: All calculations and plots were done using attached code}
\begin{figure}
	\includegraphics[scale=0.7]{cooling.eps}
\caption{Normalized cooling function for a diffuse ISM composed of Hydrogen,
Carbon, and Sulfur with typical abundances}
\end{figure}
\section*{References}
Penston, M.V., \textit{Cooling Mechanisms in the Interstellar Gas}, ApJ 162.
1970\\
Dalgarno, A. \& McCray, R.A., \textit{Heating and Ionization of HI Regions},
ARAA 10. 1972\\
Strasser, S.T., \textit{Properties of HI in the Galaxy}, University of Calgary
MSc Thesis. 2002\\
Strasser, S.T. \& Taylor, A.R. \textit{1420MHz Continuum Absorption toward
Extragalactic Sources in the Galactic Plane}, ApJ 603. 2004
\\
\\
\end{document}

### 2013-02-20 phys785/problemset2/assign2.tex
Added all of the classwork stuff that was on fox2

\documentclass{article}
\usepackage[hmargin=3cm, vmargin=3cm]{geometry}
\usepackage{graphicx}
\author{Ben Keller}
\title{Physics 785 Problem Set 2}
\begin{document}
\maketitle
\section{Oxygen Chemical Network}
We can gain a qualitative view of the relative abundances of oxygen compounds
by looking at the reactants needed to produce each species, and the rate
coefficient for the production reactions along with the same information for
reactions that destroy that species.  If a species has numerous reactions
producing it, with relatively high rate coefficeints and abundant precursors,
and few destruction reactions, we can expect to find this compound in abundance
in the molecular ISM. Since many of the compounds in the oxygen chemical network 
are also reactants for producing other compounds, to gain a quantitative estimate, 
integrating the series of coupled differential equations defining the densities
of all species would be necessary.  However, for a number of species (Especially
$H_2$ and $H$, the densities are many orders of magnitude higher than other
compounds, and reactions involving these species will be very rapid, even with
relatively low rate coefficients.  Figure 1 shows graph showing the chemical network
for oxygen.  Reactions that involve additional reactants have their transitions
labeled with the additional reactants, and the transitions are colored based on
the type of reaction involved.  The reaction types and rate coefficients are
defined in the table below:\\

\begin{tabular}{| c | c | c |}
	\hline
	Reaction Type & Rate Coefficient & Colour \\
	\hline
	Neutral-Neutral without Potential Barriers & $10^{-11}$ & Purple\\
	Photodissociation & $10^{-9}$ & Blue\\
	Ion-Molecule Reactions & $10^{-9}$ & Green\\
	Charge Transfer & $10^{-9}$ & Orange\\
	Dissociative Recombination & $10^{-6}-10^{-7}$ & Red\\
	\hline
\end{tabular}\\

The charge transfer rate coefficient was estimated to be on the same order of
magnitude as the coefficients esstimated in Le Teuff et al. 2000.  In addition
to the rate coefficients given above, we also need a rough idea as to the
abundances of some of the precursor compounds.  We know that the abundance of
both atomic and molecular hydrogen is many orders of magnitude higher than all
the other components of the molecular ISM, and so reactions involving those
species will be very efficient.

From looking at the labeled reaction network,
we can see that the most efficient reactions (Dissociative Recombination) are 
occuring in two production reactions that generate OH, and although it is
involved in a number of reactions that consume it, these reactions all occur
with 2-3 orders of magnitude smaller rate coefficients.  This suggests that OH
is one of the more common species.  The other species involved in dissociative
recombination reactions are CO, which is also created 5 separate reactions (also
suggesting large abundances in the molecular ISM), CO2 (which is formed from the
already established to be abundant OH through a neutral-neutral reaction and
from HCO2+, which due to it's single production reaction from HCO+ is likely not
as abundant as the previous two species), water (which should be produced at a
much lower rate than OH, since its precursor and its super-precursor both will
also form OH), and O2 (which has the largest number of reactions involving it,
and the only rapid dissociation reaction is from a product that must be itself
produced from O2, and so likely is not particularly abundant).  Based on the
network, I would predict that OH, CO, and CO2 are the most most abundant neutral
oxygen species.  Since OH+ is formed from abundant OH transfering charge to H+,
it is also likely to be relatively abundant (although it will rapidly be turned
into H2O+ by reacting with highly abundant H2).

The species I expect to see in
the lowest abundances are those that have a small number of slow production
reactions coupled with many rapid destruction reactions.  O2H+ is an obvious
example of this, since it is only formed from O2, and rapidly dissociates back
itno O2 and H+.  Another likely rare ion is H3O+ (since it is formed from H2O+ 
which will preferentially form OH, and rapidly is converted into H2O and OH).
\begin{figure}
	\centering
	\includegraphics{oxygen.ps}
	\caption{Chemical network for oxygen species}
\end{figure}\\
\section{Clumps in $\rho$ Ophiuchus}
Johnstone et al. 2000 contains $850 \mu m$ observations of dense 
molecular clumps within the $\rho$ Ophiuchus cloud using the 
SCUBA bolometer on the JCMT.  Using their mass estimates calculated
for a dust temperature of 20K, I generated a differential clump
mass function $\frac{dN}{dM}$, and fit a power law to this distribution
function:
$$\frac{dN}{dM} \propto M^{-\alpha}$$
I first selected only clumps with mass $>0.6M_\odot$.  I chose this selection
firstly because it is greater than the incompleteness limit of $0.4M_\odot$, and
it is the break that Johnstone et al. reports between the two different
power-law slopes of $\alpha=0.5$ (below $0.6M_\odot$) and $\alpha=1.0\pm0.5$
for the cumulative mass function $N(M)$ (this would mean a change in slope for
the differential mass function as well).
I calculated these values by taking a histogram of the base-10 log of the masses
to find the number of clumps $N_i$ at a bin $\log M_i$ of width $\delta \log M$.
$\frac{dN}{dM}$ was then calculated simply as:
$$\frac{dN}{dM}(M_i) = \frac{N_i}{M_i}$$
I used the width of the bin $\delta \log M$ and the relative Poisson noise
$\sqrt{N_i^{-1}}$ as my uncertainties in $\log M_i$ and $\log \frac{dN_i}{dM_i}$
I then used a least squares optimizer from the Scipy python library to fit a
power law (linear in logspace) to $\frac{dN}{dM}$ vs. $M$.  I weighted the
error function using the geometric mean of my two uncertainties.
The result of this fit is a power law with $\alpha = 1.9 \pm 0.3$.  This is
exactly what we would expect if the cumulative mass function has a power law
with $\alpha = 1$, since the derivative will reduce $\alpha$ by one.
$$\frac{dN}{dM} \propto M^{-1.9\pm 0.3}$$
This fit, along with the data, is shown in figure 2.
\begin{figure}
	\includegraphics[scale=0.8]{clumpmass.eps}
	\caption{Differential Mass Function dN/dM vs. Clump Mass M}
\end{figure}\\
\textit{Note: All calculations and plots were done using attached code}
\section*{References}
Johnstone et al. 2000 \textit{Large-Area Mapping at 850 Microns. II} ApJ 545,
pp. 327\\
Le Teuff et al. 2000 \textit{The UMIST Database for Astrochemistry 1999} AJS
146, pp. 157\\
\\
\\
\end{document}

### 2013-02-20 phys715/scripts/plot_turb_cylinder.py

@@ -1,0 +1,38 @@
+#!/usr/bin/python
+import csv
+import numpy as np
+import matplotlib.pyplot as plt
+
+def fmtpoint(point):
+    p = {'x':float(point['Points:0']), 'y':float(point['Points:1']),
+    'z':float(point['Points:2']), 'vx':float(point['Velocity:0']), 
+    'vy':float(point['Velocity:1']), 'vz':float(point['Velocity:2']), 
+    'te':float(point['TurbEner']), 'p':float(point['Pressure'])}
+    p['r'] = np.sqrt(p['x']*p['x'] + p['y']*p['y'])
+    return p
+
+def get_points_annulus(data, radius):
+    points = []
+    for point in data:
+        p = fmtpoint(point)
+        if p['r'] < radius:
+            points.append(p)
+    return points
+
+def plot_turb(data, label):
+    te = []
+    r = []
+    for point in data:
+        r.append(point['r'])
+        te.append(point['te'])
+    print "Mean Turbulent Energy Loss: ", label, ":", np.mean(te)
+    plt.semilogy(r, te, 'o', label=label)
+
+if __name__ == "__main__":
+    radius = 0.05
+    cylinder_csv = csv.DictReader(open('../data/cylinder.csv', 'r'))
+    cylinder_ann = get_points_annulus(cylinder_csv, radius)
+    plot_turb(cylinder_ann, "Cylinder")
+    plt.xlabel("Radius (m)")
+    plt.ylabel("Energy Lost to Turbulence (J)")
+    plt.show()

### 2013-02-20 phys715/scripts/plot_turb_profile.py

@@ -1,0 +1,47 @@
+#!/usr/bin/python
+import csv
+import numpy as np
+import matplotlib.pyplot as plt
+
+def fmtpoint(point):
+    p = {'x':float(point['Points:0']), 'y':float(point['Points:1']),
+    'z':float(point['Points:2']), 'vx':float(point['Velocity:0']), 
+    'vy':float(point['Velocity:1']), 'vz':float(point['Velocity:2']), 
+    'te':float(point['TurbEner']), 'p':float(point['Pressure'])}
+    p['r'] = np.sqrt(p['x']*p['x'] + p['y']*p['y'])
+    return p
+
+def get_points_annulus(data, radius):
+    points = []
+    for point in data:
+        p = fmtpoint(point)
+        if p['r'] < radius:
+            points.append(p)
+    return points
+
+def plot_turb(data, label):
+    te = []
+    r = []
+    for point in data:
+        r.append(point['r'])
+        te.append(point['te'])
+    print "Mean Turbulent Energy Loss: ", label, ":", np.mean(te)
+    plt.plot(r, te, 'o', label=label)
+
+if __name__ == "__main__":
+    radius = 0.05
+    empty_csv = csv.DictReader(open('../data/empty.csv', 'r'))
+    cylinder_csv = csv.DictReader(open('../data/cylinder.csv', 'r'))
+    NACA5440_csv = csv.DictReader(open('../data/NACA5440.csv', 'r'))
+    NACA5420_csv = csv.DictReader(open('../data/NACA5420.csv', 'r'))
+    empty_ann = get_points_annulus(empty_csv, radius)
+    cylinder_ann = get_points_annulus(cylinder_csv, radius)
+    NACA5440_ann = get_points_annulus(NACA5440_csv, radius)
+    NACA5420_ann = get_points_annulus(NACA5420_csv, radius)
+    plot_turb(empty_ann, "Empty Box")
+    plot_turb(NACA5440_ann, "NACA5440")
+    plot_turb(NACA5420_ann, "NACA5420")
+    plt.xlabel("Radius (m)")
+    plt.ylabel("Energy Lost to Turbulence (J)")
+    plt.legend(loc='best')
+    plt.show()

### 2013-02-20 phys715/scripts/plot_velocity_cylinder.py

@@ -1,0 +1,42 @@
+#!/usr/bin/python
+import csv
+import numpy as np
+import matplotlib.pyplot as plt
+
+def fmtpoint(point):
+    p = {'x':float(point['Points:0']), 'y':float(point['Points:1']),
+    'z':float(point['Points:2']), 'vx':float(point['Velocity:0']), 
+    'vy':float(point['Velocity:1']), 'vz':float(point['Velocity:2']), 
+    'te':float(point['TurbEner']), 'p':float(point['Pressure'])}
+    p['r'] = np.sqrt(p['x']*p['x'] + p['y']*p['y'])
+    return p
+
+def get_points_annulus(data, radius):
+    points = []
+    for point in data:
+        p = fmtpoint(point)
+        if p['r'] < radius:
+            points.append(p)
+    return points
+
+def plot_vz(data, label):
+    vz = []
+    r = []
+    for point in data:
+        r.append(point['r'])
+        vz.append(-1.0*point['vz'])
+    print "Mean Velocity: ", label, ":", np.mean(vz)
+    print "RMS Velocity: ", label, ":", np.std(vz)
+    plt.semilogy(r, vz, 'o', label=label)
+
+if __name__ == "__main__":
+    radius = 0.05
+    empty_csv = csv.DictReader(open('../data/empty.csv', 'r'))
+    cylinder_csv = csv.DictReader(open('../data/cylinder.csv', 'r'))
+    NACA5440_csv = csv.DictReader(open('../data/NACA5440.csv', 'r'))
+    NACA5420_csv = csv.DictReader(open('../data/NACA5420.csv', 'r'))
+    cylinder_ann = get_points_annulus(cylinder_csv, radius)
+    plot_vz(cylinder_ann, "Empty Box")
+    plt.xlabel("Radius (m)")
+    plt.ylabel("Flow Velocity (m/s)")
+    plt.show()

### 2013-02-20 phys715/scripts/plot_velocity_profile.py

@@ -1,0 +1,49 @@
+#!/usr/bin/python
+import csv
+import numpy as np
+import matplotlib.pyplot as plt
+
+def fmtpoint(point):
+    p = {'x':float(point['Points:0']), 'y':float(point['Points:1']),
+    'z':float(point['Points:2']), 'vx':float(point['Velocity:0']), 
+    'vy':float(point['Velocity:1']), 'vz':float(point['Velocity:2']), 
+    'te':float(point['TurbEner']), 'p':float(point['Pressure'])}
+    p['r'] = np.sqrt(p['x']*p['x'] + p['y']*p['y'])
+    return p
+
+def get_points_annulus(data, radius):
+    points = []
+    for point in data:
+        p = fmtpoint(point)
+        if p['r'] < radius:
+            points.append(p)
+    return points
+
+def plot_vz(data, label):
+    vz = []
+    r = []
+    for point in data:
+        r.append(point['r'])
+        vz.append(-1.0*point['vz'])
+    print "Mean Velocity: ", label, ":", np.mean(vz)
+    print "RMS Velocity: ", label, ":", np.std(vz)
+    plt.plot(r, vz, 'o', label=label)
+
+if __name__ == "__main__":
+    radius = 0.05
+    empty_csv = csv.DictReader(open('../data/empty.csv', 'r'))
+    cylinder_csv = csv.DictReader(open('../data/cylinder.csv', 'r'))
+    NACA5440_csv = csv.DictReader(open('../data/NACA5440.csv', 'r'))
+    NACA5420_csv = csv.DictReader(open('../data/NACA5420.csv', 'r'))
+    empty_ann = get_points_annulus(empty_csv, radius)
+    cylinder_ann = get_points_annulus(cylinder_csv, radius)
+    NACA5440_ann = get_points_annulus(NACA5440_csv, radius)
+    NACA5420_ann = get_points_annulus(NACA5420_csv, radius)
+    plot_vz(empty_ann, "Empty Box")
+    plot_vz(NACA5440_ann, "NACA5440")
+    plot_vz(NACA5420_ann, "NACA5420")
+    plt.ylim(0, 30)
+    plt.xlabel("Radius (m)")
+    plt.ylabel("Flow Velocity (m/s)")
+    plt.legend(loc='best')
+    plt.show()

### 2013-02-20 phys715/scripts/plot_vorticity_profile.py

@@ -1,0 +1,48 @@
+#!/usr/bin/python
+import csv
+import numpy as np
+import matplotlib.pyplot as plt
+
+def fmtpoint(point):
+    p = {'x':float(point['Points:0']), 'y':float(point['Points:1']),
+    'z':float(point['Points:2']), 'vx':float(point['Velocity:0']), 
+    'vy':float(point['Velocity:1']), 'vz':float(point['Velocity:2']), 
+    'te':float(point['TurbEner']), 'p':float(point['Pressure'])}
+    p['r'] = np.sqrt(p['x']*p['x'] + p['y']*p['y'])
+    return p
+
+def get_points_annulus(data, radius):
+    points = []
+    for point in data:
+        p = fmtpoint(point)
+        if p['r'] < radius:
+            points.append(p)
+    return points
+
+def plot_vz(data, label):
+    vtan = []
+    r = []
+    for point in data:
+        r.append(point['r'])
+        vtan.append(np.sqrt(point['vx']*point['vx']+point['vy']*point['vy']))
+    r = np.array(r)
+    vtan = np.array(vtan)
+    plt.plot(r, 2*vtan/r, 'o', label=label)
+
+if __name__ == "__main__":
+    radius = 0.05
+    empty_csv = csv.DictReader(open('../data/empty.csv', 'r'))
+    cylinder_csv = csv.DictReader(open('../data/cylinder.csv', 'r'))
+    NACA5440_csv = csv.DictReader(open('../data/NACA5440.csv', 'r'))
+    NACA5420_csv = csv.DictReader(open('../data/NACA5420.csv', 'r'))
+    empty_ann = get_points_annulus(empty_csv, radius)
+    cylinder_ann = get_points_annulus(cylinder_csv, radius)
+    NACA5440_ann = get_points_annulus(NACA5440_csv, radius)
+    NACA5420_ann = get_points_annulus(NACA5420_csv, radius)
+    plot_vz(empty_ann, "Empty Box")
+    plot_vz(NACA5440_ann, "NACA5440")
+    plot_vz(NACA5420_ann, "NACA5420")
+    plt.xlabel("Radius (m)")
+    plt.ylabel("Vorticity $(s^{-1})$")
+    plt.legend(loc='best')
+    plt.show()

### 2013-02-20 phys715/simulation/AIRFOIL/CYLINDER/SRC/REFERENCE/base/cs_user_periodicity.c

@@ -1,0 +1,263 @@
+/*============================================================================
+ * Define (conforming or non-conforming) periodicity.
+ *============================================================================*/
+
+/* Code_Saturne version 2.1.4 */
+
+/*
+  This file is part of Code_Saturne, a general-purpose CFD tool.
+
+  Copyright (C) 1998-2011 EDF S.A.
+
+  This program is free software; you can redistribute it and/or modify it under
+  the terms of the GNU General Public License as published by the Free Software
+  Foundation; either version 2 of the License, or (at your option) any later
+  version.
+
+  This program is distributed in the hope that it will be useful, but WITHOUT
+  ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+  FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+  details.
+
+  You should have received a copy of the GNU General Public License along with
+  this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+  Street, Fifth Floor, Boston, MA 02110-1301, USA.
+*/
+
+/*----------------------------------------------------------------------------*/
+
+#if defined(HAVE_CONFIG_H)
+#include "cs_config.h"
+#endif
+
+/*----------------------------------------------------------------------------
+ * Standard C library headers
+ *----------------------------------------------------------------------------*/
+
+/*----------------------------------------------------------------------------
+ * BFT library headers
+ *----------------------------------------------------------------------------*/
+
+/*----------------------------------------------------------------------------
+ * FVM library headers
+ *----------------------------------------------------------------------------*/
+
+/*----------------------------------------------------------------------------
+ *  Local headers
+ *----------------------------------------------------------------------------*/
+
+#include "cs_base.h"
+#include "cs_join.h"
+#include "cs_join_perio.h"
+
+/*----------------------------------------------------------------------------
+ *  Header for the current file
+ *----------------------------------------------------------------------------*/
+
+#include "cs_prototypes.h"
+
+/*----------------------------------------------------------------------------*/
+
+BEGIN_C_DECLS
+
+/*============================================================================
+ * User function definitions
+ *============================================================================*/
+
+/*----------------------------------------------------------------------------
+ * Define periodic faces.
+ *
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/CYLINDER/SRC/REFERENCE/base/cs_user_solver.c

@@ -1,0 +1,272 @@
+/*============================================================================
+ * User solver
+ *============================================================================*/
+
+/* Code_Saturne version 2.1.4 */
+
+/*
+  This file is part of Code_Saturne, a general-purpose CFD tool.
+
+  Copyright (C) 1998-2011 EDF S.A.
+
+  This program is free software; you can redistribute it and/or modify it under
+  the terms of the GNU General Public License as published by the Free Software
+  Foundation; either version 2 of the License, or (at your option) any later
+  version.
+
+  This program is distributed in the hope that it will be useful, but WITHOUT
+  ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+  FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+  details.
+
+  You should have received a copy of the GNU General Public License along with
+  this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+  Street, Fifth Floor, Boston, MA 02110-1301, USA.
+*/
+
+/*----------------------------------------------------------------------------*/
+
+#if defined(HAVE_CONFIG_H)
+#include "cs_config.h"
+#endif
+
+/*----------------------------------------------------------------------------
+ * Standard C library headers
+ *----------------------------------------------------------------------------*/
+
+#include <assert.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <string.h>
+
+/*----------------------------------------------------------------------------
+ * BFT library headers
+ *----------------------------------------------------------------------------*/
+
+#include "bft_error.h"
+#include "bft_mem.h"
+#include "bft_printf.h"
+
+/*----------------------------------------------------------------------------
+ * FVM library headers
+ *----------------------------------------------------------------------------*/
+
+#include "fvm_defs.h"
+
+/*----------------------------------------------------------------------------
+ *  Local headers
+ *----------------------------------------------------------------------------*/
+
+#include "cs_base.h"
+#include "cs_mesh.h"
+#include "cs_mesh_quantities.h"
+#include "cs_post.h"
+#include "cs_restart.h"
+#include "cs_time_plot.h"
+
+/*----------------------------------------------------------------------------
+ *  Header for the current file
+ *----------------------------------------------------------------------------*/
+
+#include "cs_prototypes.h"
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/CYLINDER/SRC/REFERENCE/base/usclim.f90

@@ -1,0 +1,843 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usclim &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   icodcl , itrifb , itypfb ,                                     &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  , rcodcl )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Fill boundary conditions arrays (icodcl, rcodcl) for unknown variables.
+
+
+! Introduction
+! ============
+
+! Here one defines boundary conditions on a per-face basis.
+
+! Boundary faces may be identified using the 'getfbr' subroutine.
+
+!  getfbr(string, nelts, eltlst):
+!  - string is a user-supplied character string containing selection criteria;
+!  - nelts is set by the subroutine. It is an integer value corresponding to
+!    the number of boundary faces verifying the selection criteria;
+!  - lstelt is set by the subroutine. It is an integer array of size nelts
+!    containing the list of boundary faces verifying the selection criteria.
+
+!  string may contain:
+!  - references to colors (ex.: 1, 8, 26, ...)
+!  - references to groups (ex.: inlet, group1, ...)
+!  - geometric criteria (ex. x < 0.1, y >= 0.25, ...)
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/CYLINDER/SRC/REFERENCE/base/usiniv.f90

@@ -1,0 +1,199 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usiniv &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   dt     , rtp    , propce , propfa , propfb , coefa  , coefb  )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Initialize variables
+
+! This subroutine is called at beginning of the computation
+! (restart or not) before the loop time step
+
+! This subroutine enables to initialize or modify (for restart)
+!     unkown variables and time step values
+
+! rom and viscl values are equal to ro0 and viscl0 or initialize
+! by reading the restart file
+! viscls and cp variables (when there are defined) have no value
+! excepted if they are read from a restart file
+
+! Physical quantities are defined in the following arrays:
+!  propce (physical quantities defined at cell center),
+!  propfa (physical quantities defined at interior face center),
+!  propfa (physical quantities defined at border face center).
+!
+! Examples:
+!  propce(iel, ipproc(irom  )) means rom  (iel)
+!  propce(iel, ipproc(iviscl)) means viscl(iel)
+!  propce(iel, ipproc(icp   )) means cp   (iel)
+!  propce(iel, ipproc(ivisls(iscal))) means visls(iel, iscal)
+!  propfa(ifac, ipprof(ifluma(ivar))) means flumas(ifac, ivar)
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/CYLINDER/SRC/REFERENCE/base/usvima.f90

@@ -1,0 +1,164 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usvima &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  ,                                              &
+   viscmx , viscmy , viscmz )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine dedicated the use of ALE (Arbitrary Lagrangian Eulerian Method) :
+!                 fills mesh viscosity arrays.
+
+
+!    This subroutine is called at the beginning of each time step.
+
+!    Here one can modify mesh viscosity value to prevent cells and nodes
+!    from huge displacements in awkward areas, such as boundary layer for example.
+
+!    IF variable IORTVM = 0, mesh viscosity modeling is isotropic therefore VISCMX
+!    array only needs to be filled.
+!    IF variable IORTVM = 1, mesh viscosity modeling is orthotropic therefore
+!    all arrays VISCMX, VISCMY and VISCMZ need to be filled.
+
+!    Note that VISCMX, VISCMY and VISCMZ arrays are initialized at the first time step to the value of 1.
+
+! Cells identification
+! ====================
+
+! Cells may be identified using the 'getcel' subroutine.
+! The syntax of this subroutine is described in the 'usclim' subroutine,
+! but a more thorough description can be found in the user guide.
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/CYLINDER/SRC/REFERENCE/cogz/usd3p1.f90

@@ -1,0 +1,186 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usd3p1
+!================
+
+
+!===============================================================================
+!  Features of this subroutine:
+!  ----------------------------
+!  1. Variable Output
+!     a. Transported Variables
+!     b. Variables of State; User definied Variables
+!
+!  2. Additional Calculation Options
+!     a. Density Relaxation
+!
+!  3. Physical Constants
+!     a.Dynamic Diffusion Coefficient
+!===============================================================================
+
+!===============================================================================
+! Module files
+!===============================================================================
+
+use paramx
+use dimens
+use numvar
+use optcal
+use cstphy
+use entsor
+use cstnum
+use parall
+use period
+use ppppar
+use ppthch
+use coincl
+use cpincl
+use ppincl
+use radiat
+
+!===============================================================================
+
+implicit none
+
+integer          ipp
+
+!===============================================================================
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/CYLINDER/SRC/REFERENCE/cogz/usebu1.f90

@@ -1,0 +1,193 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usebu1
+
+!===============================================================================
+!  PURPOSE:
+!  --------
+!  1. Variable Output
+!     a. Transported Variables
+!     b. Variables of State; User definied Variables
+!
+!  2. Additional Calculation Options
+!     a. Density Relaxation
+!
+!  3. Physical Constants
+!     a.Dynamic Diffusion Coefficient
+!===============================================================================
+
+!===============================================================================
+! Module files
+!===============================================================================
+
+use paramx
+use dimens
+use numvar
+use optcal
+use cstphy
+use entsor
+use cstnum
+use parall
+use period
+use ppppar
+use ppthch
+use coincl
+use cpincl
+use ppincl
+use radiat
+
+!===============================================================================
+
+implicit none
+
+integer          ipp
+
+!===============================================================================
+!===============================================================================
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/CYLINDER/SRC/REFERENCE/cogz/usebuc.f90

@@ -1,0 +1,693 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usebuc &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   icodcl , itrifb , itypfb , izfppp ,                            &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  , rcodcl )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Fill boundary conditions arrays (icodcl, rcodcl)
+!    for unknown variables.
+
+
+! Introduction
+! ============
+
+! Here we define boundary conditions on a per-face basis.
+
+! Boundary faces may be identified using the 'getfbr' subroutine.
+
+!  getfbr(string, nelts, eltlst) :
+!  - string is a user-supplied character string containing
+!    selection criteria;
+!  - nelts is set by the subroutine. It is an integer value
+!    corresponding to the number of boundary faces verifying the
+!    selection criteria;
+!  - lstelt is set by the subroutine. It is an integer array of
+!    size nelts containing the list of boundary faces verifying
+!    the selection criteria.
+
+!  string may contain:
+!  - references to colors (ex.: 1, 8, 26, ...
+!  - references to groups (ex.: inlet, group1, ...)
+!  - geometric criteria (ex. x < 0.1, y >= 0.25, ...)
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/CYLINDER/SRC/REFERENCE/cogz/uslwcc.f90

@@ -1,0 +1,693 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uslwcc &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   icodcl , itrifb , itypfb , izfppp ,                            &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  , rcodcl )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Fill boundary conditions arrays (icodcl, rcodcl)
+!    for unknown variables.
+
+
+! Introduction
+! ============
+
+! Here we define boundary conditions on a per-face basis.
+
+! Boundary faces may be identified using the 'getfbr' subroutine.
+
+!  getfbr(string, nelts, eltlst) :
+!  - string is a user-supplied character string containing
+!    selection criteria;
+!  - nelts is set by the subroutine. It is an integer value
+!    corresponding to the number of boundary faces verifying the
+!    selection criteria;
+!  - lstelt is set by the subroutine. It is an integer array of
+!    size nelts containing the list of boundary faces verifying
+!    the selection criteria.
+
+!  string may contain:
+!  - references to colors (ex.: 1, 8, 26, ...
+!  - references to groups (ex.: inlet, group1, ...)
+!  - geometric criteria (ex. x < 0.1, y >= 0.25, ...)
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/CYLINDER/SRC/REFERENCE/cplv/uscpiv.f90

@@ -1,0 +1,423 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uscpiv &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   dt     , rtp    , propce , propfa , propfb , coefa  , coefb  )
+
+!===============================================================================
+! Purpose:
+! --------
+
+! Initialisation of transported variables for extended physics :
+!  pulverised coal combustion
+!   similar to USINIV
+!
+! This routine is called at the beginning of every computation
+!  (new or continuation) before the time loop
+!
+! This routine initialize or modify (if continuation)
+!  values of transported variables and of the time step
+!
+! The exemple is ... default value
+
+!
+! Physical properties are stored in PROPCE(cell center)
+!  PROPFA(inner face) and PROPFB(boundary face)
+!  e.g.
+!  PROPCE(IEL, IPPROC(IROM  )) is ROM(IEL) mean density kg/m3
+!  PROPFA(IFAC,IPPROF(IFLUMA(IVAR ))) is FLUMAS(IFAC,IVAR) convective flux
+!                                                        of variable IVAR
+!  PROPFB(......                      .................................
+!
+! Physical properties (ROM, VISCL, CP ...) are computed in PPPHYV
+!  not to be modified here
+!
+!   All cells can be identified by using the subroutine 'getcel'.
+!    Syntax of getcel:
+!     getcel(string, nelts, eltlst) :
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/CYLINDER/SRC/REFERENCE/cplv/uscpl1.f90

@@ -1,0 +1,239 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uscpl1
+!================
+
+
+!===============================================================================
+!  FONCTION  :
+!  ---------
+
+
+!   SOUS-PROGRAMME DU MODULE LAGRANGIEN COUPLE CHARBON PULVERISE :
+!   --------------------------------------------------------------
+
+!    ROUTINE UTILISATEUR POUR PHYSIQUE PARTICULIERE
+
+!      COMBUSTION EULERIENNE DE CHARBON PULVERISE ET
+!      TRANSPORT LAGRANGIEN DES PARTICULES DE CHARBON
+
+!    ROUTINE UTILISATEUR POUR ENTREE DES PARAMETRES DE CALCUL
+!      (COMMONS)
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+!    nom           !type!mode !                   role                         !
+!__________________!____!_____!________________________________________________!
+!__________________!____!_____!________________________________________________!
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/CYLINDER/SRC/REFERENCE/elec/uselcl.f90

@@ -1,0 +1,688 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uselcl &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   icodcl , itrifb , itypfb , izfppp ,                            &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  , rcodcl )
+
+!===============================================================================
+! Purpose
+! --------
+!
+!    User subroutine
+!
+!    THIS ROUTINE IS UNAVOIDABLE
+!    ===========================
+!
+!    Fill boundary conditions arrays (icodcl, rcodcl) for variables
+!    used in the electric modules of the code
+!    (Joule effect by direct conduction, Electric arc and ionic mobility).
+!
+!    The variable are the standart one (enthalpy, velocity )and the "electric variables".
+!
+!    The "electric" variable are :
+!     - at first and always the electric potential (real component in the case of complex potential)
+!     - in option you could have imaginary component of the electrical potential
+!       (Joule effect by direct conduction)
+!
+!     - 3 components of the vector potential A (for Electric arc module)
+!
+!
+!
+! Introduction
+! ============
+
+! Here one defines boundary conditions on a per-face basis.
+
+! Boundary faces may be identified using the 'getfbr' subroutine.
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/CYLINDER/SRC/REFERENCE/elec/uselrc.f90

@@ -1,0 +1,681 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uselrc &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   dt     , rtpa   , rtp    , propce , propfa , propfb ,          &
+   coefa  , coefb  )
+
+!===============================================================================
+! FONCTION :
+! ----------
+
+! ROUTINE PHYSIQUE PARTICULIERE POUR LE MODULE ELECTRIQUE
+
+!             CALCULS DU COEFFICIENT DE RECALAGE
+!               POUR LES VARIABLES ELECTIQUES
+!             RECALAGE DES VARIABLES ELECTRIQUES
+!               EN FONCTION DE CE COEFFICIENT
+
+!-------------------------------------------------------------------------------
+!ARGU                             ARGUMENTS
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/CYLINDER/SRC/REFERENCE/lagr/uslaen.f90

@@ -1,0 +1,329 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uslaen &
+!================
+
+ ( nvar   , nscal  , nvlsta ,                                     &
+   ivarl  , ivarl1 , ivarlm , iflu   , ilpd1  , icla   ,          &
+   dt     , rtpa   , rtp    , propce , propfa , propfb ,          &
+   coefa  , coefb  , statis , stativ , tracel )
+
+!===============================================================================
+! Purpose:
+! --------
+
+!   Subroutine of the Lagrangian particle-tracking module :
+!   -------------------------------------------------------
+
+!    User subroutine (non-mandatory intervention)
+
+!    For the writing of the listing and the post-processing:
+!    Average of the Lagrangian volume statistical variables
+!    Possible intervention of the user.
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
+! nvar             ! i  ! <-- ! total number of variables                      !
+! nscal            ! i  ! <-- ! total number of scalars                        !
+! nvlsta           ! i  ! <-- ! nb of Lagrangian statistical variables         !
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/CYLINDER/SRC/REFERENCE/lagr/uslafe.f90

@@ -1,0 +1,205 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uslafe &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   nbpmax , nvp    , nvp1   , nvep   , nivep  ,                   &
+   ntersl , nvlsta , nvisbr ,                                     &
+   itepa  , ibord  ,                                              &
+   dt     , rtpa   , rtp    , propce , propfa , propfb ,          &
+   ettp   , ettpa  , tepa   , statis , stativ ,                   &
+   taup   , tlag   , piil   ,                                     &
+   tsuf   , tsup   , bx     , tsfext ,                            &
+   vagaus , gradpr , gradvf ,                                     &
+   romp   , fextla )
+
+!===============================================================================
+! Purpose:
+! ----------
+
+!   Subroutine of the Lagrangian particle-tracking module:
+!   -------------------------------------
+
+!    User subroutine (non-mandatory intervention)
+
+!    Management of an external force field acting on the particles
+!    It must be prescribed in every cell and be homogeneous to gravity (m/s^2)
+!
+!    By default gravity and drag force are the only forces acting on the particles
+!    (the gravity components gx gy gz are assigned in usini1)
+!
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/CYLINDER/SRC/REFERENCE/rayt/usray3.f90

@@ -1,0 +1,240 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usray3 &
+!================
+
+ ( nvar   , nscal  , iappel ,                                     &
+   itypfb ,                                                       &
+   izfrdp ,                                                       &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   ck     )
+
+!===============================================================================
+! Purpose:
+! --------
+
+! Absorption coefficient for radiative module
+! ----------------------
+
+! It is necessary to define the value of the fluid's absorption
+! coefficient Ck.
+
+! For a transparent medium, the coefficient should be set to 0.d0.
+
+! In the case of the P-1 model, we check that the optical length is at
+! least of the order of 1.
+
+! Caution:
+! ========
+!   For specific physics (Combustion, coal, ...),
+
+!   it is Forbidden to define the absorption coefficient here.
+!         =========
+
+!   See subroutine ppcabs.
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
+! nvar             ! i  ! <-- ! total number of variables                      !
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/atmo/usatcl.f90

@@ -1,0 +1,397 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usatcl &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   icodcl , itrifb , itypfb , izfppp ,                            &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  , rcodcl )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine for the atmospheric module.
+
+!    Fill boundary conditions arrays (icodcl, rcodcl) for unknown variables.
+
+!    (similar to usclim.f90)
+
+
+! Introduction
+! ============
+
+! Here one defines boundary conditions on a per-face basis.
+
+! Boundary faces may be identified using the 'getfbr' subroutine.
+! The syntax of this subroutine is described in the 'usclim' subroutine,
+! but a more thorough description can be found in the user guide.
+
+
+! Boundary condition types
+! ========================
+
+! Boundary conditions setup for standard variables (pressure, velocity,
+! turbulence, scalars) is described precisely in the 'usclim' subroutine.
+
+! Detailed explanation will be found in the theory guide.
+
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/atmo/usati1.f90

@@ -1,0 +1,89 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usati1
+!================
+
+
+!===============================================================================
+! Purpose:
+! --------
+
+! Initialize non-standard calculation options for the atmospheric version.
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
+!__________________!____!_____!________________________________________________!
+
+!     Type: i (integer), r (real), s (string), a (array), l (logical),
+!           and composite types (ex: ra real array)
+!     mode: <-- input, --> output, <-> modifies data, --- work array
+!===============================================================================
+
+!===============================================================================
+! Module files
+!===============================================================================
+
+use paramx
+use dimens
+use numvar
+use optcal
+use cstphy
+use entsor
+use cstnum
+use ppppar
+use atincl
+
+!===============================================================================
+
+implicit none
+
+!===============================================================================
+
+
+
+!===============================================================================
+! 1. Example of calculation options to modify
+!===============================================================================
+
+! Reading the meteo file
+
+imeteo = 1
+
+! Option for variable density and viscosity
+
+!   For each phase
+
+irovar = 0
+ivivar = 0
+
+!----
+! End
+!----
+
+return
+end subroutine

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/base/cs_user_saturne_coupling.c

@@ -1,0 +1,122 @@
+/*============================================================================
+ * Define conjuguate heat transfer couplings with the SYRTHES code
+ *============================================================================*/
+
+/* Code_Saturne version 2.1.4 */
+
+/*
+  This file is part of Code_Saturne, a general-purpose CFD tool.
+
+  Copyright (C) 1998-2011 EDF S.A.
+
+  This program is free software; you can redistribute it and/or modify it under
+  the terms of the GNU General Public License as published by the Free Software
+  Foundation; either version 2 of the License, or (at your option) any later
+  version.
+
+  This program is distributed in the hope that it will be useful, but WITHOUT
+  ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+  FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+  details.
+
+  You should have received a copy of the GNU General Public License along with
+  this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+  Street, Fifth Floor, Boston, MA 02110-1301, USA.
+*/
+
+/*----------------------------------------------------------------------------*/
+
+#if defined(HAVE_CONFIG_H)
+#include "cs_config.h"
+#endif
+
+/*----------------------------------------------------------------------------
+ * Standard C library headers
+ *----------------------------------------------------------------------------*/
+
+/*----------------------------------------------------------------------------
+ * BFT library headers
+ *----------------------------------------------------------------------------*/
+
+/*----------------------------------------------------------------------------
+ * FVM library headers
+ *----------------------------------------------------------------------------*/
+
+/*----------------------------------------------------------------------------
+ *  Local headers
+ *----------------------------------------------------------------------------*/
+
+#include "cs_base.h"
+#include "cs_sat_coupling.h"
+
+/*----------------------------------------------------------------------------
+ *  Header for the current file
+ *----------------------------------------------------------------------------*/
+
+#include "cs_prototypes.h"
+
+/*----------------------------------------------------------------------------*/
+
+BEGIN_C_DECLS
+
+/*============================================================================
+ * User function definitions
+ *============================================================================*/
+
+/*----------------------------------------------------------------------------
+ * Define couplings with other instances of Code_Saturne.
+ *
+ * This is done by calling the cs_sat_coupling_define() function for each
+ * coupling to add.
+ *
+ * The arguments to cs_sat_coupling_define are:
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/base/usalcl.f90

@@ -1,0 +1,470 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usalcl &
+!================
+
+ ( itrale ,                                                       &
+   nvar   , nscal  ,                                              &
+   icodcl , itypfb , ialtyb , impale ,                            &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  , rcodcl , xyzno0 , depale )
+
+!===============================================================================
+! Purpose:
+! -------
+
+! --- User subroutine dedicated the use of ALE (Arbitrary Lagrangian Eulerian Method) :
+!                 Fills boundary conditions (ialtyb, icodcl, rcodcl) for mesh velocity.
+!                 This subroutine also enables one to fix displacement on nodes.
+
+!
+! Introduction
+! ============
+
+! Here one defines boundary conditions on a per-face basis.
+
+! Boundary faces may be identified using the 'getfbr' subroutine.
+! The syntax of this subroutine is described in 'usclim' subroutine,
+! but a more thorough description can be found in the user guide.
+
+! Boundary conditions setup for standard variables (pressure, velocity,
+! turbulence, scalars) is described precisely in 'usclim' subroutine.
+
+! Detailed explanation will be found in the theory guide.
+
+! Boundary condition types
+! ========================
+
+! Boundary conditions may be assigned in two ways.
+
+!
+!    For "standard" boundary conditions:
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/base/user_modules.f90

@@ -1,0 +1,93 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+! User-defined modules
+
+! This file is compiled before all other user Fortran files.
+! To ensure this, it must not be renamed.
+
+! The user may define an arbitrary number of modules here, even though
+! only one is defined in the example.
+
+!-------------------------------------------------------------------------------
+
+module user_module
+
+  ! Example: allocatable user arrays
+
+  integer,          dimension(:), allocatable :: iwork
+  double precision, dimension(:,:), allocatable :: rwork
+
+contains
+
+  !=============================================================================
+
+  ! Allocate arrays
+
+  subroutine init_user_module(ncel, ncelet)
+
+    ! Arguments
+
+    integer, intent(in) :: ncel, ncelet
+
+    ! Local variables
+
+    integer :: err = 0
+
+    if (.not.allocated(iwork)) then
+      allocate(iwork(ncelet), stat=err)
+    endif
+
+    if (err .eq. 0 .and. .not.allocated(rwork)) then
+      allocate(rwork(3, ncelet), stat=err)
+    endif
+
+    if (err /= 0) then
+      write (*, *) "Error allocating array."
+      call csexit(err)
+    endif
+
+    return
+
+  end subroutine init_user_module
+
+  !=============================================================================
+
+  ! Free related arrays
+
+  subroutine finalize_user_module
+
+    if (allocated(iwork)) then
+      deallocate(iwork)
+    endif
+
+    if (allocated(rwork)) then
+      deallocate(rwork)
+    endif
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/base/usphyv.f90

@@ -1,0 +1,731 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usphyv &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   ibrom  ,                                                       &
+   dt     , rtp    , rtpa   ,                                     &
+   propce , propfa , propfb ,                                     &
+   coefa  , coefb  )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Definition of physical variable laws.
+
+! Warning:
+! -------
+
+! It is forbidden to modify turbulent viscosity "visct" here
+!       =========
+!    (a specific subroutine is dedicated to that: usvist)
+
+
+! icp = 1 must have been specified
+!                ========================
+!    in usini1 if we wish to define a variable specific heat
+!    cp (otherwise: memory overwrite).
+
+
+! ivisls = 1 must have been specified
+!                   ========================
+!    in usini1 if we wish to define a variable viscosity
+!    viscls (otherwise: memory overwrite).
+
+
+! Notes:
+! -----
+
+! This routine is called at the beginning of each time step
+
+!    Thus, AT THE FIRST TIME STEP (non-restart case), the only
+!    values initialized before this call are those defined
+!      - in usini1 :
+!             . density    (initialized at ro0)
+!             . viscosity  (initialized at viscl0)
+!      - in usiniv :
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/base/usthht.f90

@@ -1,0 +1,194 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usthht &
+!================
+
+ ( mode   , enthal , temper  )
+
+!===============================================================================
+! FONCTION :
+! --------
+
+!    ROUTINE UTILISATEUR
+!    LOI ENTHALPIE   -> TEMPERATURE (MODE =  1)
+!    LOI TEMPERATURE -> ENTHALPIE   (MODE = -1)
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
+! mode             ! e  ! <-- !  -1 : t -> h  ;   1 : h -> t                   !
+! enthal           ! r  ! <-- ! enthalpie                                      !
+! temper           ! r  ! <-- ! temperature                                    !
+!__________________!____!_____!________________________________________________!
+
+!     Type: i (integer), r (real), s (string), a (array), l (logical),
+!           and composite types (ex: ra real array)
+!     mode: <-- input, --> output, <-> modifies data, --- work array
+!===============================================================================
+
+!===============================================================================
+! Module files
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/base/ustsnv.f90

@@ -1,0 +1,243 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine ustsnv &
+!================
+
+ ( nvar   , nscal  , ncepdp , ncesmp ,                            &
+   ivar   ,                                                       &
+   icepdc , icetsm , itypsm ,                                     &
+   dt     , rtpa   , propce , propfa , propfb ,                   &
+   coefa  , coefb  , ckupdc , smacel ,                            &
+   crvexp , crvimp )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Additional right-hand side source terms for velocity components equation
+!    (Navier-Stokes)
+
+!
+! Usage
+! -----
+! The routine is called for each velocity component. It is therefore necessary
+! to test the value of the variable ivar to separate the treatments of the
+! components iu, iv or iw.
+!
+! The additional source term is decomposed into an explicit part (crvexp) and
+! an implicit part (crvimp) that must be provided here.
+! The resulting equation solved by the code for a velocity component u is:
+!
+!  rho*volume*du/dt + .... = crvimp*u + crvexp
+!
+! Note that crvexp and crvimp are defined after the Finite Volume integration
+! over the cells, so they include the "volume" term. More precisely:
+!   - crvexp is expressed in kg.m/s2
+!   - crvimp is expressed in kg/s
+!
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/base/ustsv2.f90

@@ -1,0 +1,262 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine ustsv2 &
+!================
+
+ ( nvar   , nscal  , ncepdp , ncesmp ,                            &
+   ivar   ,                                                       &
+   icepdc , icetsm , itypsm ,                                     &
+   dt     , rtpa   , propce , propfa , propfb ,                   &
+   coefa  , coefb  , ckupdc , smacel , produc , gphigk ,          &
+   crvexp , crvimp )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Additional right-hand side source terms for the equations of phi and f_bar
+!    with the v2-f phi-model turbulence model (ITURB=50)
+!
+! Usage
+! -----
+! The routine is called for both phi and f_bar. It is therefore necessary
+! to test the value of the variable ivar to separate the treatments of the
+! ivar=iphi or ivar=ifb.
+!
+! The additional source term is decomposed into an explicit part (crvexp) and
+! an implicit part (crvimp) that must be provided here.
+! The resulting equation solved by the code are as follows:
+!
+! For f_bar (ivar=ifb):
+!  volume*div(grad(f_bar))= ( volume*f_bar + ..... + crvimp*f_bar + crvexp )/L^2
+!
+! For phi (ivar=iphi)
+!  rho*volume*d(phi)/dt + .... = crvimp*phi + crvexp
+
+!
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/base/usvort.f90

@@ -1,0 +1,483 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usvort &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   iappel ,                                                       &
+   dt     , rtpa   , propce , propfa , propfb ,                   &
+   coefa  , coefb  )
+
+!===============================================================================
+! FONCTION :
+! --------
+
+! METHODE DES VORTEX POUR LES CONDITIONS AUX LIMITES D'ENTREE
+!  EN L.E.S. :
+!  DEFINITION DES ENTREES AVEC VORTEX
+!  DEFINITION DES CARACTERISTIQUES DES VORTEX
+
+
+! Boundary faces identification
+! =============================
+
+! Boundary faces may be identified using the 'getfbr' subroutine.
+! The syntax of this subroutine is described in the 'usclim' subroutine,
+! but a more thorough description can be found in the user guide.
+
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/base/usvpst.f90

@@ -1,0 +1,856 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usvpst &
+!================
+
+ ( ipart  ,                                                       &
+   nvar   , nscal  , nvlsta ,                                     &
+   ncelps , nfacps , nfbrps ,                                     &
+   itypps ,                                                       &
+   lstcel , lstfac , lstfbr ,                                     &
+   dt     , rtpa   , rtp    , propce , propfa , propfb ,          &
+   coefa  , coefb  , statis ,                                     &
+   tracel , trafac , trafbr )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Output additional variables on a postprocessing mesh.
+
+! Several "automatic" postprocessing meshes may be defined:
+! - The volume mesh (ipart=-1) if 'ichrvl' = 1
+! - The boundary mesh (ipart=-2) if 'ichrbo' = 1
+! - SYRTHES coupling surface (ipart < -2) if 'ichrsy' = 1
+! - Cooling tower exchange zone meshes (ipart < -2) if 'ichrze' = 1
+!
+! Additional meshes (cells or faces) may also be defined through the GUI or
+! using the cs_user_postprocess_meshes() function from the
+! cs_user_postprocess.c file, (and possibly modified using 'usmpst').
+
+! This subroutine is called once for each post-processing mesh
+! (with a different value of 'ipart') for each time step at which output
+! on this mesh is active.
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/cfbl/uscfx2.f90

@@ -1,0 +1,124 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uscfx2
+!================
+
+
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Set options for viscosity and conductivity for compressible flow.
+
+!    In addition to options set in the user subroutine 'usini1' (or in
+!    the GUI): this subroutine allows to set switches to indicate if the
+!    volumetric viscosity and the conductivity are constants. If they are,
+!    the subroutines allows to set their values.
+
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+!    nom           !type!mode !                   role                         !
+!__________________!____!_____!________________________________________________!
+!__________________!____!_____!________________________________________________!
+
+
+!     Type: i (integer), r (real), s (string), a (array), l (logical),
+!           and composite types (ex: ra real array)
+!     mode: <-- input, --> output, <-> modifies data, --- work array
+!===============================================================================
+
+!===============================================================================
+! Module files
+!===============================================================================
+
+use paramx
+use dimens
+use numvar
+use optcal
+use cstphy
+use entsor
+use cstnum
+use ppppar
+use ppthch
+use ppincl
+
+!===============================================================================
+
+implicit none
+
+! Arguments
+
+! Local variables
+
+!===============================================================================
+
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/cogz/usd3pc.f90

@@ -1,0 +1,743 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usd3pc &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   icodcl , itrifb , itypfb , izfppp ,                            &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  , rcodcl )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Fill boundary conditions arrays (icodcl, rcodcl)
+!    for unknown variables.
+
+
+! Introduction
+! ============
+
+! Here we define boundary conditions on a per-face basis.
+
+! Boundary faces may be identified using the 'getfbr' subroutine.
+
+!  getfbr(string, nelts, eltlst) :
+!  - string is a user-supplied character string containing
+!    selection criteria;
+!  - nelts is set by the subroutine. It is an integer value
+!    corresponding to the number of boundary faces verifying the
+!    selection criteria;
+!  - lstelt is set by the subroutine. It is an integer array of
+!    size nelts containing the list of boundary faces verifying
+!    the selection criteria.
+
+!  string may contain:
+!  - references to colors (ex.: 1, 8, 26, ...
+!  - references to groups (ex.: inlet, group1, ...)
+!  - geometric criteria (ex. x < 0.1, y >= 0.25, ...)
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/cogz/usd3pi.f90

@@ -1,0 +1,265 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usd3pi &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   dt     , rtp    , propce , propfa , propfb , coefa  , coefb  )
+
+!===============================================================================
+! PURPOSE :
+! --------
+! Initialisation of the transported variables of the 3-point
+! chemistry combustion model. The latter ones are used to calculate
+! diffusion flame properties by applying detailed thermochemistry data.
+!
+! FEATURES:
+! --------
+! - This subroutine is called at the beginning of both a restart-calculation
+!   and a new calculation.
+! - The user is able to modify the initial conditions of the tranported
+!   variables.
+! - All variables of state deducible from the transported variables, as well as
+!   the detailed thermochemistry data (JANAF-table) are located in the array named
+!
+!   a) PROPCE (Properties in the cell center).
+!   b) PROPFA (Properties at internal faces).
+!   c) PROPFB (Properties at boundary faces).
+!
+!   Examples:
+!   PROPCE(IEL,IPPROC(IROM  )) =  IROM of cell IEL
+!   PROPCE(IEL,IPPROC(ICP   )) =  ICP  of cell IEL
+!
+!   PROPFA(IFAC,IPPROF(IFLUMA(IVAR )))=  FLUMAS of IVAR at the internal face IFAC
+!
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/cogz/uslwc1.f90

@@ -1,0 +1,270 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uslwc1
+
+
+!===============================================================================
+!  PURPOSE:
+!  --------
+!  1. Variable Output
+!     a. Transported Variables
+!     b. Variables of State; User definied Variables
+!
+!  2. Additional Calculation Options
+!     a. Density Relaxation
+!
+!  3. Physical Constants
+!     a.Dynamic Diffusion Coefficient
+!     b.Constants of the Libby-Williams Model
+!===============================================================================
+
+!===============================================================================
+! Module files
+!===============================================================================
+
+use paramx
+use dimens
+use numvar
+use optcal
+use cstphy
+use entsor
+use cstnum
+use parall
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/cplv/uscpi1.f90

@@ -1,0 +1,370 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uscpi1
+!================
+
+
+!===============================================================================
+!  PURPOSE   :
+!  ---------
+
+!  User's routine to control outing of variables for pulverised coal combustion
+!  (these parameters are in COMMON)
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
+!__________________!____!_____!________________________________________________!
+
+!     Type: i (integer), r (real), s (string), a (array), l (logical),
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/ctwr/usctcl.f90

@@ -1,0 +1,260 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usctcl &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   icodcl , itrifb , itypfb , izfppp ,                            &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  , rcodcl )
+
+!===============================================================================
+! FONCTION :
+! --------
+
+!    ROUTINE UTILISATEUR POUR PHYSIQUE PARTICULIERE
+!            MODELISATION AEROREFRIGERANTS
+!    REMPLISSAGE DU TABLEAU DE CONDITIONS AUX LIMITES
+!    (ICODCL,RCODCL) POUR LES VARIABLES INCONNUES
+!    PENDANT DE USCLIM.F
+
+
+
+!    CE SOUS PROGRAMME UTILISATEUR EST OBLIGATOIRE
+!    =============================================
+
+
+! Introduction
+! ============
+
+! Here one defines boundary conditions on a per-face basis.
+
+! Boundary faces may be identified using the 'getfbr' subroutine.
+! The syntax of this subroutine is described in the 'usclim' subroutine,
+! but a more thorough description can be found in the user guide.
+
+
+! Boundary condition types
+! ========================
+
+! Boundary conditions setup for standard variables (pressure, velocity,
+! turbulence, scalars) is described precisely in the 'usclim' subroutine.
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/ctwr/usctdz.f90

@@ -1,0 +1,113 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usctdz
+!================
+
+!===============================================================================
+! FONCTION :
+! --------
+
+! ROUTINE UTILISATEUR POUR LA DEFINITION DES ZONES D'ECHANGE
+! D'UN AEROREFRIGERANT
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
+!__________________!____!_____!________________________________________________!
+
+!     Type: i (integer), r (real), s (string), a (array), l (logical),
+!           and composite types (ex: ra real array)
+!     mode: <-- input, --> output, <-> modifies data, --- work array
+!===============================================================================
+
+!===============================================================================
+! Module files
+!===============================================================================
+
+use paramx
+use optcal
+use entsor
+use cstphy
+use parall
+use period
+use ppppar
+use ppthch
+use ppincl
+use ctincl
+use mesh
+
+!===============================================================================
+
+implicit none
+
+! Local variables
+
+integer          imzech,ntypze,idimze,neleze
+
+double precision teaueze,qeaueze,deltat
+double precision xap,xnp,surface,dgout
+
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/ctwr/uscti1.f90

@@ -1,0 +1,153 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uscti1
+!================
+
+
+!===============================================================================
+!  FONCTION  :
+!  ---------
+
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
+!__________________!____!_____!________________________________________________!
+
+!     Type: i (integer), r (real), s (string), a (array), l (logical),
+!           and composite types (ex: ra real array)
+!     mode: <-- input, --> output, <-> modifies data, --- work array
+!===============================================================================
+
+!===============================================================================
+! Module files
+!===============================================================================
+
+use paramx
+use dimens
+use numvar
+use optcal
+use cstphy
+use entsor
+use cstnum
+use parall
+use period
+use ppppar
+use ppthch
+use ppincl
+use ctincl
+
+!===============================================================================
+
+implicit none
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/elec/uselen.f90

@@ -1,0 +1,469 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uselen &
+!================
+
+ ( nummai ,                                                       &
+   nvar   , nscal  ,                                              &
+   ncelps , nfacps , nfbrps ,                                     &
+   lstcel , lstfac , lstfbr ,                                     &
+   dt     , rtpa   , rtp    , propce , propfa , propfb ,          &
+   coefa  , coefb  ,                                              &
+   tracel , trafac , trafbr )
+
+!===============================================================================
+! Purpose :
+! --------
+
+! For post-processing in electric module
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+!    nom           !type!mode !                   role                         !
+!__________________!____!_____!________________________________________________!
+! nummai           ! ec ! <-- ! numero du maillage post                        !
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/lagr/uslabo.f90

@@ -1,0 +1,987 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uslabo &
+!================
+
+ ( lndnod ,                                                       &
+   nvar   , nscal  ,                                              &
+   nbpmax , nvp    , nvp1   , nvep   , nivep  ,                   &
+   ntersl , nvlsta , nvisbr ,                                     &
+   kface  , nbpt   , isuivi ,                                     &
+   itypfb , itrifb , ifrlag , itepa  , indep  ,                   &
+   dt     , rtpa   , rtp    , propce , propfa , propfb ,          &
+   coefa  , coefb  ,                                              &
+   ettp   , ettpa  , tepa   , parbor , vitpar , vitflu , auxl   )
+
+!===============================================================================
+! Purpose:
+! --------
+!
+! User subroutine of the Lagrangian particle-tracking module:
+! -----------------------------------------------------------
+!
+! User subroutine (non-mandatory intervention)
+!
+! User subroutine managing the particle behavior during an interaction between
+! a particle and a boundary and recording the boundary statistics.
+!
+! The user does not need to modify this subroutine in the case of a standard use.
+! If he wishes to treat non-standard user-defined interactions, he needs to intervene
+! in sections 8 and 10.
+!
+! The interaction between a particle and a boundary face is treated with respect
+! to the information given by the user (value of iusclb per zone) in the subroutine uslag2.
+!
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/lagr/usladp.f90

@@ -1,0 +1,227 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usladp &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   nbpmax , nvp    , nvp1   , nvep   , nivep  ,                   &
+   ntersl , nvlsta , nvisbr ,                                     &
+   itepa  ,                                                       &
+   dt     , rtpa   , propce , propfa , propfb ,                   &
+   ettp   , ettpa  , tepa   , statis ,                            &
+   taup   , tlag   , piil   ,                                     &
+   vagaus , gradpr , gradvf ,                                     &
+   romp   ,                                                       &
+   dppar  , dnxpar , dnypar , dnzpar )
+
+!===============================================================================
+! Purpose:
+! ----------
+
+!   Subroutine of the Lagrangian particle-tracking module :
+!   -------------------------------------
+
+!    User subroutine (non-mandatory intervention)
+
+!    For each particle :
+!      - Computation of the wall-normal distance
+!      - Computation of the normal to the wall
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
+! nvar             ! i  ! <-- ! total number of variables                      !
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/lagr/uslag1.f90

@@ -1,0 +1,963 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uslag1
+!================
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine of the Lagrangian particle-tracking module:
+
+!    User subroutine for input of calculation parameters (Fortran commons).
+!    This parameters concern physical, numerical and post-processing options.
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
+!__________________!____!_____!________________________________________________!
+
+!     Type: i (integer), r (real), s (string), a (array), l (logical),
+!           and composite types (ex: ra real array)
+!     mode: <-- input, --> output, <-> modifies data, --- work array
+!===============================================================================
+
+!===============================================================================
+! Module files
+!===============================================================================
+
+use paramx
+use entsor
+use lagdim
+use lagpar
+use lagran
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/rayt/usray2.f90

@@ -1,0 +1,600 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usray2 &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   itypfb ,                                                       &
+   icodcl , izfrdp , isothp ,                                     &
+   tmin   , tmax   , tx     ,                                     &
+   dt     , rtp    , rtpa   , propce , propfa , propfb , rcodcl , &
+   coefa  , coefb  ,                                              &
+   tparop , qincid , hfcnvp , flcnvp ,                            &
+   xlamp  , epap   , epsp   , textp  , tintp  )
+
+!===============================================================================
+! Purpose:
+! --------
+
+! User subroutine for input of radiative transfer parameters: boundary conditions
+
+! Sketch of thermal flux in boundary wall
+
+
+!  Outside      Inside wall       Fluid domain
+!            |               |
+!            |               |
+!            |               |
+!            | EPSP Qincid<--|<----- Qincid             [Incident flux]
+!            |               |
+!            | [absorption]  |
+!            |               |
+!            |               |-----> (1-EPSP) Qincid    [reflexion]
+!            |               |
+!            |               |
+!            |               |                       4
+!            |               |-----> EPSP sigma Tparop  [emission]
+!            |               |
+!            |               |
+!            |               |
+!            | [conduction]  |     .....o Tfluide       [convection]
+!            |               |    .
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/EMPTY/SRC/REFERENCE/rayt/usray5.f90

@@ -1,0 +1,489 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usray5 &
+!================
+
+ ( nvar   , nscal  , iappel ,                                     &
+   itypfb ,                                                       &
+   izfrdp ,                                                       &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  ,                                              &
+   cofrua , cofrub ,                                              &
+   tparoi , qincid , flunet , xlam   , epa    , eps     ,  ck   )
+
+!===============================================================================
+!  Purpose:
+!  --------
+
+! User subroutine for input of radiative transfer parameters.
+
+! This subroutine is calle twice. The first time is for boundary conditions.
+! The second time is for the net radiation flux computation.
+
+
+!  1. Fisrt call (IAPPEL = 1)
+!  ==========================
+
+!    1.1 Boundary conditions fot the radiative intensity (DO model)
+!    --------------------------------------------------------------
+
+!       The array COFRUA store the intensity for each boundary faces,
+!         depending of the natur of the boundary (Dirichlet condition).
+!       The intensity of radiation is defined as the rate of emitted
+!         energy from unit surface area through unit solid angle.
+
+!       For example:
+
+
+! 1/ Gray wall: isotropic radiation field.
+!                                    4
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/base/cs_user_join.c

@@ -1,0 +1,199 @@
+/*============================================================================
+ * Define (conforming or non-conforming) mesh joinings.
+ *============================================================================*/
+
+/* Code_Saturne version 2.1.4 */
+
+/*
+  This file is part of Code_Saturne, a general-purpose CFD tool.
+
+  Copyright (C) 1998-2011 EDF S.A.
+
+  This program is free software; you can redistribute it and/or modify it under
+  the terms of the GNU General Public License as published by the Free Software
+  Foundation; either version 2 of the License, or (at your option) any later
+  version.
+
+  This program is distributed in the hope that it will be useful, but WITHOUT
+  ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+  FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+  details.
+
+  You should have received a copy of the GNU General Public License along with
+  this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+  Street, Fifth Floor, Boston, MA 02110-1301, USA.
+*/
+
+/*----------------------------------------------------------------------------*/
+
+#if defined(HAVE_CONFIG_H)
+#include "cs_config.h"
+#endif
+
+/*----------------------------------------------------------------------------
+ * Standard C library headers
+ *----------------------------------------------------------------------------*/
+
+/*----------------------------------------------------------------------------
+ * BFT library headers
+ *----------------------------------------------------------------------------*/
+
+/*----------------------------------------------------------------------------
+ * FVM library headers
+ *----------------------------------------------------------------------------*/
+
+/*----------------------------------------------------------------------------
+ *  Local headers
+ *----------------------------------------------------------------------------*/
+
+#include "cs_base.h"
+#include "cs_join.h"
+
+/*----------------------------------------------------------------------------
+ *  Header for the current file
+ *----------------------------------------------------------------------------*/
+
+#include "cs_prototypes.h"
+
+/*----------------------------------------------------------------------------*/
+
+BEGIN_C_DECLS
+
+/*============================================================================
+ * User function definitions
+ *============================================================================*/
+
+/*----------------------------------------------------------------------------
+ * Define mesh joinings.
+ *
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/base/cs_user_mesh_modify.c

@@ -1,0 +1,103 @@
+/*============================================================================
+ * User function for geometry and mesh modification.
+ *============================================================================*/
+
+/* Code_Saturne version 2.1.4 */
+
+/*
+  This file is part of Code_Saturne, a general-purpose CFD tool.
+
+  Copyright (C) 1998-2011 EDF S.A.
+
+  This program is free software; you can redistribute it and/or modify it under
+  the terms of the GNU General Public License as published by the Free Software
+  Foundation; either version 2 of the License, or (at your option) any later
+  version.
+
+  This program is distributed in the hope that it will be useful, but WITHOUT
+  ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+  FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+  details.
+
+  You should have received a copy of the GNU General Public License along with
+  this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+  Street, Fifth Floor, Boston, MA 02110-1301, USA.
+*/
+
+/*----------------------------------------------------------------------------*/
+
+#if defined(HAVE_CONFIG_H)
+#include "cs_config.h"
+#endif
+
+/*----------------------------------------------------------------------------
+ * Standard C library headers
+ *----------------------------------------------------------------------------*/
+
+/*----------------------------------------------------------------------------
+ * BFT library headers
+ *----------------------------------------------------------------------------*/
+
+/*----------------------------------------------------------------------------
+ * FVM library headers
+ *----------------------------------------------------------------------------*/
+
+/*----------------------------------------------------------------------------
+ *  Local headers
+ *----------------------------------------------------------------------------*/
+
+#include "cs_base.h"
+#include "cs_mesh.h"
+
+/*----------------------------------------------------------------------------
+ *  Header for the current file
+ *----------------------------------------------------------------------------*/
+
+#include "cs_prototypes.h"
+
+/*----------------------------------------------------------------------------*/
+
+BEGIN_C_DECLS
+
+/*============================================================================
+ * User function definitions
+ *============================================================================*/
+
+/*----------------------------------------------------------------------------
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/base/cs_user_postprocess.c

@@ -1,0 +1,583 @@
+/*============================================================================
+ * Define (conforming or non-conforming) mesh joinings.
+ *============================================================================*/
+
+/* Code_Saturne version 2.1.4 */
+
+/*
+  This file is part of Code_Saturne, a general-purpose CFD tool.
+
+  Copyright (C) 1998-2011 EDF S.A.
+
+  This program is free software; you can redistribute it and/or modify it under
+  the terms of the GNU General Public License as published by the Free Software
+  Foundation; either version 2 of the License, or (at your option) any later
+  version.
+
+  This program is distributed in the hope that it will be useful, but WITHOUT
+  ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+  FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+  details.
+
+  You should have received a copy of the GNU General Public License along with
+  this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+  Street, Fifth Floor, Boston, MA 02110-1301, USA.
+*/
+
+/*----------------------------------------------------------------------------*/
+
+#if defined(HAVE_CONFIG_H)
+#include "cs_config.h"
+#endif
+
+/*----------------------------------------------------------------------------
+ * Standard C library headers
+ *----------------------------------------------------------------------------*/
+
+/*----------------------------------------------------------------------------
+ * BFT library headers
+ *----------------------------------------------------------------------------*/
+
+#include "bft_mem.h"
+
+/*----------------------------------------------------------------------------
+ * FVM library headers
+ *----------------------------------------------------------------------------*/
+
+#include "fvm_writer.h"
+
+/*----------------------------------------------------------------------------
+ *  Local headers
+ *----------------------------------------------------------------------------*/
+
+#include "cs_base.h"
+#include "cs_mesh.h"
+#include "cs_selector.h"
+
+#include "cs_post.h"
+
+/*----------------------------------------------------------------------------
+ *  Header for the current file
+ *----------------------------------------------------------------------------*/
+
+#include "cs_prototypes.h"
+
+/*----------------------------------------------------------------------------*/
+
+BEGIN_C_DECLS
+
+/*============================================================================
+ * User function definitions
+ *============================================================================*/
+
+/*----------------------------------------------------------------------------
+ * Define post-processing writers.
+ *
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/base/cs_user_syrthes_coupling.c

@@ -1,0 +1,135 @@
+/*============================================================================
+ * Define conjuguate heat transfer couplings with the SYRTHES code
+ *============================================================================*/
+
+/* Code_Saturne version 2.1.4 */
+
+/*
+  This file is part of Code_Saturne, a general-purpose CFD tool.
+
+  Copyright (C) 1998-2011 EDF S.A.
+
+  This program is free software; you can redistribute it and/or modify it under
+  the terms of the GNU General Public License as published by the Free Software
+  Foundation; either version 2 of the License, or (at your option) any later
+  version.
+
+  This program is distributed in the hope that it will be useful, but WITHOUT
+  ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+  FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+  details.
+
+  You should have received a copy of the GNU General Public License along with
+  this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+  Street, Fifth Floor, Boston, MA 02110-1301, USA.
+*/
+
+/*----------------------------------------------------------------------------*/
+
+#if defined(HAVE_CONFIG_H)
+#include "cs_config.h"
+#endif
+
+/*----------------------------------------------------------------------------
+ * Standard C library headers
+ *----------------------------------------------------------------------------*/
+
+/*----------------------------------------------------------------------------
+ * BFT library headers
+ *----------------------------------------------------------------------------*/
+
+/*----------------------------------------------------------------------------
+ * FVM library headers
+ *----------------------------------------------------------------------------*/
+
+/*----------------------------------------------------------------------------
+ *  Local headers
+ *----------------------------------------------------------------------------*/
+
+#include "cs_base.h"
+#include "cs_syr_coupling.h"
+
+/*----------------------------------------------------------------------------
+ *  Header for the current file
+ *----------------------------------------------------------------------------*/
+
+#include "cs_prototypes.h"
+
+/*----------------------------------------------------------------------------*/
+
+BEGIN_C_DECLS
+
+/*============================================================================
+ * User function definitions
+ *============================================================================*/
+
+/*----------------------------------------------------------------------------
+ * Define couplings with SYRTHES code.
+ *
+ * This is done by calling the cs_syr_coupling_define() function for each
+ * coupling to add.
+ *
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/base/usalin.f90

@@ -1,0 +1,129 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usalin
+!================
+
+!===============================================================================
+!  Purpose :
+! --------
+
+! --- User subroutine dedicated to the use of ALE (Arbitrary Lagrangian Eulerian)
+!     method :
+!
+!          Here one defines parameters and input data dedicated to the use ALE
+!          method
+!
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
+!__________________!____!_____!________________________________________________!
+
+!     Type: i (integer), r (real), s (string), a (array), l (logical),
+!           and composite types (ex: ra real array)
+!     mode: <-- input, --> output, <-> modifies data, --- work array
+!===============================================================================
+
+!===============================================================================
+! Module files
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/base/ushist.f90

@@ -1,0 +1,322 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine ushist &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   dt     , rtpa   , rtp    , propce , propfa , propfb ,          &
+   coefa  , coefb  )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Non-standard monitoring point definition.
+
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
+! nvar             ! i  ! <-- ! total number of variables                      !
+! nscal            ! i  ! <-- ! total number of scalars                        !
+! dt(ncelet)       ! ra ! <-- ! time step (per cell)                           !
+! rtp, rtpa        ! ra ! <-- ! calculated variables at cell centers           !
+!  (ncelet, *)     !    !     !  (at current and previous time steps)          !
+! propce(ncelet, *)! ra ! <-- ! physical properties at cell centers            !
+! propfa(nfac, *)  ! ra ! <-- ! physical properties at interior face centers   !
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/base/usini1.f90

@@ -1,0 +1,1872 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+! Purpose:
+! -------
+
+! User subroutines for input of calculation parameters (Fortran commons).
+!   These subroutines are called in all cases.
+
+! If the Code_Saturne GUI is used, this file is not required (but may be
+!   used to override parameters entered through the GUI, and to set
+!   parameters not accessible through the GUI).
+
+! Several routines are present in the file, each destined to defined
+!   specific parameters.
+
+! To modify the default value of parameters which do not appear in the
+!   examples provided, code should be placed as follows:
+!   - usipsu   for numerical and physical options
+!   - usipes   for input-output related options
+
+! As a convention, "specific physics" defers to the following modules only:
+!   pulverized coal, gas combustion, electric arcs.
+
+!-------------------------------------------------------------------------------
+
+
+!===============================================================================
+
+
+subroutine usipph &
+!================
+
+ ( iihmpu, nfecra , iturb , icp , iverif )
+
+
+!===============================================================================
+! Purpose:
+! --------
+
+! User subroutine for input of parameters depending on the number of phases.
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/base/usproj.f90

@@ -1,0 +1,1565 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usproj &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   nbpmax , nvp    , nvep   , nivep  , ntersl , nvlsta , nvisbr , &
+   itepa  ,                                                       &
+   dt     , rtpa   , rtp    , propce , propfa , propfb ,          &
+   coefa  , coefb  ,                                              &
+   ettp   , ettpa  , tepa   , statis , stativ , tslagr , parbor )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Called at end of each time step, very general purpose
+!    (i.e. anything that does not have another dedicated user subroutine)
+
+
+! Several examples are given here:
+
+!  - compute a thermal balance
+!    (if needed, see note  below on adapting this to any scalar)
+
+!  - compute global efforts on a subset of faces
+
+!  - arbitrarily modify a calculation variable
+
+!  - extract a 1 d profile
+
+!  - print a moment
+
+!  - examples on using parallel utility functions
+
+! These examples are valid when using periodicity (iperio .gt. 0)
+! and in parallel (irangp .ge. 0).
+
+! The thermal balance compution also illustates a few other features,
+! including the required precautions in parallel or with periodicity):
+! - gradient calculation
+! - computation of a value depending on cells adjacent to a face
+!   (see synchronization of Dt and Cp)
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/base/ustske.f90

@@ -1,0 +1,240 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine ustske &
+!================
+
+ ( nvar   , nscal  , ncepdp , ncesmp ,                            &
+   icepdc , icetsm , itypsm ,                                     &
+   dt     , rtpa   , propce , propfa , propfb ,                   &
+   coefa  , coefb  , ckupdc , smacel , tinstk , divu   ,          &
+   crkexp , creexp , crkimp , creimp )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Additional right-hand side source terms for k and epsilon equations
+!    when using:
+!     - k-epsilon model (ITURB=20)
+!     - k-epsilon Linear Production model (ITURB=21)
+!     - v2-f phi-model (ITURB=50)
+!
+! Usage
+! -----
+!
+! The additional source term is decomposed into an explicit part (crkexp,creexp) and
+! an implicit part (crkimp,creimp) that must be provided here.
+! The resulting equations solved by the code are:
+!
+!  rho*volume*d(k)/dt   + .... = crkimp*k   + crkexp
+
+!  rho*volume*d(eps)/dt + .... = creimp*eps + creexp
+!
+! Note that crkexp, crkimp, creexp and creimp are defined after the Finite Volume
+! integration over the cells, so they include the "volume" term. More precisely:
+!   - crkexp is expressed in kg.m2/s3
+!   - creexp is expressed in kg.m2/s4
+!   - crkimp is expressed in kg/s
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/base/ustsns.f90

@@ -1,0 +1,243 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine ustsns &
+!================
+
+ ( nvar   , nscal  , ncepdp , ncesmp ,                            &
+   ivar   ,                                                       &
+   icepdc , icetsm , itypsm ,                                     &
+   dt     , rtpa   , propce , propfa , propfb ,                   &
+   coefa  , coefb  , ckupdc , smacel ,                            &
+   crvexp , crvimp )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Additional right-hand side source terms for velocity components equation
+!    (Navier-Stokes)
+
+!
+! Usage
+! -----
+! The routine is called for each velocity component. It is therefore necessary
+! to test the value of the variable ivar to separate the treatments of the
+! components iu, iv or iw.
+!
+! The additional source term is decomposed into an explicit part (crvexp) and
+! an implicit part (crvimp) that must be provided here.
+! The resulting equation solved by the code for a velocity component u is:
+!
+!  rho*volume*du/dt + .... = crvimp*u + crvexp
+!
+! Note that crvexp and crvimp are defined after the Finite Volume integration
+! over the cells, so they include the "volume" term. More precisely:
+!   - crvexp is expressed in kg.m/s2
+!   - crvimp is expressed in kg/s
+!
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/base/ustssc.f90

@@ -1,0 +1,339 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine ustssc &
+!================
+
+ ( nvar   , nscal  , ncepdp , ncesmp ,                            &
+   iscal  ,                                                       &
+   icepdc , icetsm , itypsm ,                                     &
+   dt     , rtpa   , rtp    , propce , propfa , propfb ,          &
+   coefa  , coefb  , ckupdc , smacel ,                            &
+   crvexp , crvimp )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Additional right-hand side source terms for scalar equations (user
+!     scalars and specific physics scalars).
+
+!
+! Usage
+! -----
+! The routine is called for each scalar, user or specific physisc. It is
+! therefore necessary to test the value of the scalar number iscal to separate
+! the treatments of the different scalars (if (iscal.eq.p) then ....).
+!
+! The additional source term is decomposed into an explicit part (crvexp) and
+! an implicit part (crvimp) that must be provided here.
+! The resulting equation solved by the code for a scalar f is:
+!
+!  rho*volume*df/dt + .... = crvimp*f + crvexp
+!
+!
+! Note that crvexp and crvimp are defined after the Finite Volume integration
+! over the cells, so they include the "volume" term. More precisely:
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/cfbl/uscfcl.f90

@@ -1,0 +1,645 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uscfcl &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   icodcl , itrifb , itypfb , izfppp ,                            &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  , rcodcl )
+
+!===============================================================================
+! Purpose:
+! --------
+
+!    ROUTINE UTILISATEUR
+!    REMPLISSAGE DU TABLEAU DE CONDITIONS AUX LIMITES
+!    (ICODCL,RCODCL) POUR LES VARIABLES INCONNUES
+
+
+
+!    CE SOUS PROGRAMME UTILISATEUR EST OBLIGATOIRE
+!    =============================================
+
+
+! Introduction
+! ============
+
+! Here one defines boundary conditions on a per-face basis.
+
+! Boundary faces may be identified using the 'getfbr' subroutine.
+! The syntax of this subroutine is described in the 'usclim' subroutine,
+! but a more thorough description can be found in the user guide.
+
+
+! Boundary condition types
+! ========================
+
+! Boundary conditions setup for standard variables (pressure, velocity,
+! turbulence, scalars) is described precisely in the 'usclim' subroutine.
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/cfbl/uscfth.f90

@@ -1,0 +1,1945 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uscfth &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   iccfth , imodif ,                                              &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  ,                                              &
+   sorti1 , sorti2 , gamagr , xmasmr )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Define thermodynamic laws (especially for the compressible flow scheme).
+
+!    This user subroutine is mandatory for the compressible flow scheme.
+
+
+! Introduction
+! ============
+
+! This user subroutine allows to define all physical properties and
+! variables, through the implementation of thermodynamic laws.
+
+
+! Avalable thermodynamic laws
+! ===========================
+
+!  1. Perfect gas (the molar mass 'xmasml' must be provided)
+!  2. Perfect gas with non constant Gamma (example to be adapted)
+!  3. Van Der Waals (not yet implemented)
+
+
+! Implemented calculations
+! ========================
+
+! This user subroutine implements the computation of several quantities.
+! Each calculation has to be explicitly implemented in the appropriate
+! section below (already done for perfect gas).
+
+
+! Selection of the quantity to return
+! ===================================
+
+! When calling the user subroutine, the integer 'iccfth' specifies which
+! calculation has to be performed (and which quantity has to be returned).
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/cogz/usebui.f90

@@ -1,0 +1,312 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usebui &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   dt     , rtp    , propce , propfa , propfb , coefa  , coefb  )
+
+!===============================================================================
+! PURPOSE :
+! --------
+! Initialisation of the transported variables of EBU combustion model.
+! The latter ones are used to calculate premixed flame properties
+! by applying detailed thermochemistry data.
+!
+! FEATURES:
+! --------
+! - This subroutine is called at the beginning of both a restart-calculation
+!   and a new calculation.
+! - The user is able to modify the initial conditions of the tranported
+!   variables.
+! - All variables of state deducible from the transported variables, as well as
+!   the detailed thermochemistry data (JANAF-table) are located in the array named
+!
+!   a) PROPCE (Properties in the cell center).
+!   b) PROPFA (Properties at internal faces).
+!   c) PROPFB (Properties at boundary faces).
+!
+!   Examples:
+!   PROPCE(IEL,IPPROC(IROM  )) =  IROM of cell IEL
+!   PROPCE(IEL,IPPROC(ICP   )) =  ICP  of cell IEL
+!
+!   PROPFA(IFAC,IPPROF(IFLUMA(IVAR )))=  FLUMAS of IVAR at the internal face IFAC
+!
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/elec/uselph.f90

@@ -1,0 +1,422 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uselph &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   ibrom  , izfppp ,                                              &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  )
+
+!===============================================================================
+! FONCTION :
+! --------
+
+!   REMPLISSAGE DES VARIABLES PHYSIQUES POUR LE MODULE ELECTRIQUE
+
+!     ----> Effet Joule
+!     ----> Arc Electrique
+!     ----> Conduction Ionique
+
+!      1) Masse Volumique
+!      2) Viscosite moleculaire
+!      3) Chaleur massique Cp
+!      4) Lambda/Cp moleculaire
+!      4) Diffusivite moleculaire
+
+
+
+! ATTENTION :
+! =========
+
+
+! Il est INTERDIT de modifier la viscosite turbulente VISCT ici
+!        ========
+!  (une routine specifique est dediee a cela : usvist)
+
+! Pour le module electrique, toutes les proprietes physiques sont
+!   supposees variables et contenues dans le tableau PROPCE
+!   (meme si elles sont physiquement constantes)
+
+
+! Remarques :
+! ---------
+
+! Cette routine est appelee au debut de chaque pas de temps
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/elec/usetcl.f90

@@ -1,0 +1,461 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usetcl &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   icodcl , itrifb , itypfb , izfppp ,                            &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  , rcodcl )
+
+!===============================================================================
+! Purpose  :
+! --------
+
+!    User routine for extended physic
+!    Electric module
+!    Allocation of boundary conditions for varaibles unknown during usclim
+
+
+
+!    This user subroutine is compulsory
+!    =============================================
+
+
+! Introduction
+! ============
+
+! Here one defines boundary conditions on a per-face basis.
+
+! Boundary faces may be identified using the 'getfbr' subroutine.
+! The syntax of this subroutine is described in the 'usclim' subroutine,
+! but a more thorough description can be found in the user guide.
+
+
+! Boundary condition types
+! ========================
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/lagr/uslain.f90

@@ -1,0 +1,276 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uslain &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   nbpmax , nvp    , nvp1   , nvep   , nivep  ,                   &
+   ntersl , nvlsta , nvisbr ,                                     &
+   nptnew ,                                                       &
+   itypfb , itrifb , itepa  , ifrlag , injfac ,                   &
+   dt     , rtpa   , propce , propfa , propfb ,                   &
+   coefa  , coefb  ,                                              &
+   ettp   , tepa   , vagaus )
+
+!===============================================================================
+! Purpose:
+! --------
+!
+! User subroutine of the Lagrangian particle-tracking module:
+! -----------------------------------------
+!
+! User subroutine (non-mandatory intervention)
+
+! User subroutine for the boundary conditions for the particles
+! (inlet and treatment for the other boundaries)
+!
+! This routine is called after the initialization of the
+! ettp, tepa and itepa arrays for the new particles in order to modify them
+! to inject new particle profiles.
+!
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
+! nvar             ! i  ! <-- ! total number of variables                      !
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/lagr/uslast.f90

@@ -1,0 +1,405 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uslast &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   nbpmax , nvp    , nvp1   , nvep   , nivep  ,                   &
+   ntersl , nvlsta , nvisbr ,                                     &
+   itepa  ,                                                       &
+   dt     , rtpa   , rtp    , propce , propfa , propfb ,          &
+   coefa  , coefb  ,                                              &
+   ettp   , ettpa  , tepa   , taup   , tlag   , tempct ,          &
+   statis , stativ )
+
+!===============================================================================
+! Purpose:
+! --------
+!
+! User subroutine of the Lagrangian particle-tracking module:
+! -----------------------------------------
+!
+! User subroutine (non-mandatory intervention)
+
+! User-defined modifications on the variables at the end of the
+! Lagrangian iteration and calculation of user-defined
+! additional statistics on the particles.
+!
+! About the user-defined additional statistics, we recall that:
+!
+
+!   isttio = 0 : unsteady Lagrangian calculation
+!          = 1 : stationary Lagrangian calculation
+
+!   istala : calculation of the statistics if >= 1, else no stats
+
+!   isuist : Restart of statistics calculation if >= 1, else no stats
+
+!   idstnt : Number of the time step for the start of the statistics calculation
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5420/SRC/REFERENCE/rayt/usray4.f90

@@ -1,0 +1,174 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usray4 &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   mode   ,                                                       &
+   itypfb ,                                                       &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  ,                                              &
+   tparop , hparop , tempk  )
+
+!===============================================================================
+! Purpose:
+! --------
+
+! User subroutine for input of radiative transfer parameters:
+
+!   Temperature <--> enthalpy convertion
+!   Usefull if the thermal scalar is an enthalpy.
+
+!   PRECAUTIONS: ENTHALPY MUST BE CONVERTED IN KELVIN TEMPERATURE
+
+!   Warning: it is forbidden to modify MODE in this subroutine
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
+! nvar             ! i  ! <-- ! total number of variables                      !
+! nscal            ! i  ! <-- ! total number of scalars                        !
+! mode             ! i  ! <-- ! convertion mode                                !
+!                  !    !     ! mode = 1 enthaly -> temperature                !
+!                  !    !     ! mode =-1 temperature -> enthaly                !
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/DATA/REFERENCE/cs_user_scripts.py

@@ -1,0 +1,289 @@
+#!/usr/bin/env python
+
+#-------------------------------------------------------------------------------
+
+# This file is part of Code_Saturne, a general-purpose CFD tool.
+#
+# Copyright (C) 1998-2011 EDF S.A.
+#
+# This program is free software; you can redistribute it and/or modify it under
+# the terms of the GNU General Public License as published by the Free Software
+# Foundation; either version 2 of the License, or (at your option) any later
+# version.
+#
+# This program is distributed in the hope that it will be useful, but WITHOUT
+# ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+# FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+# details.
+#
+# You should have received a copy of the GNU General Public License along with
+# this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+# Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+#-------------------------------------------------------------------------------
+
+import os
+
+#===============================================================================
+# Defining parameters for a calculation domain
+#===============================================================================
+
+def define_domain_parameter_file(domain):
+    """Define the associated parameters file name"""
+
+    if False:
+        domain.param = 'param2.xml'
+
+    return
+
+#-------------------------------------------------------------------------------
+
+def define_domain_parameters(domain):
+    """Define domain execution parameters"""
+
+    # Reusing output from previous runs
+    #----------------------------------
+
+    # To use the output of a previous Preprocessor (mesh import) run, set:
+    #   domain.mesh_input = 'RESU/<run_id>/mesh_input'
+
+    # To use the mesh output of a previous solver run, set:
+    #   domain.mesh_input = 'RESU/<run_id>/mesh_output'
+
+    # To reuse a previous partitioning, set:
+    #   domain.partition_input = 'RESU/<run_id>/partition'
+
+    # To continue a calculation from a previous checkpoint, set:
+    #  domain.restart_input_dir = 'RESU/<run_id>/checkpoint'
+
+    if domain.param == None:
+        domain.mesh_input = None
+        domain.partition_input = None
+        domain.restart_input = None
+
+    # Defining meshes to import (only if domain.mesh_input = None)
+    #-------------------------------------------------------------
+
+    # A case-specific mesh directory can be defined through domain.mesh_dir.
+
+    if domain.param == None:
+        domain.mesh_dir = None
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/atmo/usativ.f90

@@ -1,0 +1,264 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usativ &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   nbmetd , nbmett , nbmetm ,                                     &
+   dt     , rtp    , propce , propfa , propfb , coefa  , coefb  , &
+   tmprom , ztprom , zdprom , xmet   , ymet   , pmer   ,          &
+   ttprom , qvprom , uprom  , vprom  , ekprom , epprom ,          &
+   rprom  , tpprom , phprom )
+
+!===============================================================================
+! FONCTION :
+! --------
+
+! ROUTINE UTILISATEUR : INITIALISATION DES VARIABLES DE CALCUL
+!     POUR LA PHYSIQUE PARTICULIERE: VERSION ATMOSPHERIQUE
+!     PENDANT DE USINIV
+
+! Cette routine est appelee en debut de calcul (suite ou non)
+!     avant le debut de la boucle en temps
+
+! Elle permet d'INITIALISER ou de MODIFIER (pour les calculs suite)
+!     les variables de calcul,
+!     les valeurs du pas de temps
+
+
+! On dispose ici de ROM et VISCL initialises par RO0 et VISCL0
+!     ou relues d'un fichier suite
+! On ne dispose des variables VISCLS, CP (quand elles sont
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/base/cs_user_mesh_input.c

@@ -1,0 +1,111 @@
+/*============================================================================
+ * Manage the exchange of data between Code_Saturne and the pre-processor
+ *============================================================================*/
+
+/* Code_Saturne version 2.1.4 */
+
+/*
+  This file is part of Code_Saturne, a general-purpose CFD tool.
+
+  Copyright (C) 1998-2011 EDF S.A.
+
+  This program is free software; you can redistribute it and/or modify it under
+  the terms of the GNU General Public License as published by the Free Software
+  Foundation; either version 2 of the License, or (at your option) any later
+  version.
+
+  This program is distributed in the hope that it will be useful, but WITHOUT
+  ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+  FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+  details.
+
+  You should have received a copy of the GNU General Public License along with
+  this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+  Street, Fifth Floor, Boston, MA 02110-1301, USA.
+*/
+
+/*----------------------------------------------------------------------------*/
+
+#if defined(HAVE_CONFIG_H)
+#include "cs_config.h"
+#endif
+
+/*----------------------------------------------------------------------------
+ * Standard C library headers
+ *----------------------------------------------------------------------------*/
+
+#include <assert.h>
+#include <math.h>
+#include <stdarg.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <string.h>
+
+/*----------------------------------------------------------------------------
+ * BFT library headers
+ *----------------------------------------------------------------------------*/
+
+#include "bft_error.h"
+#include "bft_mem.h"
+#include "bft_printf.h"
+
+/*----------------------------------------------------------------------------
+ * FVM library headers
+ *----------------------------------------------------------------------------*/
+
+#include "fvm_defs.h"
+
+/*----------------------------------------------------------------------------
+ *  Local headers
+ *----------------------------------------------------------------------------*/
+
+#include "cs_base.h"
+#include "cs_preprocessor_data.h"
+
+/*----------------------------------------------------------------------------
+ *  Header for the current file
+ *----------------------------------------------------------------------------*/
+
+#include "cs_prototypes.h"
+
+/*----------------------------------------------------------------------------*/
+
+BEGIN_C_DECLS
+
+/*============================================================================
+ * User function definitions
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/base/cs_user_mesh_thinwall.c

@@ -1,0 +1,133 @@
+/*============================================================================
+ * User function for geometry and mesh modification.
+ *============================================================================*/
+
+/* Code_Saturne version 2.1.4 */
+
+/*
+  This file is part of Code_Saturne, a general-purpose CFD tool.
+
+  Copyright (C) 1998-2011 EDF S.A.
+
+  This program is free software; you can redistribute it and/or modify it under
+  the terms of the GNU General Public License as published by the Free Software
+  Foundation; either version 2 of the License, or (at your option) any later
+  version.
+
+  This program is distributed in the hope that it will be useful, but WITHOUT
+  ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+  FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+  details.
+
+  You should have received a copy of the GNU General Public License along with
+  this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+  Street, Fifth Floor, Boston, MA 02110-1301, USA.
+*/
+
+/*----------------------------------------------------------------------------*/
+
+#if defined(HAVE_CONFIG_H)
+#include "cs_config.h"
+#endif
+
+/*----------------------------------------------------------------------------
+ * Standard C library headers
+ *----------------------------------------------------------------------------*/
+
+#include <errno.h>
+#include <locale.h>
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+#include <assert.h>
+
+/*----------------------------------------------------------------------------
+ * BFT library headers
+ *----------------------------------------------------------------------------*/
+
+#include "bft_mem.h"
+#include "bft_printf.h"
+
+/*----------------------------------------------------------------------------
+ * FVM library headers
+ *----------------------------------------------------------------------------*/
+
+#include "fvm_defs.h"
+#include "fvm_selector.h"
+
+/*----------------------------------------------------------------------------
+ *  Local headers
+ *----------------------------------------------------------------------------*/
+
+#include "cs_base.h"
+#include "cs_mesh.h"
+#include "cs_mesh_quantities.h"
+#include "cs_selector.h"
+
+/*----------------------------------------------------------------------------
+ *  Header for the current file
+ *----------------------------------------------------------------------------*/
+
+#include "cs_prototypes.h"
+#include "cs_mesh_thinwall.h"
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/base/uskpdc.f90

@@ -1,0 +1,347 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uskpdc &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   ncepdp , iappel ,                                              &
+   icepdc , izcpdc ,                                              &
+   dt     , rtpa   , rtp    , propce , propfa , propfb ,          &
+   coefa  , coefb  , ckupdc )
+
+!===============================================================================
+! FONCTION :
+! ----------
+
+!                    PERTES DE CHARGE (PDC)
+
+! IAPPEL = 1 :
+!             CALCUL DU NOMBRE DE CELLULES OU L'ON IMPOSE UNE PDC
+! IAPPEL = 2 :
+!             REPERAGE DES CELLULES OU L'ON IMPOSE UNE PDC
+! IAPPEL = 3 :
+!             CALCUL DES VALEURS DES COEFS DE PDC
+
+
+! CKUPDC EST LE COEFF DE PDC CALCULE.
+
+!  IL INTERVIENT DANS LA QDM COMME SUIT :
+!    RHO DU/DT = - GRAD P + TSPDC        (+ AUTRES TERMES)
+!                      AVEC TSPDC = - RHO CKUPDC U ( en kg/(m2 s))
+
+
+!  POUR UNE PDC REPARTIE,
+
+!    SOIT KSIL = DHL/(0.5 RHO U**2) DONNE DANS LA LITTERATURE
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/base/usmpst.f90

@@ -1,0 +1,280 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usmpst &
+!================
+
+ ( ipart  ,                                                       &
+   nvar   , nscal  , nvlsta ,                                     &
+   ncelps , nfacps , nfbrps ,                                     &
+   imodif ,                                                       &
+   itypps ,                                                       &
+   lstcel , lstfac , lstfbr ,                                     &
+   dt     , rtpa   , rtp    , propce , propfa , propfb ,          &
+   coefa  , coefb  , statis ,                                     &
+   tracel , trafac , trafbr )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+! Modify list of cells or faces defining an existing post-processing
+! output mesh; this subroutine is called for true (non-alias) user meshes,
+! for each time step at which output on this mesh is active, and only if
+! all writers associated with this mesh allow mesh modification
+! (i.e. were defined with 'indmod' = 2 or 12).
+
+!-------------------------------------------------------------------------------
+! Arguments
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/base/uspt1d.f90

@@ -1,0 +1,303 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uspt1d &
+!================
+
+ ( nvar   , nscal  , nfpt1d , iappel ,                            &
+   ifpt1d , izft1d , nppt1d , iclt1d ,                            &
+   tppt1d , rgpt1d , eppt1d ,                                     &
+   tept1d , hept1d , fept1d ,                                     &
+   xlmt1d , rcpt1d , dtpt1d ,                                     &
+   dt     , rtpa   ,                                              &
+   propce , propfa , propfb ,                                     &
+   coefa  , coefb  )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!     User subroutine.
+
+!     Data Entry ot the thermal module in 1-Dimension Wall.
+
+
+! Introduction:
+!=============
+
+! Define the different values which can be taken by iappel:
+!--------------------------------------------------------
+
+! iappel = 1 (only one call on initialization):
+!            Computation of the cells number where we prescribe a wall
+
+! iappel = 2 (only one call on initialization):
+!            Locating cells where we prescribe a wall
+!            Data linked to the meshing.
+
+! iappel = 3 (call on each time step):
+!            Value of the physical computational coefficients and
+!            boundary condition type on the exterior wall:
+!            --------------------------------------------
+!
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/base/usstru.f90

@@ -1,0 +1,465 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+! Purpose :
+! ---------
+!     User subroutine dedicated to Fluid - Structure internal coupling
+
+! --- Definition and management of internal Fluid Structure coupled calculations,
+!     using a simplified solid modeling (linear "mass, friction and spring" modeling).
+
+!     Here are 2 differents subroutines that need to be filled :
+
+!  -   USSTR1 : Called at the beginning of the calculation. It enables one to define
+!               internal structures and corresponding initial conditions (initial
+!               displacement and velocity).
+
+!  -   USSTR2 : Called at each time step of the calculation. Here one defines
+!               structural parameters (considered to be potentially time dependent),
+!               i.e. Mass, Friction, Stiffness and Fluid Stresses.
+
+! --- Boundary faces identification
+!     =============================
+
+! Boundary faces may be identified using the 'getfbr' subroutine.
+! The syntax of this subroutine is described in the 'usclim' subroutine,
+! but a more thorough description can be found in the user guide.
+
+
+!-------------------------------------------------------------------------------
+subroutine usstr1 &
+!================
+
+ ( idfstr ,                                                       &
+   aexxst , bexxst , cfopre ,                                     &
+   xstr0  , vstr0  , xstreq )
+
+!===============================================================================
+! Purpose :
+! ---------
+
+! --- Definition of internal structures and corresponding initial conditions
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/base/ustsma.f90

@@ -1,0 +1,505 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine ustsma &
+!================
+
+ ( nvar   , nscal  , ncepdp ,                                     &
+   ncesmp , iappel ,                                              &
+   icepdc , icetsm , itypsm , izctsm ,                            &
+   dt     , rtpa   , propce , propfa , propfb ,                   &
+   coefa  , coefb  , ckupdc , smacel )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Mass source term
+
+! The subroutine ustsma is called at three different stages in the code
+!  (iappel = 1, 2 or 3)
+
+! iappel = 1
+!    Calculation of the number of cells where a mass source term is
+!    imposed: ncesmp
+!    Called once at the beginnign of the calculation
+
+! iappel = 2
+!    Identification of the cells where a mass source term is imposed:
+!    array icesmp(ncesmp)
+!    Called once at the beginnign of the calculation
+
+! iappel = 3
+!    Calculation of the values of the mass source term
+!    Called at each time step
+
+
+
+! The equation for mass conservation becomes
+
+!           d(rho)/dt + div(rho u) = gamma
+
+! The equation for a variable f becomes
+
+!           d(f)/dt = ..... + gamma*(f_i - f)
+
+!   discretized as
+
+!           rho*(f^(n+1) - f^(n))/dt = .....
+!                                    + gamma*(f_i - f^(n+1))
+
+! f_i is the value of f associated to the injecte mass.
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/base/ustssa.f90

@@ -1,0 +1,224 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine ustssa &
+!================
+
+ ( nvar   , nscal  , ncepdp , ncesmp ,                            &
+   icepdc , icetsm , itypsm ,                                     &
+   dt     , rtpa   , propce , propfa , propfb ,                   &
+   coefa  , coefb  , ckupdc , smacel , tinssa , divu   ,          &
+   crvexp , crvimp )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Additional right-hand side source terms for the viscosity-like variable
+!    when using the Spalart-Allmaras model (ITURB=70)
+!
+! Usage
+! -----
+!
+! The additional source term is decomposed into an explicit part (crvexp) and
+! an implicit part (crvimp) that must be provided here.
+! The resulting equations solved by the code are:
+!
+!  rho*volume*d(nusa)/dt   + .... = crvimp*nusa   + crvexp
+!
+! Note that crvexp, crvimp are defined after the Finite Volume
+! integration over the cells, so they include the "volume" term. More precisely:
+!   - crvexp is expressed in kg.m2/s2
+!   - crvimp is expressed in kg/s
+!
+! The crvexp, crvimp arrays are already initialized to 0 before
+! entering the routine. It is not needed to do it in the routine (waste of CPU time).
+!
+! For stability reasons, Code_Saturne will not add -crvimp directly to the
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/base/usvist.f90

@@ -1,0 +1,215 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usvist &
+!================
+
+ ( nvar   , nscal  , ncepdp , ncesmp ,                            &
+   icepdc , icetsm , itypsm ,                                     &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  , ckupdc , smacel )
+
+!===============================================================================
+! Purpose:
+! -------
+
+! User subroutine.
+
+! Modify turbulent viscosity
+
+! This subroutine is called at beginning of each time step
+! after the computation of the turbulent viscosity
+! (physical quantities have already been computed in usphyv)
+
+! Turbulent viscosity VISCT (kg/(m s)) can be modified
+
+! A modification of the turbulent viscosity can lead to very
+! significant differences betwwen solutions and even give wrong
+! results
+
+! This subroutine is therefore reserved to expert users
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
+! nvar             ! i  ! <-- ! total number of variables                      !
+! nscal            ! i  ! <-- ! total number of scalars                        !
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/cfbl/uscfpv.f90

@@ -1,0 +1,661 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uscfpv &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  )
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Set (variable) physical properties for the compressible flow scheme.
+
+
+! Description
+! ===========
+
+! This subroutine replaces the user subroutine 'usphyv' for the
+! compressible flow scheme.
+
+! This subroutine is called at the beginning of each time step.
+
+! At the very first time step (not at restart), the only variables that
+! have been initialized are those provided:
+!   - in the GUI and in the user subroutines 'usini1' and 'uscfx2'; ex.:
+!     . the density             (set to ro0)
+!     . the molecular viscosity (set to viscl0)
+!     . the volumetric molecular viscosity (set to viscv0)
+!     . the molecular thermal conductivity (set to visls0(itempk))
+!   - in the user subroutines 'usiniv' and 'uscfxi'; ex.:
+!     . the unknown variables (null by default)
+
+! This subroutine allows the user to set the cell values for:
+!   - the molecular viscosity                            viscl  kg/(m s)
+!   - the isobaric specific heat (cp=dh/dT|P)            cp     J/(kg degree)
+!   - the molecular thermal conductivity                 lambda W/(m degree)
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/cfbl/uscfx1.f90

@@ -1,0 +1,95 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uscfx1
+!================
+
+
+!===============================================================================
+! Purpose:
+! -------
+
+!    User subroutine.
+
+!    Initialize non standard options for the compressible flow scheme.
+
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+!    nom           !type!mode !                   role                         !
+!__________________!____!_____!________________________________________________!
+!__________________!____!_____!________________________________________________!
+
+!     Type: i (integer), r (real), s (string), a (array), l (logical),
+!           and composite types (ex: ra real array)
+!     mode: <-- input, --> output, <-> modifies data, --- work array
+!===============================================================================
+
+!===============================================================================
+! Module files
+!===============================================================================
+
+use paramx
+use dimens
+use numvar
+use optcal
+use cstphy
+use entsor
+use cstnum
+use parall
+use period
+use ppppar
+use ppthch
+use ppincl
+
+!===============================================================================
+
+implicit none
+
+! Arguments
+
+
+! Local variables
+
+!===============================================================================
+
+!===============================================================================
+
+
+!===============================================================================
+! 1. Scheme options
+!===============================================================================
+
+! Specify if the hydrostatic equilibrium must be accounted for
+!     (yes = 1 , no = 0)
+
+icfgrp = 1
+
+!----
+! FIN
+!----
+
+return
+end subroutine

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/cogz/uslwci.f90

@@ -1,0 +1,367 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uslwci &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   dt     , rtp    , propce , propfa , propfb , coefa  , coefb  )
+
+!===============================================================================
+! PURPOSE :
+! --------
+! Initialisation of the transported variables of EBU combustion model.
+! The latter ones are used to calculate premixed flame properties
+! by applying detailed thermochemistry data.
+!
+! FEATURES:
+! --------
+! - This subroutine is called at the beginning of both a restart-calculation
+!   and a new calculation.
+! - The user is able to modify the initial conditions of the tranported
+!   variables.
+! - All variables of state deducible from the transported variables, as well as
+!   the detailed thermochemistry data (JANAF-table) are located in the array named
+!
+!   a) PROPCE (Properties in the cell center).
+!   b) PROPFA (Properties at internal faces).
+!   c) PROPFB (Properties at boundary faces).
+!
+!   Examples:
+!   PROPCE(IEL,IPPROC(IROM  )) =  IROM of cell IEL
+!   PROPCE(IEL,IPPROC(ICP   )) =  ICP  of cell IEL
+!
+!   PROPFA(IFAC,IPPROF(IFLUMA(IVAR )))=  FLUMAS of IVAR at the internal face IFAC
+!
+!   PROPFB(IFAC,IPPROB(IROM  ))=  ROMB at the boundary face IFAC
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/comb/user_coal_ini1.f90

@@ -1,0 +1,428 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine user_coal_ini1
+!==================================
+
+
+!===============================================================================
+!  PURPOSE   :
+!  ---------
+!  User's routine to control outing of variables for pulverised coal combustion
+!  (these parameters are in COMMON)
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/comb/user_coal_iniv.f90

@@ -1,0 +1,384 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine user_coal_iniv                               &
+!================
+ ( nvar   , nscal  ,                                            &
+   dt     , rtp    , propce , propfa , propfb , coefa  , coefb  )
+
+!===============================================================================
+! PURPOSE  :
+! --------
+! Initialisation of transported variables for extended physics :
+!  pulverised coal combustion
+!   similar to USINIV
+!
+! This routine is called at the beginning of every computation
+!  (new or continuation) before the time loop
+!
+! This routine initialize or modify (if continuation)
+!  values of transported variables and of the time step
+!
+! The exemple is ... default value
+
+!
+! Physical properties are stored in PROPCE(cell center)
+!  PROPFA(inner face) and PROPFB(boundary face)
+!  e.g.
+!  PROPCE(IEL, IPPROC(IROM  )) is ROM(IEL) mean density kg/m3
+!  PROPFA(IFAC,IPPROF(IFLUMA(IVAR ))) is FLUMAS(IFAC,IVAR) convective flux
+!                                                        of variable IVAR
+!  PROPFB(......                      .................................
+!
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/comb/user_fuel_bcond.f90

@@ -1,0 +1,839 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine user_fuel_bcond &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   icodcl , itrifb , itypfb , izfppp ,                            &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  , rcodcl )
+
+!===============================================================================
+! PURPOSE  :
+! --------
+
+!    USER SUBROUTINE for extended physic
+!                Combsution of heavy Fuel oil
+!    Allocation of boundary conditions (ICODCL, RCODCL)
+!    for variables unknowns during USCLIM
+
+
+! Introduction
+! ============
+
+! Here we define boundary conditions on a per-face basis.
+
+! Boundary faces may be identified using the 'getfbr' subroutine.
+
+!  getfbr(string, nelts, eltlst) :
+!  - string is a user-supplied character string containing
+!    selection criteria;
+!  - nelts is set by the subroutine. It is an integer value
+!    corresponding to the number of boundary faces verifying the
+!    selection criteria;
+!  - lstelt is set by the subroutine. It is an integer array of
+!    size nelts containing the list of boundary faces verifying
+!    the selection criteria.
+
+!  string may contain:
+!  - references to colors (ex.: 1, 8, 26, ...
+!  - references to groups (ex.: inlet, group1, ...)
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/comb/user_fuel_iniv.f90

@@ -1,0 +1,338 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine user_fuel_iniv &
+!========================
+
+ ( nvar   , nscal  ,                                              &
+   dt     , rtp    , propce , propfa , propfb , coefa  , coefb  )
+
+!===============================================================================
+! PURPOSE  :
+! --------
+
+! INITIALISATION OF TRANSPORTED VARIABLES
+!    EXTENDED PHYSICS : Heavy Fuel Oil Combustion
+!    similar to  USINIV.F
+!
+! This routine is called at the beginning of every computation
+!  (new or continuation) before the time loop
+!
+! This routine initialize or modify (if continuation)
+!  values of transported variables and of the time step
+!
+! The exemple is ... default value
+
+!
+! Physical properties are stored in PROPCE(cell center)
+!  PROPFA(inner face) and PROPFB(boundary face)
+!  e.g.
+!  PROPCE(IEL, IPPROC(IROM  )) is ROM(IEL) mean density kg/m3
+!  PROPFA(IFAC,IPPROF(IFLUMA(IVAR ))) is FLUMAS(IFAC,IVAR) convective flux
+!                                                        of variable IVAR
+!  PROPFB(......                      .................................
+!
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/cplv/uscpcl.f90

@@ -1,0 +1,748 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uscpcl &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   icodcl , itrifb , itypfb , izfppp ,                            &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  , rcodcl )
+
+!===============================================================================
+! PURPOSE  :
+! --------
+!    USER'S ROUTINE FOR EXTENDED PHYSIC
+!           PULVERISED COAL COMBUSTION
+!    ALLOCATION OF BOUNDARY CONDITIONS (ICODCL,RCODCL)
+!    FOR VARIABLES UNKNOWN DURING USCLIM
+!
+! Introduction
+! ============
+
+! Here we define boundary conditions on a per-face basis.
+
+! Boundary faces may be identified using the 'getfbr' subroutine.
+
+!  getfbr(string, nelts, eltlst) :
+!  - string is a user-supplied character string containing
+!    selection criteria;
+!  - nelts is set by the subroutine. It is an integer value
+!    corresponding to the number of boundary faces verifying the
+!    selection criteria;
+!  - lstelt is set by the subroutine. It is an integer array of
+!    size nelts containing the list of boundary faces verifying
+!    the selection criteria.
+
+!  string may contain:
+!  - references to colors (ex.: 1, 8, 26, ...
+!  - references to groups (ex.: inlet, group1, ...)
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/cplv/uscplc.f90

@@ -1,0 +1,706 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uscplc &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   icodcl , itrifb , itypfb , izfppp ,                            &
+   dt     , rtp    , rtpa   , propce , propfa , propfb ,          &
+   coefa  , coefb  , rcodcl )
+
+!===============================================================================
+! FONCTION :
+! --------
+
+!   SOUS-PROGRAMME DU MODULE LAGRANGIEN COUPLE CHARBON PULVERISE :
+!   --------------------------------------------------------------
+
+!    ROUTINE UTILISATEUR POUR PHYSIQUE PARTICULIERE
+
+!      COMBUSTION EULERIENNE DE CHARBON PULVERISE ET
+!      TRANSPORT LAGRANGIEN DES PARTICULES DE CHARBON
+
+!    REMPLISSAGE DU TABLEAU DE CONDITIONS AUX LIMITES
+!    (ICODCL,RCODCL) POUR LES VARIABLES INCONNUES
+!    PENDANT DE USCLIM.F
+
+
+
+
+! INTRODUCTION
+! ============
+
+! On donne ici les conditions aux limites par face de bord.
+
+! L'identification des faces de bord concernees se fait grace
+! a la commande GETFBR.
+
+!  GETFBR(CHAINE,NLELT,LSTELT) :
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/elec/useli1.f90

@@ -1,0 +1,234 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine useli1
+!================
+
+
+!===============================================================================
+!  Purpose  :
+!  -------
+!          User subroutines for input of calculation parameters,
+!       and to initialize variables used for specific electric models,
+!
+!
+!                 by addition of what is done in  USINI1
+!
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
+! name             !type!mode ! role                                           !
+!__________________!____!_____!________________________________________________!
+!__________________!____!_____!________________________________________________!
+
+!     Type: i (integer), r (real), s (string), a (array), l (logical),
+!           and composite types (ex: ra real array)
+!     mode: <-- input, --> output, <-> modifies data, --- work array
+!===============================================================================
+!
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/elec/useliv.f90

@@ -1,0 +1,254 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine useliv &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   dt     , rtp    , propce , propfa , propfb , coefa  , coefb  )
+
+!===============================================================================
+! Purpose :
+! --------
+
+! variables initialization for specific electric module :
+!    the same as USINIV.F for main variables
+
+! Cette routine est appelee en debut de calcul (suite ou non)
+!     avant le debut de la boucle en temps
+
+! Elle permet d'INITIALISER ou de MODIFIER (pour les calculs suite)
+!     les variables de calcul (inconnues transportees),
+!     la valeur du pas de temps,
+
+! On a repris a titre d'exemple dans cette routine utilisateur
+!     l'initialisation choisie par defaut.
+!
+
+! Thermodynamic properties and transport coefficients are in
+!     PROPCE (at the center of the cells), PROPFA (for internal faces),
+!     PROPFB (prop aux faces de bord)
+!     Ainsi,
+!      PROPCE(IEL,IPPROC(IROM  )) designe ROM   (IEL)
+!      PROPCE(IEL,IPPROC(IVISCL)) designe VISCL (IEL)
+!      PROPCE(IEL,IPPROC(ICP   )) designe CP    (IEL)
+!      PROPCE(IEL,IPPROC(IVISLS(ISCAL))) designe VISLS (IEL ,ISCAL)
+
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/lagr/uslaed.f90

@@ -1,0 +1,232 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uslaed &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   nbpmax , nvp    , nvp1   , nvep   , nivep  ,                   &
+   ntersl , nvlsta , nvisbr ,                                     &
+   itepa  , ibord  ,                                              &
+   dt     , rtp    , propce , propfa , propfb ,                   &
+   ettp   , ettpa  , tepa   , taup   , tlag   , tempct , tsvar  , &
+   auxl1  , auxl2  , auxl3  )
+
+!===============================================================================
+! Purpose :
+! ----------
+
+!   Subroutine of the Lagrangian particle-tracking module :
+!   -------------------------------------
+
+!     User subroutine (non-mandatory intervention)
+
+!     Integration of the sde for the user-defined variables.
+!     The variables are constant by default.
+
+
+!                                         d T       T - PIP
+!     The sde must be of the form:       ----- = - ---------
+!                                         d t         Tca
+
+
+!     T : IIIIeme user-defined variable, given for the ip particle by
+!            T = ETTP(IP,JVLS(IIII))
+!            T = ETTPA(IP,JVLS(IIII))
+
+!     Tca : Characteristic time for the sde
+!           to be prescribed in the array auxl1
+
+!     PIP : Coefficient of the sde (pseudo right member)
+!           to be prescribed in the array auxl2
+!
+!           If the chosen scheme is first order (nordre=1)
+!           then, at the first and only passage pip is expressed
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/lagr/uslag2.f90

@@ -1,0 +1,496 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine uslag2 &
+!================
+
+ ( nvar   , nscal  ,                                              &
+   nbpmax , nvp    , nvp1   , nvep   , nivep  ,                   &
+   ntersl , nvlsta , nvisbr ,                                     &
+   itypfb , itrifb , itepa  , ifrlag ,                            &
+   dt     , rtpa   , propce , propfa , propfb ,                   &
+   coefa  , coefb  ,                                              &
+   ettp   , tepa   )
+
+!===============================================================================
+! Purpose:
+! ----------
+
+!   Subroutine of the Lagrangian particle-tracking module:
+!   -------------------------------------
+
+!    User subroutine (Mandatory intervention)
+
+!    User subroutine for the boundary conditions associated to the particles
+!    (inlet and treatment of the other boundaries)
+
+
+! Boundary faces identification
+! =============================
+
+! Boundary faces may be identified using the 'getfbr' subroutine.
+! The syntax of this subroutine is described in the 'usclim' subroutine,
+! but a more thorough description can be found in the user guide.
+
+
+!-------------------------------------------------------------------------------
+! Arguments
+!__________________.____._____.________________________________________________.
[…]

### 2013-02-20 phys715/simulation/AIRFOIL/NACA5440/SRC/REFERENCE/rayt/usray1.f90

@@ -1,0 +1,328 @@
+!-------------------------------------------------------------------------------
+
+!                      Code_Saturne version 2.1.4
+!                      --------------------------
+! This file is part of Code_Saturne, a general-purpose CFD tool.
+!
+! Copyright (C) 1998-2011 EDF S.A.
+!
+! This program is free software; you can redistribute it and/or modify it under
+! the terms of the GNU General Public License as published by the Free Software
+! Foundation; either version 2 of the License, or (at your option) any later
+! version.
+!
+! This program is distributed in the hope that it will be useful, but WITHOUT
+! ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
+! FOR A PARTICULAR PURPOSE.  See the GNU General Public License for more
+! details.
+!
+! You should have received a copy of the GNU General Public License along with
+! this program; if not, write to the Free Software Foundation, Inc., 51 Franklin
+! Street, Fifth Floor, Boston, MA 02110-1301, USA.
+
+!-------------------------------------------------------------------------------
+
+subroutine usray1
+!================
+
+
+
+!===============================================================================
+!  FONCTION  :
+!  ---------
+
+
+!   ============================================================
+!   ROUTINE UTILISATEUR : INITIALISATION DES COMMONS RAYONNEMENT
+!   ============================================================
+
+
+
+!  CALCUL DES FLUX ET DU TERME SOURCE RADIATIFS
+
+!  METHODE DES VOLUMES FINIS.
+
+
+! 1/ DONNEES DES LUMINANCES ENTRANTES AUX LIMITES DU DOMAINE
+!       (C    .L : REFLEXION ET EMISSION ISOTROPE)
+
+!                              ->  ->           ->
+! 2/ CALCUL DE LA LUMINANCE L( X , S ) AU POINT X
+
+!                                   D L
+!    PAR RESOLUTION DE L'EQUATION : --- = -TK.L +TS
+!                                   D S
[…]

### 2013-02-20 phys746/phys746assign1q3.py

@@ -1,0 +1,45 @@
+#!/usr/bin/python
+import numpy as np
+import matplotlib.pyplot as plt
+
+#The integral differential element of the energy density in the slab
+def dslabu(z, theta, tau0):
+	return np.exp(-1.0*z*tau0/np.cos(theta))*np.sin(theta)
+
+#This function calculates the integral of a function evaluated from minimum to
+#maximum using Simpson's rule, with a grid size of step
+def simpson_integrate(function, minimum, maximum, step):
+	integral = 0.0
+	n = 1
+	while maximum > minimum+n*step:
+		if n % 2 == 0:
+			integral += 2.0*function(minimum+n*step)
+		else:
+			integral += 4.0*function(minimum+n*step)
+		n += 1
+	return step/3.0*(function(minimum) + integral)
+
+#The total integrated energy density in the slab
+def slabu(z, tau0):
+	return 2*np.pi*((1-simpson_integrate(lambda x: dslabu(z, x, tau0), 0, 
+	np.pi*0.5, 1e-4))+(1-simpson_integrate(lambda x: dslabu((1-z), x, tau0),
+	0, np.pi*0.5, 1e-4)))
+
+if __name__ == "__main__":
+	zrange = np.power(10, (np.arange(-3, 0, 0.001))) #z range [0.001, 1]
+	tau = (0.01, 0.1, 1, 10, 100) #tau0 range
+	plt.semilogx(zrange , slabu(zrange, tau[0]), 
+	label=r"$\tau_0=%3.2f$" % (tau[0]))
+	plt.semilogx(zrange , slabu(zrange, tau[1]),
+	label=r"$\tau_0=%3.2f$" % (tau[1]))
+	plt.semilogx(zrange , slabu(zrange, tau[2]),
+	label=r"$\tau_0=%d$" % (tau[2]))
+	plt.semilogx(zrange , slabu(zrange, tau[3]),
+	label=r"$\tau_0=%d$" % (tau[3]))
+	plt.semilogx(zrange , slabu(zrange, tau[4]),
+	label=r"$\tau_0=%d$" % (tau[4]))
+	plt.xlabel(r"Slab Depth, log10 scale")
+	plt.ylabel(r"Energy Density$\times c/B_\nu$")
+	plt.legend(loc=2)
+	plt.title("Exercise 2.3")
+	plt.show()

### 2013-02-20 phys761/phys761assign1.py

@@ -1,0 +1,19 @@
+#!/usr/bin/python
+import numpy as np
+import matplotlib.pyplot as plt
+
+def planckfunction(wl, temp):
+	return 1.19e-16/np.power(wl, 5.0)*(1.0/(np.exp((0.0144)/(wl*temp))-1.0))
+
+if __name__ == "__main__":
+	Irange = np.concatenate((np.arange(1e-9, 1e-6, 1e-9), np.arange(1e-6, 1e-3, 1e-6), np.arange(1e-3, 1, 1e-3), np.arange(1, 1000, 1)))
+	I30000 = np.vectorize(lambda x: planckfunction(x, 30000))
+	I6000 = np.vectorize(lambda x: planckfunction(x, 6000))
+	I2500 = np.vectorize(lambda x: planckfunction(x, 2500))
+	plt.loglog(Irange, I2500(Irange))
+	plt.loglog(Irange, I6000(Irange))
+	plt.loglog(Irange, I30000(Irange))
+	plt.ylim(1,1e14)
+	plt.axvline(3.5e-7)
+	plt.axvline(8.5e-7)
+	plt.show()

### 2013-02-20 phys761/phys761assign2.py

@@ -1,0 +1,51 @@
+#!/usr/bin/python
+# Ben Keller
+# October 2011
+# Solution for Question 2 in Physics 761 Assignment 2
+import numpy
+import matplotlib.pyplot as plt
+
+#The Lane Emden Equation, reformulated using the subsitution z=Dn' to be
+#z' = -Dn^n - 2z/x
+def LaneEmden(xi, Dn, z, n):
+	return -1.0*numpy.power(Dn, n)-(2.0/xi)*z
+
+
+#This function is simply the Runge-Kutta 4th order method for solving ODEs.
+#It solves for y' = func(x, y) at the point x=xf, and returns all the 
+#intermediate values
+def rk4(func, h, x0, y0, z0, xf):
+	yn = y0
+	xn = x0
+	zn = z0
+	yvals = []
+	xvals = []
+	while xn < xf:
+		k1 = h*func(xn, yn, zn)
+		k2 = h*func(xn+0.5*h, yn+0.5*k1, zn)
+		k3 = h*func(xn+0.5*h, yn+0.5*k2, zn)
+		k4 = h*func(xn+h, yn+k3, zn)
+		zn += (k1 + k2 + k3 + k4)/6.0
+		yn += h*zn
+		xn += h
+		yvals.append(yn)
+		xvals.append(xn)
+	return (xvals, yvals)
+
+if __name__ == "__main__":
+	#Define the n=1.5 and n=3.0 Lane Emden equations
+	lane1 = lambda x, y, z: LaneEmden(x, y, z, 1.5)
+	lane2 = lambda x, y, z: LaneEmden(x, y, z, 3.0)
+	#Calculate the points for the two solutions
+	(x1, y1) = rk4(lane1, 1e-5, 1-((1e-10)/6), 1, 0, 5)
+	(x2, y2) = rk4(lane2, 1e-5, 1-((1e-10)/6), 1, 0, 6)
+	#Plot the results
+	plt.plot(x1, y1, 'k-', label="n=1.5")
+	plt.plot(x2, y2, 'k--', label="n=3")
+	plt.legend()
+	plt.ylabel("$D_n$")
+	plt.xlabel("$\\xi$")
+	plt.title("Solutions to the Lane-Emden Equation")
+	plt.ylim((0,1))
+	plt.savefig("phys761assign2.pdf")
+	plt.show()

### 2013-02-20 phys762/phys762assign1.py

@@ -1,0 +1,19 @@
+#!/usr/bin/python
+# Phsyics 762 Assignment 1 Question 3
+# Ben Keller
+# 1178881
+# November 2 2011
+import numpy as np
+import matplotlib.pyplot as plt
+
+if __name__ == "__main__":
+	SmNd = [0.1847, 0.1963, 0.1980, 0.2061, 0.2715, 0.2879]
+	NdNd = [0.511721, 0.511998, 0.512035, 0.512238, 0.513788, 0.514154]
+	NdNdError = [0.000018, 0.000016, 0.000021, 0.000017, 0.000015, 0.000017]
+	plt.errorbar(SmNd, NdNd, yerr=NdNdError, color='k', linestyle='--')
+	plt.xlabel("Sm-147/Nd-144 Ratio")
+	plt.ylabel("Nd-143/Nd-144 Ratio")
+	plt.title("Samarium-Neodymium Isotope Dating of Lunar Basalt")
+	print np.polyfit(SmNd, NdNd, 1)
+	plt.savefig("phys762assign1.pdf")
+	plt.show()

### 2013-02-20 phys762/phys762assign2.py

@@ -1,0 +1,38 @@
+#!/usr/bin/python
+# Physics 762 Assignment 2 Question 5
+# Ben Keller
+# 1178881
+# November 8 2011
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+M0 = 7.36e36
+k = 6.2e19
+G = 6.67e-11
+Msun = 1.989e30
+parsec = 3.086e16
+
+def mass(radius):
+	return k*radius+M0
+
+def velocity(radius):
+	return np.sqrt(G*(k+M0/radius))
+
+if __name__ == "__main__":
+	radialrange = parsec*np.arange(0.01, 1000, 0.01)
+	massrange = mass(radialrange)
+	velocityrange = velocity(radialrange)
+	plt.loglog(radialrange/parsec, massrange/Msun, 'k-')
+	plt.xlabel(r'$\log_{10}r (pc)$')
+	plt.ylabel(r'$\log_{10}M_r (M\odot)$')
+	plt.title('Mass Distribution for Inner Galaxy')
+	plt.savefig('phys762assign2d.pdf')
+	plt.show()
+	plt.cla()
+	plt.loglog(radialrange/parsec, velocityrange/1000.0, 'k-')
+	plt.xlabel(r'$\log_{10}r (pc)$')
+	plt.ylabel(r'$\log_{10}v (kms^{-1})$')
+	plt.title('Velocity Distribution for Inner Galaxy')
+	plt.savefig('phys762assign2e.pdf')
+	plt.show()

### 2013-02-20 phys762/phys762assign2q1.py

@@ -1,0 +1,23 @@
+#!/usr/bin/python
+# Physics 762 Assignment 2 Question 1
+# Ben Keller
+# 1178881
+# November 8 2011
+import matplotlib.pyplot as plt
+import numpy as np
+
+if __name__ == "__main__":
+	V = np.arange(4,20)
+	Am = [-2.31, -1.71, -1.11, -0.51, 0.09, 0.69, 1.29, 1.89, 2.24, 2.59, 2.94,
+	3.29, 3.89, 4.49, 5.09, 5.69]
+	plt.plot(V, Am, 'ko')
+	(slope, int1) = np.polyfit(V[:8], Am[:8], 1)
+	(slope, int2) = np.polyfit(V[-5:], Am[-5:], 1)
+	plt.plot(V, V*slope+int1, 'r-', label='Fitted Slope: %1.1f Fitted Intercept: %1.2f' % (slope, int1))
+	plt.plot(V, V*slope+int2, 'b-', label='Fitted Slope: %1.1f Fitted Intercept: %1.2f' % (slope, int2))
+	plt.legend(loc=0)
+	plt.ylabel(r'$\log_{10}A_M$')
+	plt.xlabel(r'$V$')
+	plt.title('Gas Cloud Extinction')
+	plt.savefig('phys762assign2q1.pdf')
+	plt.show()

### 2013-02-20 phys785/problemset2/question2.py

@@ -1,0 +1,34 @@
+#!/usr/bin/python
+import numpy as np
+from scipy.optimize import leastsq
+import matplotlib.pyplot as plt
+
+if __name__ == "__main__":
+	masses = np.genfromtxt("20Kmasses.dat")
+	#Apply the low-mass threshold (0.4 Msol is when incompleteness becomes
+	#significant, but Johnstone et al. 2000 found a change in slope at 0.6 Msol
+	masses = masses[np.where(masses > 0.6)]
+	#Take a mass histogram to find dN/dM.  6 bins is the maximum number that has no
+	#empty bins
+	(count, bins) = np.histogram(np.log10(masses), 6)
+	binerr = (bins[1:]-bins[:-1])/2
+	bincenters = bins[:-1]+binerr
+	#Relative Uncertainty in N is sqrt(N)/N
+	counterr = 1/np.sqrt(count)
+	count = count.astype(np.float64)/np.power(10, bincenters)
+	#Generate a power-law fit using a uncertainty-weighted least-squares fit of
+	#log(N) to log(M)
+	fitfunc = lambda p, x: p[0]+p[1]*x
+	errfunc = lambda p, x,y, yerr,xerr: (y-fitfunc(p,x))/np.sqrt(xerr**2+yerr**2)
+	fit = leastsq(errfunc, [-0.2,6], args=(bins[:-1], np.log10(count), counterr, binerr),
+			full_output=1)
+	(intercept, slope) = fit[0]
+	#Print the slope and the covariance matrix's inner product with the slope (uncertainty)
+	print "Slope of Power Law Fit %3.2f +/- %3.2f" % (slope, np.sqrt(fit[1][0][0]))
+	plt.plot(bincenters, bincenters*slope+intercept, 'k--', label='Power-Law Fit')
+	plt.errorbar(bincenters, np.log10(count), linestyle='none', color='red', marker='o', 
+			yerr=counterr, xerr=binerr, label='Clump Observation')
+	plt.xlabel('$log_{10}$ Mass $(M_\odot)$')
+	plt.ylabel(r'$log_{10}$ $dN/dM$ $(M^{-1}_\odot)$')
+	plt.legend()
+	plt.show()

### 2013-02-21 phys781/report.tex
Added all the classwork on angband

@@
 observations, as well as the current state of knowledge on the topic.
+
 \section{Background \& Observations}
@@
 radio wavelengths at higher densities in this core region.
+
 \subsection{A Central, Supermassive Black Hole}
@@
 that there is no configuration of stars that could be long lived at that 
-density.
+density.  Currently, the SMBH hypothesis is the consensus view of the dark mass
+at the galactic center.
+
+The SMBH hypothesis explaining the central dark mass of the Milky Way was an
+attractive answer for another group of astronomers working on a separate 
+question:  quasars.  The extremely high luminosity (on the order of 
+$10^{13}L\odot$) of these objects was a
+mystery for a number of years, and hinted at a driving engine far more energetic
+than any stellar effects could account for.  As the physics of black hole
+accretion developed, it was realized that accretion onto a SMBH could easily 
+produce the luminosity of quasars.  As quasars were hypothesized as the early
+stages of modern disk galaxies, the existence of an SMBH in the Milky Way was
+taken as further confirmation of the SMBH accretion model of quasar emission.
+Further evidence of both the quasar connection and the SMBH hypothesis was found
+in the form of radio variability in the form of rapid flares in radio intensity
+coming from Sgr A*, corresponding to the accretion of stars or dense clouds.
 
 \subsection{Extragalactic SMBHs}
-\subsection{The $M_{BH}-\sigma$ Relation}
+Regardless of what the Copernican principle might tell us, the existence of a
+SMBH within the Milky Way is insufficient evidence for any sort of universal
+relationship between disk galaxies and SMBHs.  In the decades following the 
+discovery of the Milky Way SMBH, gas and stellar dynamical observations were 
+made of nearby disk galaxies, and in a number of these galaxies, similar mass
+distributions were found to that of our own galaxy.  Both gas and stellar 
+velocity distributions in the inner few parsecs of numerous disk
+galaxies, including our two nearest disk neighbours M31 and M33, suggested the
+presence of a SMBH within them.  It is now believed that the majority of disk
+galaxies contain a SMBH at their core (Magorrian et al. 1997 places the fraction
+at 97\% for early-type galaxies).
+
+\subsection{The $M_{BH}-M_{bulge}$ and $M_{BH}-\sigma$ Relations}
 We are used to seeing relations between masses and velocity distributions before
@@
 Virial Theorem tells us there must be a relation between the kinetic energy and
-the enclosed mass.
+the enclosed mass.  In the case of galactic spheroids, a similar relation is 
+observed between the total bulge mass, the stellar velocity dispersion $\sigma$
+within the bulge, and the mass of the black hole. By measuring the mass of the
+central dark object (the SMBH) through velocity dispersions at very small 
+radii and the mass of the bulge through dispersions at larger radii, a number
+of studies (Magorrian et al. 1997, Ford et al. 1997, and others) found that the
+SMBH and bulge masses were fairly well correlated, with a $M_{BH}$ between
+$2*10^{-3}M_{bulge}$ and $6*10^{-3}M_{bulge}$.  Observers, as one might imagine,
+also found a correlation between
+
 \section{Theory}
@@
 to answer this question was presented in Silk \& Rees 1998, with a coevolution 
-model.
+model.  This model starts from rather simple assumptions.  First, they assume
+that some primoridal gas clouds collapse to form 
 \section{Recent Developments}
@@
 Falcke, ARAA 39, 2001
-\item \textit{Quasars and Galaxy Formation} Silk \& Rees, A\&A 331, 1998.
+\item \textit{Quasars and Galaxy Formation} Silk \& Rees, A\&A 331, 1998
+\item \textit{The Demography of Massive Dark Objects in Galactic Centers} 
+Magorrian et al., AJ 115, 1998
 \item \textit{Inward Bound -- The Search for Supermassive Black Holes in 

### 2013-02-21 phys785/paper/paper.tex
Added all the classwork on angband

--- 2013-02-20 phys781/report.tex
@@
 %\usepackage{epsfig}
-\linespread{1.9}
+\doublespacing
 
@@
 
-\title{Physics 781 Term Report:\\  Bulges, Black Holes, and Cores:\\ A Review of
-the $M_{BH}-\sigma$ and  $M_{BH}-M_{bulge}$ Relation in Theory \& Observation}
+\title{Physics 785 Term Paper: Turbulence in Molecular Clouds: Origins \&
+Impacts}
 \author{Ben Keller}
@@
 
-\section{Introduction}
-when one examines the structure and evolution of a galaxy, at first glance it 
-would seem that the central supermassive black hole (SMBH) would play a 
-minimal role in the larger observable properties of the galaxy.  On both mass 
-and length scales, the SMBH is small compared to the galaxy as a whole.  For
-a typical Milky-Way type galaxy, the SMBH mass is 4 orders of magnitude less 
-than the total baryonic mass of the galaxy 
-($4*10^6M_\odot$ vs $6*10^{10}M\odot$).  The Schwartzchild radius of this black
-hole is even further from the scale of the galaxy, falling 11 orders of 
-magnitude smaller than the disk radius ($4*10^{-7}$pc vs. $25$kpc).  Recent 
-developments have shown, however, for the spheroidal bulge component of disk 
-galaxies, the mass of this SMBH has a tight correllation with the large scale
-properties of the bulge, most notably the total bulge mass and the velocity 
-dispersion of stars within the disk.  Upon a more thorough examination of the
-physical processes governing this system, and the history of its evolution, it
-should become clear to the reader that this is neither particularly mysterious
-nor is it truly something that should be unexpected.  Despite this, there still
-remains some uncertainty regarding the precise nature of these (hence
-refered to as the $M_{BH}-M_{bulge}$ and $M_{BH}-\sigma$) relations.  In this
-paper, I hope to guide the reader to an understanding of the theory behind these
-observations, as well as the current state of knowledge on the topic.
-\section{Background \& Observations}
-Simply by looking at night sky from a southern location, one can deduce that
-the Milky Way galaxy is densest in a region lying in the constellation 
-Saggitarius.  Kapteyn was able to determine, roughly a century ago, that the
-shape of our galaxy was that of a disk, and that our sun roughly halway along
-the radius of this disk.  Close examination of the core region, Sgr A, has 
-until relatively recently, been difficult due optically thick obscuring dust.
-With the advent of long wavelength astronomy, it has become possible to directly
-image stars and gas within the galactic core.  It has been known from infrared
-observations since Genzel \& Townes 1987 that the core radius of the galaxy is
-extremely compact, with current estimates placing it at $\approx 0.5$pc in
-radius (Merrit 2010).  Warm gas and dust have also been observed in infrared and
-radio wavelengths at higher densities in this core region.
-\subsection{A Central, Supermassive Black Hole}
-Within the core region of Sgr A exists a bright radio and hard X-ray emitter, 
-Sgr A*.  X-ray observations of this source have constrained it to being highly
-compact, and extremely hot ($10^8-10^{10}$K).  This observation points towards
-a highly energetic source within the core.  This source explained originally by
-two competing models: a driving SMBH, heating gas through accretion, or a 
-particularly violent and compact region of starburst activity.  The X-ray 
-emission observed within this core region constrained the mass of the black hole
-only very loosely ($M_{BH} > 100 M_\odot$) if starburst activity and UV heating
-of the gas was the source of the gas heating.  The starburst model truly fails
-in the face of one important datum:  the enclosed mass of the core.  By 
-examining the rotation curve of stars and gas very close to the core, the 
-mass enclosed by that core was able to be determined, as is shown in figure NUM.
-As is clear from the figure, the SMBH model is a perfect fit for the observed 
-rotation curve.  In addition to this, the densities for the core are so large
-that there is no configuration of stars that could be long lived at that 
-density.
-
-\subsection{Extragalactic SMBHs}
-\subsection{The $M_{BH}-\sigma$ Relation}
-We are used to seeing relations between masses and velocity distributions before
-in the form of the Tully-Fisher and Faber-Jackson relations for galaxies (though
-in these cases, it is an indirect measure of stellar mass through their 
-luminosity).  This should not come as much of a suprise to us, since the 
-Virial Theorem tells us there must be a relation between the kinetic energy and
-the enclosed mass.
-\section{Theory}
-While observations have done an excellent job of showing the \textit{existence}
-of the $M_{BH}-\sigma$ relation, they leave open the obvious question as to the
-nature of this relation, namely how and why it arises.  The first major attempt
-to answer this question was presented in Silk \& Rees 1998, with a coevolution 
-model.
-\section{Recent Developments}
-\section{Conclusion}
-\section*{References}
-\begin{enumerate}
-\item \textit{Exploring the unusually high black hole-to-bulge mass ratios in 
-NGC4342 and NGC4291: the asynchronous growth of bulges and black holes} Bogdan 
-et al.,  submitted to ApJ, retrieved via arXiv 2012
-\item \textit{The Distribution of Stars and Stellar Remnants at the Galactic 
-Center} Merritt, ApJ 718, 2010
-\item \textit{The Supermassive Black Hole at the Galactic Center} Melia \& 
-Falcke, ARAA 39, 2001
-\item \textit{Quasars and Galaxy Formation} Silk \& Rees, A\&A 331, 1998.
-\item \textit{Inward Bound -- The Search for Supermassive Black Holes in 
-Galaxtic Nuclei} Kormendy \& Richstone, ARAA 33, 1995
-\item \textit{Physical Conditions, Dynamics, and Mass Distribution in the Center
-of the Galaxy} Genzel \& Townes, ARAA 25, 1987
-\end{enumerate}
 \end{document}

### 2013-02-21 phys785/problemset1/cooling.py

@@ -1,0 +1,27 @@
+#!/usr/bin/python
+#Solution for Part 2 of PHYS785 Problem Set 1
+import numpy as np
+import matplotlib.pyplot as plt
+
+def lambdaH(temperature): #See Penston 1970 pp. 776
+	return 1.634e-11*3.23e-10*np.sqrt(temperature)*(1+17500/temperature)*np.exp(-118000/temperature)
+	return temperature
+def lambdaCII(temperature, Cfrac=3.75e-4): #See Dalgarno & McCray 1972 Eq. 3.
+	return Cfrac*7.9e-20/np.sqrt(temperature)*np.exp(-92/temperature)
+def lambdaSII(temperature, Sfrac=1.4e-5): #See Penston 1970 pp. 780
+	return Sfrac*8.44e-18/np.sqrt(temperature)*np.exp(-21400/temperature)
+def lambdaTotal(temperature):
+	return lambdaH(temperature)+lambdaCII(temperature)+lambdaSII(temperature)
+
+
+if __name__ == "__main__":
+	temperature = np.power(10, np.arange(1,6,0.01))
+	plt.loglog(temperature, lambdaH(temperature), lw=2, label='Hydrogen')
+	plt.loglog(temperature, lambdaCII(temperature), lw=2, label='Carbon II')
+	plt.loglog(temperature, lambdaSII(temperature), lw=2, label='Sulfur II')
+	plt.loglog(temperature, lambdaTotal(temperature), 'k--', lw=3, label='Total')
+	plt.ylim(1e-28,1e-17)
+	plt.legend(loc='best', title='Cooling Component')
+	plt.xlabel("Temperature $(K)$")
+	plt.ylabel(r"$\Lambda/n^2 (erg$ $cm^3 s^{-1})$")
+	plt.show()

### 2013-02-21 phys785/problemset1/plot_strasser.py

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+#Generate the Strasser & Taylor 2004 style plots for part 1 of PHYS785 problem set 1.
+import numpy as np
+from sys import argv
+import matplotlib.pyplot as plt
+
+if __name__ == "__main__":
+	datfile = np.genfromtxt(argv[1], skiprows=1)
+	LSR = datfile[:,0]
+	Toff = datfile[:,1]
+	Ton = datfile[:,2]
+	exptau = datfile[:,3]
+	dToff = datfile[:,4]
+	dTon = datfile[:,5]
+	dexptau = datfile[:,6]
+	Ts = Toff/(1-exptau)
+	dTs = dToff/(1-exptau)+dexptau/np.power(exptau-1, 2)
+	SN = np.abs(Toff-Ton)/np.sqrt(dToff**2+dTon**2)
+	highSN = np.where(SN > 3)[0]
+	plt.subplot(311)
+	plt.plot(LSR, Toff, 'k-')
+	plt.title("$l = %s \degree, b = %s \degree$" % (argv[1].split('_')[0], argv[1].split('_')[1][:-4]))
+	plt.ylabel(r'$T_{boff} (K)$')
+	plt.xlim(-160,50)
+	plt.subplot(312)
+	plt.errorbar(LSR, exptau, yerr=dexptau, color='k', marker='.')
+	plt.ylim(0,1.3)
+	plt.xlim(-160,50)
+	plt.ylabel(r'$<e^\tau>$')
+	plt.subplot(313)
+	plt.errorbar(LSR[highSN], Ts[highSN], color='k', linestyle='none', marker='.', yerr=dTs[highSN])
+	plt.xlim(-160,50)
+	plt.ylabel(r'$<T_S> (K)$')
+	plt.xlabel(r'Velocity $(km/s)$')
+	plt.tight_layout()
+	plt.show()

### 2013-02-21 phys785/paper/paper.tex
Added necessary bibtex stuff
Added some quick outline sections
Got the damn references working

@@
-\documentclass[12pt]{article}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage{setspace}
-\usepackage{geometry}
-\usepackage{gensymb}
-%\usepackage{epsfig}
-\doublespacing
-
-\geometry{
-  body={5in, 8.5in},
-left=1.25in,
-right=1.25in,
-  top=1.5in
-}
+\documentclass[12pt, preprint]{aastex}
 
@@
 \newpage
-
+\section{Introduction}
+The phenomenon of turbulence is one of the most heavily studied, and yet poorly
+understood processes in physics.  It can influence the flow of fluids across
+length scales spanning more than a dozen orders of magnitude, and can affect
+astrophysical processes at every scale, from dense cores up to the intergalactic
+medium (\citet{scan2013} suggests that cold galactic outflows can be
+driven by turbulence in the ISM).  In this paper, I will review the current understanding of turbulence in
+the molecular cloud environment.
+\section{Basic Turbulence Theory}
+\section{Observational Evidence}
+\section{Origins of Turbulence}
+\section{Impact of Turbulence on Cloud Structure \& Evolution}
+\section{Conclusion}
+\begin{thebibliography}{}
+	\bibitem[Scannapieco(2013)]{scan2013} Scannapieco, E.\ 2013, \apjl, 763, L31 
+\end{thebibliography}
 \end{document}

### 2013-02-21 phys785/paper/build.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+
+latex paper.tex
+latex paper.tex
+dvipdf paper.dvi
+evince paper.pdf

### 2013-02-25 phys785/paper/paper.tex
Added the first bit of the introduction.
Finished for sunday night.  Few more pages left, and figures

--- 2013-02-21 phys785/paper/paper.tex
@@
-\documentclass[12pt]{article}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage{setspace}
-\usepackage{geometry}
-\usepackage{gensymb}
-%\usepackage{epsfig}
-\doublespacing
-
-\geometry{
-  body={5in, 8.5in},
-left=1.25in,
-right=1.25in,
-  top=1.5in
-}
-
+\documentclass[12pt, preprint]{aastex}
+\doublespace
 \begin{document}
@@
 \newpage
+\section{Introduction}
+The phenomenon of turbulence is one of the most heavily studied, and yet poorly
+understood processes in astrophysics.  It can influence the flow of fluids across
+length scales spanning more than a dozen orders of magnitude, and can affect
+astrophysical processes at every scale, from dense cores \citep{larson1981} up to the intergalactic
+medium (\citet{scan2013} suggests that galactic outflows can be
+driven by the decay of turbulence in the ISM).  In this paper, I will review 
+the current understanding of turbulence in the context of molecular clouds.  I
+will focus primarily on how turbulence can arise within a cloud (primarily in terms of
+energy balance), and how it can drive the evolution of that cloud by promoting
+or preventing cloud coalescence, dispersal, and star formation within clouds.
 
+Molecular clouds are important locations for ISM chemistry and physics.  Though
+they occupy only $0.05\%$ of the ISM by volume, they contain roughly $20\%$ of
+the mass of the ISM.  The high densities ($>300 cm^{-3}$) and low temperatures
+($<100K$) make them important sites for ISM chemistry, and the location of most of
+the clustered and massive starformation within galaxies\citep{tiel2010}
+
+\section{Basic Turbulence Theory}
+\subsection{Kolmogorov's 1941 Theory}
+Nearly all modern theories of turbulence are build upon the Kolmogorov's 1941
+theory \citep{kolm1991}.  The Kolmogorov theory of turbulence describes locally
+homogeneous, locally isotropic turbulence (a reasonable assumption for turbulent
+flow with large Reynolds numbers, which certainly holds in all the phases of the
+ISM).  Kolmogorov proposed two key hypotheses. The first is that the distribution 
+of velocities in a turbulent flow are uniquely determined by the viscosity 
+$\nu$ and the average specific dispersion energy rate $\epsilon$,  From 
+this, a characteristic length $\eta$ and velocity $\sigma$:
+$$\eta = \nu^{3/4}\epsilon^{1/4}$$
+$$\sigma = \sqrt{\nu/\epsilon}$$
+The second hypothesis is that on scales much larger than $\eta$, the turbulent flow
+is uniquely determined \textit{only} by $\epsilon$.  These two assumptions
+allow you to uniquely determine a energy spectrum as a function of wavenumber
+$k$:
+$$E(k) \propto \epsilon^{2/3}k^{-5/3}$$
+The Kolmogorov energy spectrum has been the foundation of nearly all susbsequent
+theories of turbulence.  The negative power law slope can be seen as the cascade
+of energy down from large scale turbulent motions down to scales where viscous
+dissipation becomes important ($\lambda \approx \eta$).
+\subsection{MHD Turbulence}
+Modern theories of turbulence in molecular clouds rely on the interplay between
+"pure" fluid turbulence, and turbulence within magnetic fields.  By storing
+energy within these fields, the decay of turbulence can be delayed long enough
+to allow more modest energy sources to drive the turbulence observed in
+molecular clouds.  \citet{shu1987} reports magnetic field strengths in a number
+of molecular clouds on the order of $10-100 \mu G$.  Simple virial/equipartition
+arguments suggest that thermal, turbulent, and magnetic energies within a cloud
+should be roughly equal.
+
+The biggest difference between hydrodynamic and MHD turbulence is the breaking
+of Kolmogorov's assumption of isotropy.  The presence of magnetic field lines
+impose a preferred direction for the fluid flow (namely along these field
+lines).  This anisotropy can produce density gradients perpendicular to field
+lines.  In addition to these changes, magnetized fluids can also transport MHD
+waves, namely shear and compression Alfv\'{e}n waves (travelling along vs.
+across field lines respectively).  Since these oscillations have a different
+characteristic speed than the acoustic waves of Kolmogorov turbulence, they can
+result in a different power spectrum for turbulent modes, and their anisotropy
+means that wavenumbers parallel to field lines $k_\parallel$ have a different
+energy contribution to those perpendicular to the field $k_\perp$.  However, a
+mixing of these two modes can allow for a average power spectrum to be derived
+that approaches the values seen in isotropic MHD turbulence.  For
+isotropic MHD turbulence, the power spectrum derived by \citet{irosh1964} is a
+similar power-law spectrum to the Kolmogorov, with a $-3/2$ slope.  In the
+strong-field limit, this approximation matches reasonable with simulated and
+theoretical results.  In weak and intermediate fields, however, local conditions
+can have a significant effect on the energy spectrum.
+
+MHD also provides new modes for turbulent energy to decay.  Ohmic heating and
+ambipolar diffusion can convert turbulent energy within the fluid directly into
+heat, and dynamo processes can pull kinetic energy out of the fluid and store it
+in magnetic fields.  3D simulations of MHD turbulence suggest it decays in
+approximately $\tau_{cross} = L/v_{rms}$, where $L$ is the scale of the cloud,
+and $v_{rms}$ is the rms turbulent velocity. In environments like molecular
+clouds, where turbulence is highly supersonic, the effects of MHD vs. "pure"
+hydrodynamic turbulence may be small \citep{elm2004}
+
+\section{Observational Evidence}
+Direct observations of turbulence have been made by looking at the velocity
+spectrum in molecular hydrogen tracer elements (commonly $^{12}CO$ and
+$^{13}CO$). The velocity dispersion $\sigma$ in a region of size $L$ can be
+derived from the Kolmogorov power spectrum, and is found to be:
+$$\sigma \propto L^{1/3}$$
+for the $-5/3$ power-law energy spectrum \citep{larson1979}.
+\citet{larson1979} used observations of $CO$ and $HI$ within cool
+clouds, along with the velocity dispersion of stellar spectra collected from
+young (less than a few $Gyr$ old) stars to estimate the dispersion in cool clouds.  
+The use of young stars was justified by the fact that they should retain the
+momentum of the gas they formed from.  His
+observatiosn covered scales from a few $pc$ up to $20 kpc$.  Figure NUM shows
+the relationship he found between region size and the velocity dispersion
+within these regions is in good agreement with the $1/3$ slope power law
+predicted by Kolmogorov turbulence.
+More recent works have used additional statistical and numerical tools to detect
+turbulence.  \citet{brunt2003} used principal component analysis of $^{12}CO$
+emission in the FCRAO radio telescope's Outer Galaxy Survey.  to calculate the
+power spectrum of molecular clouds in the outer galaxy.  He found values for the
+power spectrum slope $\beta$ ranging $\approx 1.5$ to $\approx 3$, bounding the
+Kolmogorov value of $5/3$.
+\section{Origins of Turbulence}
+The observation of turbulence in molecular clouds raises two major questions.
+Firstly, from whence does the energy within the turbulent motions come, and
+secondly, how does this energy convert from whatever form it arrives in into 
+turbulent motion.
+
+Unlike turbulence on larger scales, which can be driven by galactic rotations
+and motions of clouds through the galactic ISM \citep{balb1991}, turbulence in
+molecular clouds is primarily powered by local sources of energy.  Since
+turbulence is rapidly dissipated, a constant input of energy is needed to keep
+it from simply decaying down the Kolmogorov microscales and converting into
+heat.  This decay is characterized by the rms Mach number $M_{rms}$, the Jeans
+length $\lambda_J$, free-fall time $\tau_{ff}$ and the characteristic driving 
+wavelength of the turbulence $\lambda_T$ \citep{mac1999}:
+$$ \tau_D \approx 3.9 \frac{\tau_{ff}\lambda_D}{M_{rms}\lambda_J}$$
+The values of $\lambda_D$ and $\lambda_J$ for molecular clouds is not
+well-known, but the ratio of the two is expected to be on the order of 1-10
+\citep{mac2004}.
+
+Once a molecular cloud has begun forming stars, stellar feedback can provide
+ample energy to drive both bulk and turbulent motions within clouds.
+\citet{agertz2012} reports that stars typically return 
+$\approx 10^{34} erg s^{1-} M_\odot^{-1}$ in the form of stellar winds and
+supernovae.  Massive stars also produce ionizing UV, generating HII regions that
+can shock the surrounding molecular gas.  With even conservative estimates of
+efficiencies between the feedback rates, stellar feedback combined with
+turbulence generated by fluid instabilities in the formation of molecular clouds
+provides sufficient energy to power the observed turbulence within molecular
+clouds\citep{elm2004}.  The chaotic driving of supernovae blasts and wind-carved
+bubbles on a scale of $50-500pc$ (ie, on the scales comparable tot the total
+cloud size), which then cascades down the to smaller scales.
+\section{Impact of Turbulence on Cloud Structure \& Evolution}
+\subsection{Cloud Formation}
+\subsection{Turbulent Pressure Support}
+Observations of molecular clouds provide two perplexing facts, namely that they
+are typically cold (10-100K), and massive (much larger than the Jeans mass
+$M_J$) \citep{gold1978}.  Yet they do not show evidence of rapid collapse, or of being the
+extremely short lived objects that these facts would imply.  This suggests that
+a there is some sort of non-thermal pressure supporting these clouds.
+In molecular clouds that are in hydrostatic equilibrium, determining the sources
+of pressure that supports the clouds against gravitational collapse is key in
+determining which clouds will collapse, and why.  Non-thermal pressure support is
+essential to allow super-Jeans mass clouds to persist.
+
+Treating the energy within a volume's turbulence as  asource of pressure was
+proposed as early as \citet{chandra1951}, where the Jeans stability criteria is
+modified from:
+$$\lambda_J = 2\pi \sqrt{\frac{c_s^2}{4\pi G\rho}}$$
+where $c_s$ is the soundspeed, to a smaller value derived using the mean
+turbulent velocity $u$:
+$$\lambda_J = 2\pi \sqrt{\frac{c_s^2+u^2/3}{4\pi G\rho}}$$
+For molecular clouds, where turbulence tends to be highly supersonic, this can
+act to significantly increase the stability of a cloud against gravitational
+collapse.
+\subsection{Mixing \& Chemistry}
+\subsection{Larson's Laws \& Star formation}
+Strangely, turbulence can both support clouds (on a global scale), and cause
+collapse (on smaller scales) \citep{mac2004}.  Since molecular cloud
+turubulence is often supersonic, it is well beyond the incompressible regime,
+and can produce density perturbations that can then collapse to form
+stars\citep{elm2004}. Turbulence in nascent starforming 
+regions is a critical element in the modern theory 
+of starformation. One of the earliest works proposing this connection is
+\citet{larson1981}.  Building on previous "merging bubble/shell" models of
+molecular clouds and the larger ISM from works such as \citet{norman1980} and
+\citet{mckee1977}, Larson used $^{13}CO$ observations of Taurus, $\rho$
+Ophiucus, Orion, and a number of other clouds to determine a the mass function
+of clouds within these clumps.  By measuring the velocity dispersions of these
+clouds, along with their dimension, he observed that $\sigma \propto L^{0.38}$
+(the ``size-linewidth" relation).  Since this value is close to the Kolmogorov
+real-space power law slope $1/3$, \citet{larson1981} argued that the size of
+clumps within molecular clouds was determined primarily by turbulence within
+the cloud.
+
+One of the most interesting recent developments is the suggestion by
+\citet{hopk2013} that the
+shape and universality of the stellar initial mass function is the result of 
+turbulent dynamics within
+starforming clouds. \citet{hopk2013} proposes a model of gravo-turbulent
+fragmentation using the excursion set formalism similar to that previously used 
+succesfully to predict the Halo Mass Function and clustering rates in
+large-scale cosmological structures by \citet{press1974}.  By applying this tool
+to the turbulent fluid of a molecular cloud, and tracking the first and last
+crossings of overdense perturbations (see figure NUM), the mass function of
+protostellar cores, (and thus the IMF) can be predicted using Monte Carlo
+realizations of the turbulent density spectrum.  This analytic framework
+can be used to generally predict the mass function from fragmentation
+on any scale from essentially first principles (including the formation 
+of clouds themselves, if they do in fact
+form from turbulent fragmentation).  This framework suggests that gravitational
+collapse of turbulent overdensity is the dominant driving force for much of the
+substructure within molecular clouds.
+\section{Conclusion}
+
+\begin{thebibliography}{}
+	\bibitem[Chandrasekhar(1951)]{chandra1951} Chandrasekhar, S.\ 1951, 
+		Royal Society of London Proceedings Series A, 210, 26 
+	\bibitem[Iroshnikov(1964)]{irosh1964} Iroshnikov, P.~S.\ 1964, 
+		\sovast, 7, 566 
+	\bibitem[Press \& Schechter(1974)]{press1974} Press, W.~H., \& Schechter, P.\
+			1974, \apj, 187, 425 
+	\bibitem[McKee \& Ostriker(1977)]{mckee1977} McKee, C.~F., \& Ostriker,
+			J.~P.\ 1977, \apj, 218, 148 
+	\bibitem[Goldsmith \& Langer(1978)]{gold1978} Goldsmith, P.~F., \& Langer,
+			W.~D.\ 1978, \apj, 222, 881 
+		\bibitem[Larson(1979)]{larson1979} Larson, R.~B.\ 1979, \mnras, 
+		186, 479 
+	\bibitem[Norman \& Silk(1980)]{norman1980} Norman, C., \& Silk, J.\ 
+		1980, \apj,	238, 158 
+	\bibitem[Larson(1981)]{larson1981} Larson, R.~B.\ 1981, \mnras, 
+		194, 809 
+	\bibitem[Shu, Adams \& Lizano(1987)]{shu1987} Shu, F. H., Adams, F.C.,
+		Lizano, S.\ 1987 \araa, 25, 23
+	\bibitem[Balbus \& Hawley(1991)]{balb1991} Balbus, S.~A., \& Hawley, J.~F.\
+			1991, \apj, 376, 214 
+	\bibitem[Kolmogorov(1991)]{kolm1991} Kolmogorov, A.~N.\ 1991, 
+		Royal Society of London Proceedings Series A, 434, 9 
+	\bibitem[Evans (1999)]{evans1999} Evans, N. J.\
+			1999, \araa, 37, 311
+	\bibitem[Mac Low(1999)]{mac1999} Mac Low, M.-M.\ 1999, \apj, 
+		524, 169 
+	\bibitem[Brunt(2003)]{brunt2003} Brunt, C.~M.\ 2003, \apj, 583, 
+		280 
+	\bibitem[Elmegreen \& Scalo(2004)]{elm2004} Elmegreen, B.~G., \& Scalo, J.\
+			2004, \araa, 42, 211 
+	\bibitem[Scalo 	\& Elmegreen(2004)]{scalo2004} Scalo, J., \& Elmegreen, B.~G.\
+			2004, \araa, 42, 275
+	\bibitem[Mac Low \& Klessen(2004)]{mac2004} Mac Low, M.-M., \& Klessen,
+		R.~S.\ 2004, Reviews of Modern Physics, 76, 125 
+	\bibitem[Tielens(2010)]{tiel2010} Tielens, A.~G.~G.~M.\ 2010, 
+		The Physics and Chemistry of the Interstellar Medium, by 
+		A.~G.~G.~M.~Tielens, Cambridge, UK: Cambridge University Press,	2010
+	\bibitem[Crutcher(2012)]{crutch2012} Crutcher, R.~M.\ 2012, \araa,
+		50, 29 
+	\bibitem[Agertz et al.(2012)]{agertz2012} Agertz, O., Kravtsov, 
+		A.~V., Leitner, S.~N., \& Gnedin, N.~Y.\ 2012, arXiv:1210.4957 
+	\bibitem[Hopkins(2013)]{hopk2013} Hopkins, P.~F.\ 2013,
+		\mnras, 729 
+	\bibitem[Scannapieco(2013)]{scan2013} Scannapieco, E.\ 2013, \apjl, 763, L31 
+\end{thebibliography}
 \end{document}

### 2013-02-25 phys785/paper/paper.tex
Finished the writing (first draft)

@@
 Modern theories of turbulence in molecular clouds rely on the interplay between
-"pure" fluid turbulence, and turbulence within magnetic fields.  By storing
+``pure" fluid turbulence, and turbulence within magnetic fields.  By storing
 energy within these fields, the decay of turbulence can be delayed long enough
@@
 and $v_{rms}$ is the rms turbulent velocity. In environments like molecular
-clouds, where turbulence is highly supersonic, the effects of MHD vs. "pure"
+clouds, where turbulence is highly supersonic, the effects of MHD vs. ``pure"
 hydrodynamic turbulence may be small \citep{elm2004}
@@
 \subsection{Cloud Formation}
+The largest effect of turbulence on molecular clouds may not be intra-cloud
+phenomena, but instead the actual \textit{formation} of clouds.
+\citet{larson1981} suggested from his observations that cloud lifetimes were on
+the order of $10^7 yr$, about twice their free-fall time.  If most clouds are
+this young, this implies that clouds are both formed and destroyed on a
+relatively continuous and rapid basis. Recent simulation results from
+\citet{hopk2011} support this picture of a constantly replenished supply of
+short-lived GMCs, and some suggest that even shorter lifetimes of a few $10^6$
+years are more likely \cite{mac2004}.
+
+Early models of cloud formation relied on a hierarchical merger type picture of
+cloud collision and coalescence to explain the production of giant molecular
+clouds from the atomic and ionized medium.  \citet{larson1981} reports that
+these models fail to produce the production rates needed to sustain the observed
+abundance of molecular clouds in the galaxy in light of their relatively short
+lifetime (these models were developed with the assumption that cloud lifetimes
+were on the order of $10^8 yr$).  Turbulence within the larger ISM can produce, 
+in the highly compressible supersonic regime obeserved, strong density perturbations and
+clumpy, filiamentary structures like that seen in figure NUM.  \citet{val2004}
+presents a picture of supersonic turbulence or colliding flows producing thin, 
+shocked sheets that then fragments to form molecular clouds. Coupled with
+thermal multiphase instabilities, this can act to rapidly build dense clumps
+that will quickly become molecular clouds as atomic hydrogen becomes molecular
+on dust grains and the high densities of the cloud allow for self-shielding.
+The dominant theory of cloud formation currently is that shocks, from turbulence
+and supernovae, build large overdensities where molecule formation is very
+rapid, and that cloud dispersal by feedback (or the same turbulent flow that
+can form them) happens on the order of a roughly 1-10 Myr.
 \subsection{Turbulent Pressure Support}
@@
 are typically cold (10-100K), and massive (much larger than the Jeans mass
-$M_J$) \citep{gold1978}.  Yet they do not show evidence of rapid collapse, or of being the
-extremely short lived objects that these facts would imply.  This suggests that
-a there is some sort of non-thermal pressure supporting these clouds.
+$M_J$) \citep{gold1978}.  This, coupled with their relatively short lifetimes,
+seems to imply that they collapse gravitationally relatively quickly after they 
+form.  However, measurements of star formation efficiency within these clouds,
+and of the relative stellar mass fractions of the milky way and other galaxies
+tells us that these clouds only convert a small fraction of their mass into
+stars \citep{mac2004}, and that their lifetimes are in fact longer than their
+free-fall times. This suggests that
+a there is some sort of non-thermal pressure supporting these clouds, in
+addition to processes that can disrupt or destroy clouds before they can convert
+most of their mass into stars. While disruption of clouds by feedback can reduce
+their star formation efficiency (by destroying them after they form only a few
+massive stars)\citep{hopk2011}, the observation of super-Jeans mass clouds that
+are older than the time needed for them to collapse needs this additional
+mechanism to keep clouds supported.
 In molecular clouds that are in hydrostatic equilibrium, determining the sources
@@
 \subsection{Mixing \& Chemistry}
+Molecular clouds, being \textit{molecular}, are sites in which more 
+complicated ISM chemistry can occur.  Since these clouds are extremely dense and
+cool, while many of the reactants for forming simple ($CO$, $HCN$, etc.) and
+complex (PAHs, amino acids, etc) are abundant, the conditions in the molecular
+cloud are often not ideal for slow, steady formation of these compoounds.
+PDRs at the edge of clouds can catalyze the formation of some compounds, but
+destroy others.  Many of the compounds in molecular clouds have negative heats
+of formation, implying they would form extremely slowly at the mean $\approx
+10K$ temperatures in the cloud.  In addition to this, chemical reaction networks
+found that early-time solutions to time-dependent evolution equations (rather
+than equalibrium concentrations) matched most closely the observed abundances in
+molecular clouds\citep{scalo2004}.
+
+Turbulence offers an explanation for all of these observations.  Since the
+interiors of clouds are not isotropic in density, temperature, or UV flux,
+turbulent mixing can transport species into regions where their production is
+enhanced, and then spread the products into the rest of the cloud.  Decay of
+turbulence and shock heatingcan result in local temperature increases, allowing 
+endothermic reactions to produce species that otherwise would not be 
+seen\citep{xie1995}.  MHD turbulence
+can have a significant impact on ion-neutral reactions by magnetically forcing
+ions, producing an effectively faster mixing rate for ionized species.
 \subsection{Larson's Laws \& Star formation}
@@
 to the turbulent fluid of a molecular cloud, and tracking the first and last
-crossings of overdense perturbations (see figure NUM), the mass function of
+crossings of overdense perturbations (see figures NUM and NUM), the mass function of
 protostellar cores, (and thus the IMF) can be predicted using Monte Carlo
@@
 substructure within molecular clouds.
+
 \section{Conclusion}
-
+It is clear that on every scale related to the physics of molecular clouds, from
+the atomic and molecular chemical processes within them, to the actual formation
+of the clouds themselves, turbulence is a key ingredient.  Theoretical
+predictions from as early as 1951, and observations from the 1970s confirmed
+that turbulence was deeply related to the internal structure and evolution of
+molecular clouds.  Recent work has continued to build upon this, suggesting that
+the chemistry of the molecular ISM, and the mass function of stars are also 
+closely tied to the turbulent motions within molecular clouds.  As simulations
+and observations further constrain the energy spectrum, growth rate, and
+dissipation of turbulence, a key component to building a unified picture 
+of molecular cloud creation and destruction, star formation, and interstellar 
+chemistry will be complete.
 \begin{thebibliography}{}
@@
 		Royal Society of London Proceedings Series A, 434, 9 
+	\bibitem[Xie et al.(1995)]{xie1995} Xie, T., Allen, M., 
+		\& Langer, W.~D.\ 1995, \apj, 440, 674 
 	\bibitem[Evans (1999)]{evans1999} Evans, N. J.\
@@
 		R.~S.\ 2004, Reviews of Modern Physics, 76, 125 
+	\bibitem[V{\'a}zquez-Semadeni et al.(2006)]{val2006}
+		V{\'a}zquez-Semadeni, E., Ryu, D., Passot, T., Gonz{\'a}lez, R.~F., 
+		\& Gazol, A.\ 2006, \apj, 643, 245 
 	\bibitem[Tielens(2010)]{tiel2010} Tielens, A.~G.~G.~M.\ 2010, 
@@
 		A.~G.~G.~M.~Tielens, Cambridge, UK: Cambridge University Press,	2010
+	\bibitem[Hopkins et al.(2011)]{hopk2011} Hopkins, P.~F., 
+		Quataert, E., \& Murray, N.\ 2011, \mnras, 417, 950 
 	\bibitem[Crutcher(2012)]{crutch2012} Crutcher, R.~M.\ 2012, \araa,

### 2013-02-25 phys785/paper/paper.tex
Spellchecked

@@
 ($<100K$) make them important sites for ISM chemistry, and the location of most of
-the clustered and massive starformation within galaxies\citep{tiel2010}
+the clustered and massive star formation within galaxies\citep{tiel2010}
 
@@
 $$E(k) \propto \epsilon^{2/3}k^{-5/3}$$
-The Kolmogorov energy spectrum has been the foundation of nearly all susbsequent
+The Kolmogorov energy spectrum has been the foundation of nearly all subsequent
 theories of turbulence.  The negative power law slope can be seen as the cascade
@@
 lines).  This anisotropy can produce density gradients perpendicular to field
-lines.  In addition to these changes, magnetized fluids can also transport MHD
+lines.  In addition to these changes, magnetised fluids can also transport MHD
 waves, namely shear and compression Alfv\'{e}n waves (travelling along vs.
@@
 momentum of the gas they formed from.  His
-observatiosn covered scales from a few $pc$ up to $20 kpc$.  Figure NUM shows
+observation covered scales from a few $pc$ up to $20 kpc$.  Figure NUM shows
 the relationship he found between region size and the velocity dispersion
@@
 it from simply decaying down the Kolmogorov microscales and converting into
-heat.  This decay is characterized by the rms Mach number $M_{rms}$, the Jeans
+heat.  This decay is characterised by the rms Mach number $M_{rms}$, the Jeans
 length $\lambda_J$, free-fall time $\tau_{ff}$ and the characteristic driving 
@@
 $\approx 10^{34} erg s^{1-} M_\odot^{-1}$ in the form of stellar winds and
-supernovae.  Massive stars also produce ionizing UV, generating HII regions that
+supernovae.  Massive stars also produce ionising UV, generating HII regions that
 can shock the surrounding molecular gas.  With even conservative estimates of
@@
 cloud collision and coalescence to explain the production of giant molecular
-clouds from the atomic and ionized medium.  \citet{larson1981} reports that
+clouds from the atomic and ionised medium.  \citet{larson1981} reports that
 these models fail to produce the production rates needed to sustain the observed
@@
 were on the order of $10^8 yr$).  Turbulence within the larger ISM can produce, 
-in the highly compressible supersonic regime obeserved, strong density perturbations and
-clumpy, filiamentary structures like that seen in figure NUM.  \citet{val2004}
+in the highly compressible supersonic regime observed, strong density perturbations and
+clumpy, filamentary structures like that seen in figure NUM.  \citet{val2004}
 presents a picture of supersonic turbulence or colliding flows producing thin, 
@@
 
-Treating the energy within a volume's turbulence as  asource of pressure was
+Treating the energy within a volume's turbulence as  a source of pressure was
 proposed as early as \citet{chandra1951}, where the Jeans stability criteria is
@@
 $$\lambda_J = 2\pi \sqrt{\frac{c_s^2}{4\pi G\rho}}$$
-where $c_s$ is the soundspeed, to a smaller value derived using the mean
+where $c_s$ is the sound speed, to a smaller value derived using the mean
 turbulent velocity $u$:
@@
 complex (PAHs, amino acids, etc) are abundant, the conditions in the molecular
-cloud are often not ideal for slow, steady formation of these compoounds.
-PDRs at the edge of clouds can catalyze the formation of some compounds, but
+cloud are often not ideal for slow, steady formation of these compounds.
+PDRs at the edge of clouds can catalyse the formation of some compounds, but
 destroy others.  Many of the compounds in molecular clouds have negative heats
@@
 found that early-time solutions to time-dependent evolution equations (rather
-than equalibrium concentrations) matched most closely the observed abundances in
+than equilibrium concentrations) matched most closely the observed abundances in
 molecular clouds\citep{scalo2004}.
@@
 Turbulence offers an explanation for all of these observations.  Since the
-interiors of clouds are not isotropic in density, temperature, or UV flux,
+interiors of clouds are not homogeneous in density, temperature, or UV flux,
 turbulent mixing can transport species into regions where their production is
 enhanced, and then spread the products into the rest of the cloud.  Decay of
-turbulence and shock heatingcan result in local temperature increases, allowing 
+turbulence and shock heating can result in local temperature increases, allowing 
 endothermic reactions to produce species that otherwise would not be 
@@
 can have a significant impact on ion-neutral reactions by magnetically forcing
-ions, producing an effectively faster mixing rate for ionized species.
+ions, producing an effectively faster mixing rate for ionised species.
 \subsection{Larson's Laws \& Star formation}
@@
 collapse (on smaller scales) \citep{mac2004}.  Since molecular cloud
-turubulence is often supersonic, it is well beyond the incompressible regime,
+turbulence is often supersonic, it is well beyond the incompressible regime,
 and can produce density perturbations that can then collapse to form
-stars\citep{elm2004}. Turbulence in nascent starforming 
+stars\citep{elm2004}. Turbulence in nascent star forming 
 regions is a critical element in the modern theory 
-of starformation. One of the earliest works proposing this connection is
+of star formation. One of the earliest works proposing this connection is
 \citet{larson1981}.  Building on previous "merging bubble/shell" models of
@@
 turbulent dynamics within
-starforming clouds. \citet{hopk2013} proposes a model of gravo-turbulent
+star forming clouds. \citet{hopk2013} proposes a model of gravo-turbulent
 fragmentation using the excursion set formalism similar to that previously used 
-succesfully to predict the Halo Mass Function and clustering rates in
+successfully to predict the Halo Mass Function and clustering rates in
 large-scale cosmological structures by \citet{press1974}.  By applying this tool
@@
 protostellar cores, (and thus the IMF) can be predicted using Monte Carlo
-realizations of the turbulent density spectrum.  This analytic framework
+realisations of the turbulent density spectrum.  This analytic framework
 can be used to generally predict the mass function from fragmentation
@@
 		A.~V., Leitner, S.~N., \& Gnedin, N.~Y.\ 2012, arXiv:1210.4957 
-	\bibitem[Hopkins(2013)]{hopk2013} Hopkins, P.~F.\ 2013,
-		\mnras, 729 
+	\bibitem[Hopkins(2013)]{hopk2013} Hopkins, P.~F.\ 2013, \mnras, 
+		729 
 	\bibitem[Scannapieco(2013)]{scan2013} Scannapieco, E.\ 2013, \apjl, 763, L31 

### 2013-02-25 phys785/paper/paper.tex
Added figures

@@
 \documentclass[12pt, preprint]{aastex}
+\usepackage{float}
 \doublespace
@@
 momentum of the gas they formed from.  His
-observation covered scales from a few $pc$ up to $20 kpc$.  Figure NUM shows
+observation covered scales from a few $pc$ up to $20 kpc$.  Figure 1 shows
 the relationship he found between region size and the velocity dispersion
@@
 Kolmogorov value of $5/3$.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.4]{figures/larsonlaw_larson1981.eps}
+	\caption{\citet{larson1981}'s results showing a tight correlation between
+	the velocity dispersion within a cloud and the size scale of that cloud.
+The slope of the fitted line is 0.38, while the slope of the Kolmogorov
+density-velocity dispersion PDF is 1/3.}
+\end{figure}
 \section{Origins of Turbulence}
@@
 in the highly compressible supersonic regime observed, strong density perturbations and
-clumpy, filamentary structures like that seen in figure NUM.  \citet{val2004}
+clumpy, filamentary structures like that seen in figure 2.  \citet{val2006}
 presents a picture of supersonic turbulence or colliding flows producing thin, 
@@
 can form them) happens on the order of a roughly 1-10 Myr.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.4]{figures/turbulent_LMC_elm2004.eps}
+	\caption{21cm emission from the Large Magellanic Cloud.  Note the
+		filiaments, voids, and clumps in this HI emission map.  These
+		structures, and the associated 2D power spectrum of them, are closely
+		associated with turbulent motions, and can lead to the rapid production
+	of molecular clouds in overdense regions.  Image from \citet{elm2004}.}
+\end{figure}
 \subsection{Turbulent Pressure Support}
@@
 to the turbulent fluid of a molecular cloud, and tracking the first and last
-crossings of overdense perturbations (see figures NUM and NUM), the mass function of
+crossings of overdense perturbations (see figures 3 and 4), the mass function of
 protostellar cores, (and thus the IMF) can be predicted using Monte Carlo
@@
 substructure within molecular clouds.
+
+\begin{figure}[H] 
+	\centering
+	\includegraphics[scale=0.3]{figures/structure_hopk2013.eps}
+	\caption{The key feature of \citet{hopk2013}'s theory of turbulent
+		fragmentation is the transition across the line of stability (dashed
+		red) where overdensities can collapse.  This line shows when
+		gravitational potential overwhelms internal support.  By evalauating realizations of turbulent
+		overdensities, the spectrum of overdensities that cross this barrier and
+	become bound can be determined.}
+\end{figure}
+
+\begin{figure}[H] 
+	\centering
+	\includegraphics[scale=0.3]{figures/fragtree_hopk2013.eps}
+	\caption{In the \citet{hopk2013} model, turbulent overdensities fragment
+	over time in a cascading ``tree", producing a spectrum of clump/cloud sizes}
+\end{figure}
 
@@
 chemistry will be complete.
+
 \begin{thebibliography}{}
@@
 \end{thebibliography}
+
 \end{document}

### 2013-03-14 phys785/paper/paper.tex
Final tweaks to the turbulence paper

@@
 \section{Introduction}
-The phenomenon of turbulence is one of the most heavily studied, and yet poorly
+The phenomenon of turbulence is one of the most heavily studied, and, in some
+ways, poorly
 understood processes in astrophysics.  It can influence the flow of fluids across
-length scales spanning more than a dozen orders of magnitude, and can affect
+lengths spanning more than a dozen orders of magnitude, and can affect
 astrophysical processes at every scale, from dense cores \citep{larson1981} up to the intergalactic
@@
 ($<100K$) make them important sites for ISM chemistry, and the location of most of
-the clustered and massive star formation within galaxies\citep{tiel2010}
+the clustered and massive star formation within galaxies\citep{tiel2010}.
 
@@
 \subsection{Kolmogorov's 1941 Theory}
-Nearly all modern theories of turbulence are build upon the Kolmogorov's 1941
-theory \citep{kolm1991}.  The Kolmogorov theory of turbulence describes locally
+Nearly all modern theories of turbulence are built upon the Kolmogorov's 1941
+theory of incompressible turbulent flow\citep{kolm1991}.  The Kolmogorov theory of turbulence describes locally
 homogeneous, locally isotropic turbulence (a reasonable assumption for turbulent
@@
 The Kolmogorov energy spectrum has been the foundation of nearly all subsequent
-theories of turbulence.  The negative power law slope can be seen as the cascade
+theories of turbulence.  The negative power law slope can be viewed as the cascade
 of energy down from large scale turbulent motions down to scales where viscous
@@
 Modern theories of turbulence in molecular clouds rely on the interplay between
-``pure" fluid turbulence, and turbulence within magnetic fields.  By storing
+``pure" fluid turbulence, and turbulence within magnetic fields and magnetized
+fluids.  By storing
 energy within these fields, the decay of turbulence can be delayed long enough
@@
 waves, namely shear and compression Alfv\'{e}n waves (travelling along vs.
-across field lines respectively).  Since these oscillations have a different
+across field lines respectively)\citep{elm2004}  Since these oscillations have a different
 characteristic speed than the acoustic waves of Kolmogorov turbulence, they can
@@
 theoretical results.  In weak and intermediate fields, however, local conditions
-can have a significant effect on the energy spectrum.
+can have a significant effect on the energy spectrum\citep{elm2004}
 
@@
 Direct observations of turbulence have been made by looking at the velocity
-spectrum in molecular hydrogen tracer elements (commonly $^{12}CO$ and
-$^{13}CO$). The velocity dispersion $\sigma$ in a region of size $L$ can be
+spectrum in molecular hydrogen tracer elements (most often $^{12}CO$ and
+$^{13}CO$). The predicted velocity dispersion $\sigma$ in a region of size $L$ can be
 derived from the Kolmogorov power spectrum, and is found to be:
@@
 bubbles on a scale of $50-500pc$ (ie, on the scales comparable tot the total
-cloud size), which then cascades down the to smaller scales.
+cloud size), which then cascades down the to smaller scales.  Clouds formed from
+a turbulent medium will also retain much of the turbulence of their progenitor
+gas.
 \section{Impact of Turbulence on Cloud Structure \& Evolution}
@@
 relatively continuous and rapid basis. Recent simulation results from
-\citet{hopk2011} support this picture of a constantly replenished supply of
+\citet{hopk2011} support this picture of a constantly replenished galactic supply of
 short-lived GMCs, and some suggest that even shorter lifetimes of a few $10^6$
-years are more likely \cite{mac2004}.
+years are more likely \citep{mac2004}.
 
@@
 ions, producing an effectively faster mixing rate for ionised species.
+The turbulent flows within a molecular cloud act like a conveyor belt for
+chemical species, ferrying them to and from physical conditions that promote or
+halt creation, destruction, and reactions into other compounds.
 \subsection{Larson's Laws \& Star formation}
@@
 of star formation. One of the earliest works proposing this connection is
-\citet{larson1981}.  Building on previous "merging bubble/shell" models of
+\citet{larson1981}.  Building on previous ``merging bubble/shell" models of
 molecular clouds and the larger ISM from works such as \citet{norman1980} and
@@
 
-One of the most interesting recent developments is the suggestion by
-\citet{hopk2013} that the
+One of the most interesting recent developments is the work done in 
+\citet{hopk2013} that suggests the
 shape and universality of the stellar initial mass function is the result of 
@@
 protostellar cores, (and thus the IMF) can be predicted using Monte Carlo
-realisations of the turbulent density spectrum.  This analytic framework
+realisations of density fields from the turbulent density spectrum.  This analytic framework
 can be used to generally predict the mass function from fragmentation
@@
 	\centering
-	\includegraphics[scale=0.3]{figures/fragtree_hopk2013.eps}
+	\includegraphics[scale=0.4]{figures/fragtree_hopk2013.eps}
 	\caption{In the \citet{hopk2013} model, turbulent overdensities fragment
@@
 \section{Conclusion}
-It is clear that on every scale related to the physics of molecular clouds, from
+It is clear that on every scale that physics happens in molecular clouds, from
 the atomic and molecular chemical processes within them, to the actual formation

### 2013-12-09 phys719/paper/paper.tex
Finished fluids paper

\documentclass[12pt, preprint]{aastex}
\usepackage{float}
\usepackage[cm]{fullpage}
\begin{document}

\title{Physics 719 Term Paper: AREPO, a Hydrodynamics Solver on an Unstructured
Moving Mesh}
\author{Ben Keller}
\maketitle
\newpage
\section{Introduction}
AREPO solves the Euler equations using a novel method: rather than calculating
fluxes through a fixed, structured grid (Cartesian or otherwise), it generates
an unstructured mesh on the fly from state information of the volume and
uses that mesh to define where fluxes are calculated \citep{springel2009}.  By
allowing the fluid flow to define the grid, AREPO is meant to serve as a
compromise between the alternate formulations of hydrodynamics: Eulerian (i.e.
grid based methods), and Lagrangian (ie, particle based methods).  It is part of
a family of hybrid techniques: ``Arbitrary Lagrangian-Eulerian'' (ALE) methods.

While both the Lagrangian and Eulerian formulations are equally valid from a
mathematical standpoint, each has weaknesses when applied to solve problems
where only finite resolution and computational resources are available. Eulerian
codes are able to use Godunov-type methods to capture shocks without the need
for high spatial resolution, and also suppress spurious artifacts (post-shock
ringing, etc.), while smoothed particle hydrodynamics (SPH, the dominant
Lagrangian method) require both more resolution and carefully chosen explicit
artificial viscosity (AV) to accurately capture strong shocks.  Eulerian codes
suffer from the fact that their grids act as unphysical preferred frames of
reference (they lack Galilean invariance), introducing spurious diffusion as
features are smeared over grid cells. Additionally, they often require much
smaller timesteps criteria than SPH codes.

In this paper, I will first explain how AREPO solves the Euler equations using a
finite volume method over a moving Voronoi mesh.  A Voronoi mesh is a unique
tessellation of all points where each cell is composed of space closer to the
contained mesh-generating point than any other mesh generation point.  As a
large amount of effort is required to construct and maintain this mesh, the
second section covers these mesh-generation routines.  In the penultimate
section, I explain how AREPO does its time integration, as it uses a careful
timestep criteria and multiple timesteps. Finally, I conclude with
some remarks about where AREPO stands in a somewhat crowded field of
astrophysics simulation codes.  AREPO also includes modifications to the Euler
equations for self-gravitating fluids and cosmological expansion, mesh
refinement and de-refinement, as well as a dual-energy formulation for use in
low-resolution simulations of cold, supersonic flows that I will not discuss
here out of space consideration.
\section{AREPO's Finite Volume Hydrodynamics Method} 
\subsection{Core Method}
While the idea of solving the fluid equations on an unstructured mesh
\citep{xu1997} or a moving mesh \citep{gnedin1995} is not new, using
\textit{both} of these methods simultaneously was not heavily explored prior to
AREPO.  The basic derivation of the method follows fairly similarly to 
other Monotone Upstream-centered Schemes for Conservation Laws (MUSCL), with a
few differences.  To integrate the primitive state vector $\mathbf{U}$, with
flux vector $\mathbf{F}$ and cell-averaged value $\mathbf{Q}$:
\begin{equation}
	\begin{array}{l l l}
		\mathbf{U} = (\rho, \rho\mathbf{v}, \rho e),  &
		\mathbf{F} = (\rho\mathbf{v}, \rho v^2+P, \mathbf{v}(\rho e+P)), &
	\mathbf{Q_i} = (m_i, \mathbf{p_i}, E_i), \\
\end{array}
\end{equation}
AREPO first calculates a flux across across each face (with surface normal
$\mathbf{A_{ij}}$ of a given mesh cell):
\begin{equation}
	\mathbf{F_{ij}} = \frac{1}{A_{ij}}\int_{A_{ij}}
	[\mathbf{F(U)-Uw}]d\mathbf{A_{ij}}
\end{equation}
where $\mathbf{w}$ is the velocity of the the boundary itself (naturally, this
term is omitted in the Eulerian form).  With these fluxes, the cell-averaged
values can be updated simply using a Godunov-type scheme:
\begin{equation}
	Q_{i}^{n+1} = Q_i^n -\Delta t \sum_j A_{ij} \mathbf{\hat F_{ij}^{n+1/2}}
\end{equation}
where $\mathbf{\hat F_{ij}}$ is a time-average approximate flux.  AREPO uses an
unsplit method, where fluxes are calculated for each face before any are
applied.  These fluxes can be generated using a slope-limited piecewise linear
approximation.  To determine the slope of the approximation, AREPO uses a
gradient for each of the primitive variables, estimated using the vector between
the mesh-generating points (more details on these points can be found in section
3), $\mathbf{r_{ij}}$, and the vector from the midpoint of this vector to the
$ij$-face's center of mass $\mathbf{c_{ij}}$:
\begin{equation}
	\nabla \phi_i = \frac{1}{V_i}\sum_{i\neq j}
	A_{ij}\left([\phi_j-\phi_i]\mathbf{\frac{c_{ij}}{r_{ij}}} -
\frac{\phi_i+\phi_j}{2}\frac{\mathbf{r_{ij}}}{r_{ij}}\right)
\end{equation}
The linear approximation for in each cell, with center of mass $\mathbf{s_i}$
becomes: 
\begin{equation}
	\phi(\mathbf{r}) = \phi_i + \nabla \phi_i\cdot(\mathbf{r-s_i})
\end{equation}
This gives a second order space and time accuracy, with a stencil consisting of the
cell and all its neighbours.  In order for the integration scheme
to remain monotonicity preserving (MP), a slope limiter is used to ensure that the
estimate doesn't over/undershoot in cases involving discontinuous flow:
\begin{equation}
	\nabla\phi_{i,limited} = \mathrm{min}(1,\Psi_{ij})\nabla\phi_{i}
\end{equation}
\begin{equation}
	\Psi_{ij} = \left\{
		\begin{array}{l l l}
			(\phi_i^{max}-\phi_i)/\Delta\phi_{ij} & if & \Delta\phi_{ij} > 0\\
			(\phi_i^{min}-\phi_i)/\Delta\phi_{ij} & if & \Delta\phi_{ij} < 0\\
			1 & if \Delta\phi_{ij} = 0
	\end{array} \right.
\end{equation}
This acts to reduce the order of the method near discontinuities, and ensures
that monotonicity is preserved. AREPO uses a somewhat liberal slope limiter 
that makes it MP, but not total variation diminishing (TVD), making the scheme
less dissipative overall at the cost of allowing some artifacts to be produced
at shocks.
\subsection{Calculating Fluxes}
To calculate the flux through a cell face, first the face's local frame velocity
must be calculated.  For a face bounding two cells, with velocities $w_R$ and
$w_L$, the face velocity $w$ is:
\begin{equation}
	w = \frac{w_R+w_L}{2}+w'
\end{equation}
where $w'$ is a rotation term to account for the component of the velocity
arising from the relative motion of the cell centers of mass and their
mesh-generating points.  Once this is calculated, the lab-frame states of each
cell is first boosted to the face's rest frame.  The state vectors are then
interpolated to find their values on the face's centroid, at $\Delta t/2$.
These interpolated values are then multiplied by a rotation matrix $\Lambda$ to bring
their x-axis perpendicular to the face.  This finally allows the solution
$\mathbf{W_F}$ to a 1D Riemann problem across the face to be calculated. By
reversing the rotation and the boost, this solution in the lab frame
$\mathbf{W_{lab}}$ can be determined:
\begin{equation}
	\mathbf{W_{lab}} = \Lambda^{-1}\mathbf{W_F+w}
\end{equation}
This is the used to generate the flux vector $\mathbf{\hat F}$:
\begin{equation}
	\mathbf{\hat F = F(W_{lab}) - W_{lab}\cdot w}
\end{equation}
Using this, the AREPO scheme is Galilean invariant, as fluxes are all
calculated in the invariant boundary frame.
\section{Building \& Maintaining Voronoi Meshes}
Solving the fluid equations over a Voronoi mesh is only half the battle of
evolving a set of initial conditions with AREPO.  Before each step in the
hydrodynamics solver begins, a new tessellation must be computed; after each
step, the points that generate the mesh must be moved (at the velocity of their
cell's fluid).
\subsection{Initial Construction}
Given a set of points, there exists only one tessellation in which each cell
contains only points closest to its contained point: the Voronoi tessellation.
AREPO exploits a convenient fact that every Voronoi tessellation has a dual
tessellation, the Delaunay, that is much easier computed.  The Delaunay mesh is a
triangulation which places a triangle across chords of a circumsphere that contains on
its edge the three vertex points (mesh generating points), such that this
circle contains no mesh generating points.  This can be built using recursive
divide-and-conquer algorithms similar to quicksort (e.g. \textit{quickhull}
\citep{barber1996}, \textit{Dewall}\citep{cignoni1997}). These algorithms have
asymptotic cost comparable to tree-building ($O(N\log N)$ in the average case,
$O(N^2)$ in the worst case).  Once the Delaunay triangulation is completed, the
Voronoi faces are generated using the midpoints of the Delaunay circumspheres as
the vertices of the Voronoi cells.  This gives each cell a set of faces, a
volume, and a center of mass that is then used by the hydrodynamics solver to
evolve the system.
\subsection{Restructuring}
While the ``pure'' Voronoi tessellation is perfectly capable of being evolved
forward in time without introducing error-causing mesh artifacts, it can often
produce a very anisotropic mesh, even in situations where the physical density
of a volume is isotropic. This doesn't affect the accuracy of the method, but it
does increase its cost.  To deal with this, AREPO introduces a small numerical
``kick'' to the mesh-generator velocities, to move their mesh-generating points
towards their centers of mass.  If these points are close, then the resulting
Voronoi cells are highly regular at equal density after a small number of
iterations.  AREPO adds a velocity kick (less than the sound speed $c_i$) to the velocities of the mesh
generators if the distance $d_i$ between their centers of mass $\mathbf{s_i}$
and mesh-generators $\mathbf{r_i}$ become more than some fraction $\eta$ of the the
cell radius $R_i$ (see equation 12).  
\begin{equation}
	\mathbf{w_i'} = \mathbf{w_i}+\left\{
		\begin{array}{l l l}
			0 & if & d_i/(\eta R_i) < 0.9\\
			c_i\frac{\mathbf{s_i-r_i}}{d_i}\frac{d_j-0.9\eta R_i}{0.2\eta R_i} & if & 0.9\leq d_i/(\eta R_i) < 1.1\\
			c_i\frac{\mathbf{s_i-r_i}}{d_i} & if & 1.1\leq d_i/(\eta R_i) \\
	\end{array} \right.
\end{equation}
AREPO typically uses a threshold of $\eta=1/4$. This kick acts to keep cells
``round'' as the simulation evolves.  As the solver is fully Galilean invariant,
the boost resulting from these kicks does not result in any errors introduced in
the hydrodynamics solutions.  It appears to me that this would introduce a small
amount of shot-noise into the mesh velocity field, which may manifest in the
solution AREPO produces.
\section{Time Integration \& Independent Timesteps}
The general CFL condition used in AREPO calculates an effective distance scale
$R_i$, sound speed $c_i$ and flow velocity relative to the grid $v_i'$ (which is
typically negligible because of the semi-Lagrangian mesh motion).  Preventing
$R_i$ from becoming small is one of the primary reasons for mesh restructuring.
\begin{equation}
	\begin{array}{l l l}
		R_i = (3V_i/4\pi)^{1/3}, & &
	\Delta t_i = C_{CFL}\frac{R_i}{c_i+v_i'}\\
\end{array}
\end{equation}
AREPO typically adopts $C_{CFL} \approx 0.4-0.8$.  Since these timesteps are
calculated individually per cell, individual cells are capable of being run at
different time resolutions, depending on their local velocities and densities.
AREPO gives each cell a timestep that is a power of two smaller than the global
timestep, such that the above timestep criteria is obeyed for all cells.

Since this calculation only examines local properties, it needs a way to
anticipate interactions with approaching supersonic flows. In order to do this,
AREPO takes the smaller of the timestep from equation 12 or the distance over
the ``signal speed'' (flow velocity+sound speed) between two cells.  It uses a
tree-based search in order to find all other cells and calculate the non-local
timesteps for each cell (at a cost of $O(N\log N)$, compared to $O(1)$ for a
\citet{saitoh2009} type limit).

For each face, the smaller timestep of the two cells at the interface is used.
Each substep then calculates fluxes for all faces that reside on that timestep
or, a smaller timestep (active faces) (e.g. a face on a step 1/4 the timestep of
another face will calculate fluxes 4 times for every 1 time the long step face
calculates them).  At the end of each substep, the mesh is rebuilt for active
cells.  Cells that are not active ``store up'' fluxes coming from faces that are
on shorter timesteps, and apply them once they complete their step.

This looks to me to be potentially the most problematic aspect of the method, as
you ought to have (if you want to preserve the Lagrangian aspect) the grid fully
rebuilt every time \textit{any} cell is evolved, but the grid is only rebuilt
for the active cells.  This means the faces that the fluxes between cells on
small timesteps and cells on large timesteps become less accurate as the
difference in timestep increases (and thus the fluxes calculated become less
accurate). In other words, the longer the range in timesteps, the less
Lagrangian the method is.

\section{Conclusion}
AREPO seems to be a clever mix of the Eulerian and Lagrangian approaches to
fluid mechanics.  It promises to deliver accurate, low diffusivity shock
capturing with a 2nd order space and time accurate, unsplit Godunov MUSCL
method.  At the same time, it has modified the Eulerian version of this method
to be Galilean invariant, and provide Courant times competitive with SPH.  For
simulations of highly supersonic, cold flows (situations like turbulence in the
cold ISM), AREPO likely offers one of the best methods available.

Whether it becomes a serious challenge to popular SPH and AMR codes will depend
on whether the additional cost of the method is worth the accuracy it provides.
AREPO needs to solve 2 Riemann problems per face, with much more faces per cell
than in a standard Cartesian grid.  Its timestep estimator is also fairly
expensive and quite conservative.  In a fairly small galaxy cluster test ($32^3$
particles), AREPO was 60\% slower than a comparable SPH code.  If AREPO can be
shown to scale well to both large numbers of cells and large numbers of
processors, it has a good chance of becoming one of the frontrunners in the
field of cosmological hydrodynamics codes.
\begin{thebibliography}{}
	\bibitem[Gnedin (1995)]{gnedin1995} Gnedin, N. Y. 1995.
		ApJS, 97, 231
	\bibitem[Bradford Barber et al. (1996)]{barber1996} Bradford Barber, C. et
		al. 1996.
		ACM Transactions on Mathematical Software 22, 469
	\bibitem[Xu (1997)]{xu1997} Xu, G. 1997.
		MNRAS 288, 903
	\bibitem[Cignoni Z et al. (1997)]{cignoni1997} Cignoni Z, P et al. 1997.
		Computer-Aided Design, 30, 333
	\bibitem[Saito \& Makino (2009)]{saitoh2009} Saitoh, T. R. \& Makino, J
		2009. ApJ 697, 99
	\bibitem[Springel (2009)]{springel2009} Springel, V. 2009.
		MNRAS 401, 791
\end{thebibliography}

\end{document}
